---
title: "Website Update Helpers"
author: "Alexander Ross"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)

# Set the path to your website directory
# Change this if you move the website folder
WEBSITE_DIR <- "/Users/alexanderross/Desktop/website"
```

# Overview

This document contains helper functions for updating your academic website. The website is built with Quarto and deployed to GitHub Pages at [alexrosspolisci.com](https://alexrosspolisci.com).

**Key files:**

- `index.qmd` - Homepage with bio
- `cv.qmd` - CV page (embeds PDF)
- `resume.qmd` - Resume page (unlisted, accessible at /resume.html)
- `projects.qmd` - Research & publications
- `files/Alex_CV.pdf` - Your CV PDF
- `files/Alex_Ross_Resume.pdf` - Your resume PDF

---

# Setup

First, run this chunk to load the helper functions into your R session:

```{r load-helpers}
# ============================================================================
# WEBSITE UPDATE HELPER FUNCTIONS
# ============================================================================
# These functions help you update your academic website from R.
# The website uses Quarto and is deployed via GitHub Pages.
# ============================================================================

# ----------------------------------------------------------------------------
# CONFIGURATION
# ----------------------------------------------------------------------------

# Path to your website directory
# Update this if you move the website folder to a different location
WEBSITE_DIR <- "/Users/alexanderross/Desktop/website"

# ----------------------------------------------------------------------------
# FUNCTION: update_cv
# ----------------------------------------------------------------------------
# Purpose: Replace your CV PDF with a new version
#
# How it works:
#   1. Copies the new PDF file to the website's files/ directory
#   2. Renames it to "Alex_CV.pdf" (the expected filename)
#   3. The cv.qmd page embeds this PDF, so no other changes needed
#
# Arguments:
#   new_cv_path - The full path to your new CV PDF file
#                 Example: "~/Downloads/CV_March_2026.pdf"
#
# Returns: TRUE if successful, FALSE otherwise
# ----------------------------------------------------------------------------
update_cv <- function(new_cv_path) {

  # Check that the source file exists
  if (!file.exists(new_cv_path)) {
    # File not found - print error and return FALSE
    message("Error: File not found at: ", new_cv_path)
    return(FALSE)
  }

  # Check that it's a PDF file
  if (!grepl("\\.pdf$", tolower(new_cv_path))) {
    # Not a PDF - print warning but continue anyway
    message("Warning: File does not appear to be a PDF. Continuing anyway...")
  }

  # Define the destination path
  # The CV must be named "Alex_CV.pdf" for the website to find it
  dest_path <- file.path(WEBSITE_DIR, "files", "Alex_CV.pdf")

  # Copy the file, overwriting the existing CV
  # file.copy returns TRUE on success, FALSE on failure
  success <- file.copy(
    from = new_cv_path,      # Source: your new CV
    to = dest_path,           # Destination: website files folder
    overwrite = TRUE          # Replace the existing file
  )

  # Report the result
  if (success) {
    message("CV updated successfully!")
    message("New CV copied to: ", dest_path)
    message("Run render_site() and then push_changes() to publish.")
  } else {
    message("Error: Failed to copy file.")
  }


  return(success)
}

# ----------------------------------------------------------------------------
# FUNCTION: update_resume
# ----------------------------------------------------------------------------
# Purpose: Replace your resume PDF with a new version
#
# How it works:
#   1. Copies the new PDF file to the website's files/ directory
#   2. Renames it to "Alex_Ross_Resume.pdf" (the expected filename)
#   3. The resume.qmd page embeds this PDF
#
# Note: The resume page is unlisted (not in navigation) and has noindex
#       so search engines won't index it. Access it directly at:
#       https://alexrosspolisci.com/resume.html
#
# Arguments:
#   new_resume_path - The full path to your new resume PDF file
#
# Returns: TRUE if successful, FALSE otherwise
# ----------------------------------------------------------------------------
update_resume <- function(new_resume_path) {

  # Check that the source file exists
  if (!file.exists(new_resume_path)) {
    message("Error: File not found at: ", new_resume_path)
    return(FALSE)
  }

  # Define the destination path
  dest_path <- file.path(WEBSITE_DIR, "files", "Alex_Ross_Resume.pdf")


  # Copy the file, overwriting the existing resume
  success <- file.copy(
    from = new_resume_path,
    to = dest_path,
    overwrite = TRUE
  )

  if (success) {
    message("Resume updated successfully!")
    message("New resume copied to: ", dest_path)
    message("Run render_site() and then push_changes() to publish.")
  } else {
    message("Error: Failed to copy file.")
  }

  return(success)
}

# ----------------------------------------------------------------------------
# FUNCTION: render_site
# ----------------------------------------------------------------------------
# Purpose: Render the Quarto website to generate HTML files
#
# How it works:
#   1. Changes to the website directory
#   2. Runs "quarto render" which processes all .qmd files
#   3. Outputs HTML files to the docs/ folder
#   4. The docs/ folder is what GitHub Pages serves
#
# Note: The _quarto.yml file has a render list that only includes:
#       index.qmd, cv.qmd, resume.qmd, projects.qmd, contact.qmd
#       This prevents the Projects/ folder from being rendered.
#
# Arguments: None
#
# Returns: The exit code from quarto (0 = success)
# ----------------------------------------------------------------------------
render_site <- function() {

  message("Rendering website...")

  # Store the current working directory so we can return to it later
  original_dir <- getwd()

  # Change to the website directory
  # Quarto needs to run from the project root to find _quarto.yml
  setwd(WEBSITE_DIR)

  # Run the quarto render command
  # system() executes a shell command and returns its exit code
  # Exit code 0 means success, anything else is an error
  result <- system("quarto render")

  # Return to the original directory
  setwd(original_dir)

  # Report the result

  if (result == 0) {
    message("Site rendered successfully!")
    message("Run push_changes() to publish, or preview_site() to preview locally.")
  } else {
    message("Error: Quarto render failed with exit code ", result)
  }

  return(result)
}

# ----------------------------------------------------------------------------
# FUNCTION: preview_site
# ----------------------------------------------------------------------------
# Purpose: Open a local preview of the rendered website
#
# How it works:
#   1. Opens the docs/index.html file in your default browser
#   2. This shows what the site will look like when published
#
# Note: This opens the local files, not the live site. To see the live
#       site after pushing, use open_live_site().
#
# Arguments: None
#
# Returns: Nothing (opens browser as side effect)
# ----------------------------------------------------------------------------
preview_site <- function() {

  # Construct the path to the rendered index.html
  index_path <- file.path(WEBSITE_DIR, "docs", "index.html")

  # Check that the file exists (site has been rendered)
  if (!file.exists(index_path)) {
    message("Error: docs/index.html not found. Run render_site() first.")
    return(invisible(NULL))
  }

  message("Opening local preview...")

  # browseURL opens a URL or file path in the default browser
  browseURL(index_path)
}

# ----------------------------------------------------------------------------
# FUNCTION: open_live_site
# ----------------------------------------------------------------------------
# Purpose: Open the live website in your browser
#
# How it works:
#   Opens https://alexrosspolisci.com in your default browser
#
# Arguments: None
#
# Returns: Nothing (opens browser as side effect)
# ----------------------------------------------------------------------------
open_live_site <- function() {
  message("Opening live site...")
  browseURL("https://alexrosspolisci.com")
}

# ----------------------------------------------------------------------------
# FUNCTION: git_status
# ----------------------------------------------------------------------------
# Purpose: Show the current git status of the website repository
#
# How it works:
#   1. Changes to the website directory
#   2. Runs "git status" to show modified/untracked files
#   3. Helps you see what changes will be committed
#
# Arguments: None
#
# Returns: Nothing (prints status to console)
# ----------------------------------------------------------------------------
git_status <- function() {

  original_dir <- getwd()
  setwd(WEBSITE_DIR)

  # Run git status
  # intern = TRUE captures the output as a character vector
  status <- system("git status", intern = TRUE)

  setwd(original_dir)

  # Print each line of the status output
  cat(status, sep = "\n")
}

# ----------------------------------------------------------------------------
# FUNCTION: push_changes
# ----------------------------------------------------------------------------
# Purpose: Commit and push all changes to GitHub
#
# How it works:
#   1. Changes to the website directory
#   2. Stages all changes with "git add ."
#   3. Creates a commit with your message
#   4. Pushes to GitHub
#   5. GitHub Pages automatically deploys the new version
#
# Arguments:
#   message - A short description of what you changed
#             Example: "Update CV with new publication"
#
# Returns: The exit code from git push (0 = success)
# ----------------------------------------------------------------------------
push_changes <- function(message = "Update website") {

  message("Pushing changes to GitHub...")

  original_dir <- getwd()
  setwd(WEBSITE_DIR)

  # Stage all changes
  # "git add ." adds all modified and new files in the directory
  system("git add .")

  # Create a commit with the provided message
  # shQuote() safely escapes the message for the shell
  commit_cmd <- paste0('git commit -m ', shQuote(message))
  commit_result <- system(commit_cmd)

  # Check if commit succeeded
  if (commit_result != 0) {
    message("Note: Nothing to commit, or commit failed.")
    setwd(original_dir)
    return(commit_result)
  }

  # Push to GitHub
  push_result <- system("git push")

  setwd(original_dir)

  if (push_result == 0) {
    message("Changes pushed successfully!")
    message("Site will update at https://alexrosspolisci.com in 1-2 minutes.")
  } else {
    message("Error: Push failed with exit code ", push_result)
  }

  return(push_result)
}

# ----------------------------------------------------------------------------
# FUNCTION: quick_cv_update
# ----------------------------------------------------------------------------
# Purpose: All-in-one function to update CV and publish
#
# How it works:
#   1. Copies your new CV to the website
#   2. Renders the site
#   3. Commits and pushes to GitHub
#   4. Opens the live site so you can verify
#
# This is the easiest way to update your CV - just one function call!
#
# Arguments:
#   new_cv_path - The full path to your new CV PDF file
#
# Returns: TRUE if all steps succeeded, FALSE otherwise
# ----------------------------------------------------------------------------
quick_cv_update <- function(new_cv_path) {

  message("=== Quick CV Update ===\n")

  # Step 1: Update the CV file
  message("Step 1/4: Copying new CV...")
  if (!update_cv(new_cv_path)) {
    return(FALSE)
  }

  # Step 2: Render the site
  message("\nStep 2/4: Rendering site...")
  if (render_site() != 0) {
    return(FALSE)
  }

  # Step 3: Push to GitHub
  message("\nStep 3/4: Pushing to GitHub...")
  if (push_changes("Update CV") != 0) {
    return(FALSE)
  }

  # Step 4: Open the live site
  message("\nStep 4/4: Opening live site...")
  Sys.sleep(2)
  # Brief pause before opening browser
  open_live_site()

 message("\n=== CV Update Complete! ===")
  message("The site will update in 1-2 minutes. Refresh to see changes.")

  return(TRUE)
}

# Print a message confirming functions are loaded
message("Website helper functions loaded!")
message("Available functions:")
message("  - update_cv(path)        : Replace CV PDF")
message("  - update_resume(path)    : Replace resume PDF")
message("
  - render_site()          : Render the Quarto site")
message("  - preview_site()         : Preview locally")
message("  - open_live_site()       : Open live website")
message("  - git_status()           : Show git status")
message("  - push_changes(msg)      : Commit and push")
message("  - quick_cv_update(path)  : Update CV in one step")
```

---

# Usage Examples

## Update Your CV (Quick Method)

The easiest way to update your CV is with `quick_cv_update()`. This does everything in one step:

```{r example-quick-cv}
# Replace with the actual path to your new CV
quick_cv_update("~/Downloads/My_New_CV.pdf")
```

## Update Your CV (Step by Step)

If you prefer more control, you can do each step separately:

```{r example-cv-steps}
# Step 1: Copy the new CV to the website
update_cv("~/Downloads/My_New_CV.pdf")

# Step 2: Render the site to generate new HTML
render_site()

# Step 3: Preview locally to make sure it looks right
preview_site()

# Step 4: Push to GitHub to publish
push_changes("Update CV - March 2026")

# Step 5: Open the live site to verify
open_live_site()
```

## Update Your Resume

The resume works the same way as the CV:
```{r example-resume}
# Update the resume PDF
update_resume("~/Downloads/My_New_Resume.pdf")

# Render and push
render_site()
push_changes("Update resume")
```

## Check Status Before Pushing

You can check what files have changed before pushing:

```{r example-status}
# See what files have been modified
git_status()
```

---

# Troubleshooting

## "Command not found: quarto"

If you get this error, Quarto isn't in your PATH. You may need to:

1. Install Quarto from [quarto.org](https://quarto.org/docs/get-started/)
2. Or specify the full path to quarto in the `render_site()` function

## "Nothing to commit"

This means you haven't made any changes since the last commit. This is fine - it just means there's nothing new to push.

## Site not updating after push

GitHub Pages can take 1-2 minutes to rebuild. Try:

1. Wait a minute and refresh
2. Hard refresh with Cmd+Shift+R to clear cache
3. Check the GitHub Actions tab in your repo for build status

---

# Reference

| Function | Purpose |
|----------|---------|
| `update_cv(path)` | Copy new CV PDF to website |
| `update_resume(path)` | Copy new resume PDF to website |
| `render_site()` | Render Quarto site to HTML |
| `preview_site()` | Open local preview in browser |
| `open_live_site()` | Open live site in browser |
| `git_status()` | Show git status |
| `push_changes(message)` | Commit and push to GitHub |
| `quick_cv_update(path)` | All-in-one CV update |
