---
title: "Benefit Timing and Government Attitudes"
format:
  pdf:
    toc: true
    number-sections: true
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Setup

```{r packages}
rm(list = ls())

pacman::p_load(
  tidyverse,
  lubridate,
  sjlabelled,
  knitr,
  scales
)
```

```{r load-data}
df <- readRDS("df_full_panel_both_samples.rds")
cat("Loaded:", nrow(df), "observations,", ncol(df), "variables\n")
```

# Outcome Variables

All outcome variables are measured on 0-10 scales where higher values indicate more of the construct.

## Trust in Quebec Government

```{r trust-qc}
# trust_qcgov: 0-10 scale, higher = more trust
# Available in all waves

df <- df %>%
  mutate(
    trust_qc = as.numeric(trust_qcgov)
  )

# Validate
cat("trust_qc summary:\n")
summary(df$trust_qc)
cat("\nDistribution:\n")
table(df$trust_qc, useNA = "ifany")
cat("\nN by wave:\n")
print(table(df$wave, !is.na(df$trust_qc)))
```

## Trust in Canadian Government

```{r trust-can}
# trust_cangov: 0-10 scale, higher = more trust
# NOTE: Only available in waves 2 and 3

df <- df %>%
  mutate(
    trust_can = as.numeric(trust_cangov)
  )

# Validate
cat("trust_can summary:\n")
summary(df$trust_can)
cat("\nN by wave (NOTE: not asked in wave 1):\n")
print(table(df$wave, !is.na(df$trust_can)))
```

## Attachment to Quebec

```{r attach-qc}
# attach_qc: 0-10 scale, higher = more attachment
# Available in all waves

df <- df %>%
  mutate(
    attachment_qc = as.numeric(attach_qc)
  )

# Validate
cat("attachment_qc summary:\n")
summary(df$attachment_qc)
cat("\nDistribution:\n")
table(df$attachment_qc, useNA = "ifany")
```

## Financial Satisfaction

```{r financial-satisf}
# current_financialsatisf: 0-10 scale, higher = more satisfied
# Available in all waves

df <- df %>%
  mutate(
    financial_satisf = as.numeric(current_financialsatisf)
  )

# Validate
cat("financial_satisf summary:\n")
summary(df$financial_satisf)
cat("\nDistribution:\n")
table(df$financial_satisf, useNA = "ifany")
```

## Summary of Outcome Variables

```{r outcome-summary}
outcomes <- df %>%
  summarise(
    across(
      c(trust_qc, trust_can, attachment_qc, financial_satisf),
      list(
        n = ~sum(!is.na(.)),
        mean = ~mean(., na.rm = TRUE),
        sd = ~sd(., na.rm = TRUE),
        min = ~min(., na.rm = TRUE),
        max = ~max(., na.rm = TRUE)
      ),
      .names = "{.col}_{.fn}"
    )
  ) %>%
  pivot_longer(
    everything(),
    names_to = c("variable", "stat"),
    names_sep = "_(?=[^_]+$)"
  ) %>%
  pivot_wider(names_from = stat, values_from = value)

kable(outcomes, digits = 2, caption = "Outcome Variable Summary Statistics")
```

## Correlation Matrix

```{r outcome-correlations}
cor_matrix <- df %>%
  select(trust_qc, trust_can, attachment_qc, financial_satisf) %>%
  cor(use = "pairwise.complete.obs")

kable(round(cor_matrix, 3), caption = "Outcome Variable Correlations")
```

# Validation Checks

## Check that higher values mean "more"

Based on questionnaire review and data inspection:

-   **trust_qc**: 0 = no trust, 10 = complete trust ✓
-   **trust_can**: 0 = no trust, 10 = complete trust ✓
-   **attachment_qc**: 0 = no attachment, 10 = strong attachment ✓
-   **financial_satisf**: 0 = very dissatisfied, 10 = very satisfied ✓

```{r direction-check}
# Check correlations make sense (all should be positive with each other)
cat("All pairwise correlations positive (as expected):\n")
print(all(cor_matrix[!is.na(cor_matrix)] >= 0 |
          cor_matrix == diag(cor_matrix)))

# Financial satisfaction should correlate with trust
cat("\nFinancial satisfaction correlates with trust_qc:",
    round(cor(df$financial_satisf, df$trust_qc, use = "complete.obs"), 3), "\n")
```

## Distribution Visualization

```{r outcome-histograms, fig.height=8, fig.width=10}
df %>%
  select(trust_qc, trust_can, attachment_qc, financial_satisf) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  filter(!is.na(value)) %>%
  ggplot(aes(x = value)) +
  geom_histogram(binwidth = 1, fill = "steelblue", color = "white") +
  facet_wrap(~variable, scales = "free_y") +
  scale_x_continuous(breaks = 0:10) +
  labs(
    title = "Distribution of Outcome Variables",
    x = "Value (0-10 scale)",
    y = "Count"
  ) +
  theme_minimal()
```

# Treatment Variables

## Survey Timing

```{r survey-timing}
# Parse survey date and extract day of month
df <- df %>%
  mutate(
    survey_datetime = as.POSIXct(startdate),
    survey_date = as.Date(survey_datetime),
    day_of_month = day(survey_datetime),
    month = month(survey_datetime),
    year = year(survey_datetime)
  )

cat("Day of month distribution:\n")
print(table(df$day_of_month, useNA = "ifany"))
```

## Temporal Proximity Functions

```{r proximity-functions}
# Function to calculate distance to a fixed payment day
# Returns: days_since_last, days_until_next, circular_distance (min of the two)

calc_payment_proximity <- function(survey_day, payment_day, days_in_month = 30) {
  # Days since last payment
  if (survey_day >= payment_day) {
    days_since <- survey_day - payment_day
    days_until <- (days_in_month - survey_day) + payment_day
  } else {
    days_since <- (days_in_month - payment_day) + survey_day
    days_until <- payment_day - survey_day
  }

  # Circular distance (shortest path)
  circular <- min(days_since, days_until)

  return(list(
    days_since = days_since,
    days_until = days_until,
    circular = circular
  ))
}

# Vectorized version
calc_proximity_vec <- function(survey_days, payment_day, days_in_month = 30) {
  n <- length(survey_days)
  days_since <- numeric(n)
  days_until <- numeric(n)

  for (i in seq_len(n)) {
    if (is.na(survey_days[i])) {
      days_since[i] <- NA
      days_until[i] <- NA
    } else {
      result <- calc_payment_proximity(survey_days[i], payment_day, days_in_month)
      days_since[i] <- result$days_since
      days_until[i] <- result$days_until
    }
  }

  circular <- pmin(days_since, days_until)

  return(data.frame(
    days_since = days_since,
    days_until = days_until,
    circular = circular
  ))
}
```

## Create Proximity Variables for Fixed-Date Programs

Payment days by program:

-   **mprog_childbnft** (Child Benefit): 20th
-   **mprog_socasst** (Social Assistance): 1st
-   **mprog_basinc** (Basic Income): 1st
-   **mprog_cfincsupp** (CF Income Support): 1st
-   **mprog_housingbnft** (Housing Benefit): 28th
-   **mprog_retpen** (Retirement Pension): 28th (approx, end of month)
-   **mprog_dispen** (Disability Pension): 28th (approx, end of month)

```{r proximity-vars}
# Calculate proximity for each fixed-date program

# Child Benefit (20th)
prox_child <- calc_proximity_vec(df$day_of_month, payment_day = 20)
df$prox_child_since <- prox_child$days_since
df$prox_child_until <- prox_child$days_until
df$prox_child_circ <- prox_child$circular

# Social Assistance / Basic Income / CFIS (1st)
prox_first <- calc_proximity_vec(df$day_of_month, payment_day = 1)
df$prox_first_since <- prox_first$days_since
df$prox_first_until <- prox_first$days_until
df$prox_first_circ <- prox_first$circular

# Housing Benefit / Pensions (28th)
prox_28 <- calc_proximity_vec(df$day_of_month, payment_day = 28)
df$prox_28_since <- prox_28$days_since
df$prox_28_until <- prox_28$days_until
df$prox_28_circ <- prox_28$circular

# Verify
cat("=== Proximity to 20th (Child Benefit) ===\n")
cat("Days since last payment:\n")
print(summary(df$prox_child_since))

cat("\nDays until next payment:\n")
print(summary(df$prox_child_until))

cat("\nCircular distance:\n")
print(summary(df$prox_child_circ))
```

## Beneficiary Status Variables

Logic:

-   If someone reports receiving a benefit in ANY wave, code them as beneficiary in ALL waves
-   UNLESS they select "None of these programs" in a specific wave, then code as non-beneficiary only in that wave

```{r beneficiary-vars}
# Fixed-date benefit programs
fixed_benefits <- c("mprog_childbnft", "mprog_socasst", "mprog_basinc",
                    "mprog_cfincsupp", "mprog_housingbnft", "mprog_retpen",
                    "mprog_dispen")

# Step 1: Create raw indicator (1 if reported in this wave, 0 otherwise)
for (prog in fixed_benefits) {
  var_name <- paste0("raw_", prog)
  df[[var_name]] <- ifelse(!is.na(df[[prog]]), 1, 0)
}

# Step 2: Create indicator for "none of these programs" selected
df$selected_none <- ifelse(!is.na(df$mprog_none), 1, 0)

# Step 3: For each person, check if they EVER reported each benefit
# Then propagate to all waves, UNLESS they selected "none" in that wave

create_beneficiary_var <- function(df, prog_col) {
  var_raw <- paste0("raw_", prog_col)
  var_final <- paste0("ben_", gsub("mprog_", "", prog_col))

  # Get IDs of anyone who ever reported this benefit
  ever_beneficiary <- df %>%
    filter(!!sym(var_raw) == 1) %>%
    pull(ID) %>%
    unique()

  # Create final variable
  df <- df %>%
    mutate(
      !!var_final := case_when(
        # If selected "none" in this wave, not a beneficiary
        selected_none == 1 ~ 0,
        # If ever reported this benefit, code as beneficiary
        ID %in% ever_beneficiary ~ 1,
        # Otherwise, not a beneficiary
        TRUE ~ 0
      )
    )

  return(df)
}

# Apply to each fixed-date benefit
for (prog in fixed_benefits) {
  df <- create_beneficiary_var(df, prog)
}

# Create "any fixed benefit" indicator
df <- df %>%
  mutate(
    ben_any_fixed = pmax(ben_childbnft, ben_socasst, ben_basinc,
                         ben_cfincsupp, ben_housingbnft, ben_retpen,
                         ben_dispen, na.rm = TRUE)
  )

# Verify
cat("=== BENEFICIARY STATUS SUMMARY ===\n\n")
ben_vars <- c("ben_childbnft", "ben_socasst", "ben_basinc", "ben_cfincsupp",
              "ben_housingbnft", "ben_retpen", "ben_dispen", "ben_any_fixed")

for (v in ben_vars) {
  cat(v, ":\n")
  print(table(df[[v]], useNA = "ifany"))
  cat("\n")
}
```

## Validate Beneficiary Coding

```{r validate-beneficiary}
# Check that the panel propagation worked correctly
# Find someone who reported a benefit in one wave but not another

cat("=== VALIDATION: Panel propagation ===\n\n")

# Example: Find people who reported child benefit in some waves but not all
child_check <- df %>%
  group_by(ID) %>%
  filter(n() > 1) %>%  # multi-wave respondents
  summarise(
    n_waves = n(),
    raw_sum = sum(raw_mprog_childbnft),
    ben_sum = sum(ben_childbnft),
    none_sum = sum(selected_none),
    .groups = "drop"
  ) %>%
  filter(raw_sum > 0 & raw_sum < n_waves)  # reported in some but not all waves

cat("People who reported Child Benefit in some waves but not all:", nrow(child_check), "\n")
cat("Sample:\n")
print(head(child_check, 5))

# Show actual data for one of these people
if (nrow(child_check) > 0) {
  example_id <- child_check$ID[1]
  cat("\nExample person:", example_id, "\n")
  df %>%
    filter(ID == example_id) %>%
    select(ID, wave, raw_mprog_childbnft, ben_childbnft, selected_none) %>%
    print()
}
```

## Summary Statistics for Treatment Variables

```{r treatment-summary}
cat("=== TREATMENT VARIABLE SUMMARY ===\n\n")

# Beneficiary rates
cat("Beneficiary rates (N observations):\n")
df %>%
  summarise(
    across(starts_with("ben_"), ~sum(. == 1, na.rm = TRUE))
  ) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "N_Beneficiary") %>%
  mutate(Pct = round(100 * N_Beneficiary / nrow(df), 1)) %>%
  kable()

# Proximity summary by beneficiary status
cat("\n\nProximity to Child Benefit payment (20th) by beneficiary status:\n")
df %>%
  group_by(ben_childbnft) %>%
  summarise(
    n = n(),
    mean_days_since = mean(prox_child_since, na.rm = TRUE),
    mean_days_until = mean(prox_child_until, na.rm = TRUE),
    mean_circular = mean(prox_child_circ, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  kable(digits = 2)
```

# Panel Fixed Effects Analysis

## Setup

```{r panel-setup}
pacman::p_load(fixest, modelsummary)

# Create parent indicator (has minor children in household)
df <- df %>%
  mutate(
    childminor_num = case_when(
      childminor %in% c("0") ~ 0,
      childminor %in% c("1", "2", "3", "4", "5", "6", "More than 6") ~ 1,
      TRUE ~ NA_real_
    ),
    is_parent = childminor_num == 1
  )

cat("Parent status:\n")
table(df$is_parent, useNA = "ifany")
```

## Trust in Quebec Government

### Full Sample

```{r trust-qc-full}
# All
m_all <- feols(trust_qc ~ prox_child_circ | ID, data = df)

# Child benefit recipients only
m_ccb <- feols(trust_qc ~ prox_child_circ | ID,
               data = df %>% filter(ben_childbnft == 1))

# Non-child-benefit recipients only
m_noccb <- feols(trust_qc ~ prox_child_circ | ID,
                 data = df %>% filter(ben_childbnft == 0))

# Immigrants - All
m_imm_all <- feols(trust_qc ~ prox_child_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Child benefit recipients
m_imm_ccb <- feols(trust_qc ~ prox_child_circ | ID,
                   data = df %>% filter(immigrant == TRUE, ben_childbnft == 1))

# Immigrants - Non-child-benefit recipients
m_imm_noccb <- feols(trust_qc ~ prox_child_circ | ID,
                     data = df %>% filter(immigrant == TRUE, ben_childbnft == 0))

# Non-immigrants - All
m_nat_all <- feols(trust_qc ~ prox_child_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Child benefit recipients
m_nat_ccb <- feols(trust_qc ~ prox_child_circ | ID,
                   data = df %>% filter(immigrant == FALSE, ben_childbnft == 1))

# Non-immigrants - Non-child-benefit recipients
m_nat_noccb <- feols(trust_qc ~ prox_child_circ | ID,
                     data = df %>% filter(immigrant == FALSE, ben_childbnft == 0))

modelsummary(
  list("All" = m_all, "CCB" = m_ccb, "No CCB" = m_noccb,
       "Imm" = m_imm_all, "Imm+CCB" = m_imm_ccb, "Imm+NoCCB" = m_imm_noccb,
       "Nat" = m_nat_all, "Nat+CCB" = m_nat_ccb, "Nat+NoCCB" = m_nat_noccb),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Trust in Quebec Government ~ Proximity to 20th (Full Sample)"
)
```

### Parents Only

```{r trust-qc-parents}
# Parents - All
m_par_all <- feols(trust_qc ~ prox_child_circ | ID,
                   data = df %>% filter(is_parent == TRUE))

# Parents - Child benefit recipients
m_par_ccb <- feols(trust_qc ~ prox_child_circ | ID,
                   data = df %>% filter(is_parent == TRUE, ben_childbnft == 1))

# Parents - Non-child-benefit recipients
m_par_noccb <- feols(trust_qc ~ prox_child_circ | ID,
                     data = df %>% filter(is_parent == TRUE, ben_childbnft == 0))

# Parents + Immigrants - All
m_par_imm_all <- feols(trust_qc ~ prox_child_circ | ID,
                       data = df %>% filter(is_parent == TRUE, immigrant == TRUE))

# Parents + Immigrants - Child benefit recipients
m_par_imm_ccb <- feols(trust_qc ~ prox_child_circ | ID,
                       data = df %>% filter(is_parent == TRUE, immigrant == TRUE, ben_childbnft == 1))

# Parents + Immigrants - Non-child-benefit recipients
m_par_imm_noccb <- feols(trust_qc ~ prox_child_circ | ID,
                         data = df %>% filter(is_parent == TRUE, immigrant == TRUE, ben_childbnft == 0))

# Parents + Non-immigrants - All
m_par_nat_all <- feols(trust_qc ~ prox_child_circ | ID,
                       data = df %>% filter(is_parent == TRUE, immigrant == FALSE))

# Parents + Non-immigrants - Child benefit recipients
m_par_nat_ccb <- feols(trust_qc ~ prox_child_circ | ID,
                       data = df %>% filter(is_parent == TRUE, immigrant == FALSE, ben_childbnft == 1))

# Parents + Non-immigrants - Non-child-benefit recipients
m_par_nat_noccb <- feols(trust_qc ~ prox_child_circ | ID,
                         data = df %>% filter(is_parent == TRUE, immigrant == FALSE, ben_childbnft == 0))

modelsummary(
  list("All" = m_par_all, "CCB" = m_par_ccb, "No CCB" = m_par_noccb,
       "Imm" = m_par_imm_all, "Imm+CCB" = m_par_imm_ccb, "Imm+NoCCB" = m_par_imm_noccb,
       "Nat" = m_par_nat_all, "Nat+CCB" = m_par_nat_ccb, "Nat+NoCCB" = m_par_nat_noccb),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Trust in Quebec Government ~ Proximity to 20th (Parents Only)"
)
```

## Trust in Canadian Government

### Full Sample

```{r trust-can-full}
# All
m_all <- feols(trust_can ~ prox_child_circ | ID, data = df)

# Child benefit recipients only
m_ccb <- feols(trust_can ~ prox_child_circ | ID,
               data = df %>% filter(ben_childbnft == 1))

# Non-child-benefit recipients only
m_noccb <- feols(trust_can ~ prox_child_circ | ID,
                 data = df %>% filter(ben_childbnft == 0))

# Immigrants - All
m_imm_all <- feols(trust_can ~ prox_child_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Child benefit recipients
m_imm_ccb <- feols(trust_can ~ prox_child_circ | ID,
                   data = df %>% filter(immigrant == TRUE, ben_childbnft == 1))

# Immigrants - Non-child-benefit recipients
m_imm_noccb <- feols(trust_can ~ prox_child_circ | ID,
                     data = df %>% filter(immigrant == TRUE, ben_childbnft == 0))

# Non-immigrants - All
m_nat_all <- feols(trust_can ~ prox_child_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Child benefit recipients
m_nat_ccb <- feols(trust_can ~ prox_child_circ | ID,
                   data = df %>% filter(immigrant == FALSE, ben_childbnft == 1))

# Non-immigrants - Non-child-benefit recipients
m_nat_noccb <- feols(trust_can ~ prox_child_circ | ID,
                     data = df %>% filter(immigrant == FALSE, ben_childbnft == 0))

modelsummary(
  list("All" = m_all, "CCB" = m_ccb, "No CCB" = m_noccb,
       "Imm" = m_imm_all, "Imm+CCB" = m_imm_ccb, "Imm+NoCCB" = m_imm_noccb,
       "Nat" = m_nat_all, "Nat+CCB" = m_nat_ccb, "Nat+NoCCB" = m_nat_noccb),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Trust in Canadian Government ~ Proximity to 20th (Full Sample, Waves 2-3 only)"
)
```

### Parents Only

```{r trust-can-parents}
# Parents - All
m_par_all <- feols(trust_can ~ prox_child_circ | ID,
                   data = df %>% filter(is_parent == TRUE))

# Parents - Child benefit recipients
m_par_ccb <- feols(trust_can ~ prox_child_circ | ID,
                   data = df %>% filter(is_parent == TRUE, ben_childbnft == 1))

# Parents - Non-child-benefit recipients
m_par_noccb <- feols(trust_can ~ prox_child_circ | ID,
                     data = df %>% filter(is_parent == TRUE, ben_childbnft == 0))

# Parents + Immigrants - All
m_par_imm_all <- feols(trust_can ~ prox_child_circ | ID,
                       data = df %>% filter(is_parent == TRUE, immigrant == TRUE))

# Parents + Immigrants - Child benefit recipients
m_par_imm_ccb <- feols(trust_can ~ prox_child_circ | ID,
                       data = df %>% filter(is_parent == TRUE, immigrant == TRUE, ben_childbnft == 1))

# Parents + Immigrants - Non-child-benefit recipients
m_par_imm_noccb <- feols(trust_can ~ prox_child_circ | ID,
                         data = df %>% filter(is_parent == TRUE, immigrant == TRUE, ben_childbnft == 0))

# Parents + Non-immigrants - All
m_par_nat_all <- feols(trust_can ~ prox_child_circ | ID,
                       data = df %>% filter(is_parent == TRUE, immigrant == FALSE))

# Parents + Non-immigrants - Child benefit recipients
m_par_nat_ccb <- feols(trust_can ~ prox_child_circ | ID,
                       data = df %>% filter(is_parent == TRUE, immigrant == FALSE, ben_childbnft == 1))

# Parents + Non-immigrants - Non-child-benefit recipients
m_par_nat_noccb <- feols(trust_can ~ prox_child_circ | ID,
                         data = df %>% filter(is_parent == TRUE, immigrant == FALSE, ben_childbnft == 0))

modelsummary(
  list("All" = m_par_all, "CCB" = m_par_ccb, "No CCB" = m_par_noccb,
       "Imm" = m_par_imm_all, "Imm+CCB" = m_par_imm_ccb, "Imm+NoCCB" = m_par_imm_noccb,
       "Nat" = m_par_nat_all, "Nat+CCB" = m_par_nat_ccb, "Nat+NoCCB" = m_par_nat_noccb),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Trust in Canadian Government ~ Proximity to 20th (Parents Only, Waves 2-3 only)"
)
```

## Attachment to Quebec

### Full Sample

```{r attachment-qc-full}
# All
m_all <- feols(attachment_qc ~ prox_child_circ | ID, data = df)

# Child benefit recipients only
m_ccb <- feols(attachment_qc ~ prox_child_circ | ID,
               data = df %>% filter(ben_childbnft == 1))

# Non-child-benefit recipients only
m_noccb <- feols(attachment_qc ~ prox_child_circ | ID,
                 data = df %>% filter(ben_childbnft == 0))

# Immigrants - All
m_imm_all <- feols(attachment_qc ~ prox_child_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Child benefit recipients
m_imm_ccb <- feols(attachment_qc ~ prox_child_circ | ID,
                   data = df %>% filter(immigrant == TRUE, ben_childbnft == 1))

# Immigrants - Non-child-benefit recipients
m_imm_noccb <- feols(attachment_qc ~ prox_child_circ | ID,
                     data = df %>% filter(immigrant == TRUE, ben_childbnft == 0))

# Non-immigrants - All
m_nat_all <- feols(attachment_qc ~ prox_child_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Child benefit recipients
m_nat_ccb <- feols(attachment_qc ~ prox_child_circ | ID,
                   data = df %>% filter(immigrant == FALSE, ben_childbnft == 1))

# Non-immigrants - Non-child-benefit recipients
m_nat_noccb <- feols(attachment_qc ~ prox_child_circ | ID,
                     data = df %>% filter(immigrant == FALSE, ben_childbnft == 0))

modelsummary(
  list("All" = m_all, "CCB" = m_ccb, "No CCB" = m_noccb,
       "Imm" = m_imm_all, "Imm+CCB" = m_imm_ccb, "Imm+NoCCB" = m_imm_noccb,
       "Nat" = m_nat_all, "Nat+CCB" = m_nat_ccb, "Nat+NoCCB" = m_nat_noccb),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Attachment to Quebec ~ Proximity to 20th (Full Sample)"
)
```

### Parents Only

```{r attachment-qc-parents}
# Parents - All
m_par_all <- feols(attachment_qc ~ prox_child_circ | ID,
                   data = df %>% filter(is_parent == TRUE))

# Parents - Child benefit recipients
m_par_ccb <- feols(attachment_qc ~ prox_child_circ | ID,
                   data = df %>% filter(is_parent == TRUE, ben_childbnft == 1))

# Parents - Non-child-benefit recipients
m_par_noccb <- feols(attachment_qc ~ prox_child_circ | ID,
                     data = df %>% filter(is_parent == TRUE, ben_childbnft == 0))

# Parents + Immigrants - All
m_par_imm_all <- feols(attachment_qc ~ prox_child_circ | ID,
                       data = df %>% filter(is_parent == TRUE, immigrant == TRUE))

# Parents + Immigrants - Child benefit recipients
m_par_imm_ccb <- feols(attachment_qc ~ prox_child_circ | ID,
                       data = df %>% filter(is_parent == TRUE, immigrant == TRUE, ben_childbnft == 1))

# Parents + Immigrants - Non-child-benefit recipients
m_par_imm_noccb <- feols(attachment_qc ~ prox_child_circ | ID,
                         data = df %>% filter(is_parent == TRUE, immigrant == TRUE, ben_childbnft == 0))

# Parents + Non-immigrants - All
m_par_nat_all <- feols(attachment_qc ~ prox_child_circ | ID,
                       data = df %>% filter(is_parent == TRUE, immigrant == FALSE))

# Parents + Non-immigrants - Child benefit recipients
m_par_nat_ccb <- feols(attachment_qc ~ prox_child_circ | ID,
                       data = df %>% filter(is_parent == TRUE, immigrant == FALSE, ben_childbnft == 1))

# Parents + Non-immigrants - Non-child-benefit recipients
m_par_nat_noccb <- feols(attachment_qc ~ prox_child_circ | ID,
                         data = df %>% filter(is_parent == TRUE, immigrant == FALSE, ben_childbnft == 0))

modelsummary(
  list("All" = m_par_all, "CCB" = m_par_ccb, "No CCB" = m_par_noccb,
       "Imm" = m_par_imm_all, "Imm+CCB" = m_par_imm_ccb, "Imm+NoCCB" = m_par_imm_noccb,
       "Nat" = m_par_nat_all, "Nat+CCB" = m_par_nat_ccb, "Nat+NoCCB" = m_par_nat_noccb),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Attachment to Quebec ~ Proximity to 20th (Parents Only)"
)
```

## Financial Satisfaction

### Full Sample

```{r financial-satisf-full}
# All
m_all <- feols(financial_satisf ~ prox_child_circ | ID, data = df)

# Child benefit recipients only
m_ccb <- feols(financial_satisf ~ prox_child_circ | ID,
               data = df %>% filter(ben_childbnft == 1))

# Non-child-benefit recipients only
m_noccb <- feols(financial_satisf ~ prox_child_circ | ID,
                 data = df %>% filter(ben_childbnft == 0))

# Immigrants - All
m_imm_all <- feols(financial_satisf ~ prox_child_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Child benefit recipients
m_imm_ccb <- feols(financial_satisf ~ prox_child_circ | ID,
                   data = df %>% filter(immigrant == TRUE, ben_childbnft == 1))

# Immigrants - Non-child-benefit recipients
m_imm_noccb <- feols(financial_satisf ~ prox_child_circ | ID,
                     data = df %>% filter(immigrant == TRUE, ben_childbnft == 0))

# Non-immigrants - All
m_nat_all <- feols(financial_satisf ~ prox_child_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Child benefit recipients
m_nat_ccb <- feols(financial_satisf ~ prox_child_circ | ID,
                   data = df %>% filter(immigrant == FALSE, ben_childbnft == 1))

# Non-immigrants - Non-child-benefit recipients
m_nat_noccb <- feols(financial_satisf ~ prox_child_circ | ID,
                     data = df %>% filter(immigrant == FALSE, ben_childbnft == 0))

modelsummary(
  list("All" = m_all, "CCB" = m_ccb, "No CCB" = m_noccb,
       "Imm" = m_imm_all, "Imm+CCB" = m_imm_ccb, "Imm+NoCCB" = m_imm_noccb,
       "Nat" = m_nat_all, "Nat+CCB" = m_nat_ccb, "Nat+NoCCB" = m_nat_noccb),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Financial Satisfaction ~ Proximity to 20th (Full Sample)"
)
```

### Parents Only

```{r financial-satisf-parents}
# Parents - All
m_par_all <- feols(financial_satisf ~ prox_child_circ | ID,
                   data = df %>% filter(is_parent == TRUE))

# Parents - Child benefit recipients
m_par_ccb <- feols(financial_satisf ~ prox_child_circ | ID,
                   data = df %>% filter(is_parent == TRUE, ben_childbnft == 1))

# Parents - Non-child-benefit recipients
m_par_noccb <- feols(financial_satisf ~ prox_child_circ | ID,
                     data = df %>% filter(is_parent == TRUE, ben_childbnft == 0))

# Parents + Immigrants - All
m_par_imm_all <- feols(financial_satisf ~ prox_child_circ | ID,
                       data = df %>% filter(is_parent == TRUE, immigrant == TRUE))

# Parents + Immigrants - Child benefit recipients
m_par_imm_ccb <- feols(financial_satisf ~ prox_child_circ | ID,
                       data = df %>% filter(is_parent == TRUE, immigrant == TRUE, ben_childbnft == 1))

# Parents + Immigrants - Non-child-benefit recipients
m_par_imm_noccb <- feols(financial_satisf ~ prox_child_circ | ID,
                         data = df %>% filter(is_parent == TRUE, immigrant == TRUE, ben_childbnft == 0))

# Parents + Non-immigrants - All
m_par_nat_all <- feols(financial_satisf ~ prox_child_circ | ID,
                       data = df %>% filter(is_parent == TRUE, immigrant == FALSE))

# Parents + Non-immigrants - Child benefit recipients
m_par_nat_ccb <- feols(financial_satisf ~ prox_child_circ | ID,
                       data = df %>% filter(is_parent == TRUE, immigrant == FALSE, ben_childbnft == 1))

# Parents + Non-immigrants - Non-child-benefit recipients
m_par_nat_noccb <- feols(financial_satisf ~ prox_child_circ | ID,
                         data = df %>% filter(is_parent == TRUE, immigrant == FALSE, ben_childbnft == 0))

modelsummary(
  list("All" = m_par_all, "CCB" = m_par_ccb, "No CCB" = m_par_noccb,
       "Imm" = m_par_imm_all, "Imm+CCB" = m_par_imm_ccb, "Imm+NoCCB" = m_par_imm_noccb,
       "Nat" = m_par_nat_all, "Nat+CCB" = m_par_nat_ccb, "Nat+NoCCB" = m_par_nat_noccb),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Financial Satisfaction ~ Proximity to 20th (Parents Only)"
)
```

# Retirement Pension Analysis (Proximity to 28th)

## Trust in Quebec Government

```{r trust-qc-retpen}
# All
m_all <- feols(trust_qc ~ prox_28_circ | ID, data = df)

# Retirement pension recipients only
m_retpen <- feols(trust_qc ~ prox_28_circ | ID,
                  data = df %>% filter(ben_retpen == 1))

# Non-retirement-pension recipients only
m_noretpen <- feols(trust_qc ~ prox_28_circ | ID,
                    data = df %>% filter(ben_retpen == 0))

# Immigrants - All
m_imm_all <- feols(trust_qc ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Retirement pension recipients
m_imm_retpen <- feols(trust_qc ~ prox_28_circ | ID,
                      data = df %>% filter(immigrant == TRUE, ben_retpen == 1))

# Immigrants - Non-retirement-pension recipients
m_imm_noretpen <- feols(trust_qc ~ prox_28_circ | ID,
                        data = df %>% filter(immigrant == TRUE, ben_retpen == 0))

# Non-immigrants - All
m_nat_all <- feols(trust_qc ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Retirement pension recipients
m_nat_retpen <- feols(trust_qc ~ prox_28_circ | ID,
                      data = df %>% filter(immigrant == FALSE, ben_retpen == 1))

# Non-immigrants - Non-retirement-pension recipients
m_nat_noretpen <- feols(trust_qc ~ prox_28_circ | ID,
                        data = df %>% filter(immigrant == FALSE, ben_retpen == 0))

modelsummary(
  list("All" = m_all, "RetPen" = m_retpen, "No RetPen" = m_noretpen,
       "Imm" = m_imm_all, "Imm+RetPen" = m_imm_retpen, "Imm+NoRetPen" = m_imm_noretpen,
       "Nat" = m_nat_all, "Nat+RetPen" = m_nat_retpen, "Nat+NoRetPen" = m_nat_noretpen),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Trust in Quebec Government ~ Proximity to 28th"
)
```

## Trust in Canadian Government

```{r trust-can-retpen}
# All
m_all <- feols(trust_can ~ prox_28_circ | ID, data = df)

# Retirement pension recipients only
m_retpen <- feols(trust_can ~ prox_28_circ | ID,
                  data = df %>% filter(ben_retpen == 1))

# Non-retirement-pension recipients only
m_noretpen <- feols(trust_can ~ prox_28_circ | ID,
                    data = df %>% filter(ben_retpen == 0))

# Immigrants - All
m_imm_all <- feols(trust_can ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Retirement pension recipients
m_imm_retpen <- feols(trust_can ~ prox_28_circ | ID,
                      data = df %>% filter(immigrant == TRUE, ben_retpen == 1))

# Immigrants - Non-retirement-pension recipients
m_imm_noretpen <- feols(trust_can ~ prox_28_circ | ID,
                        data = df %>% filter(immigrant == TRUE, ben_retpen == 0))

# Non-immigrants - All
m_nat_all <- feols(trust_can ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Retirement pension recipients
m_nat_retpen <- feols(trust_can ~ prox_28_circ | ID,
                      data = df %>% filter(immigrant == FALSE, ben_retpen == 1))

# Non-immigrants - Non-retirement-pension recipients
m_nat_noretpen <- feols(trust_can ~ prox_28_circ | ID,
                        data = df %>% filter(immigrant == FALSE, ben_retpen == 0))

modelsummary(
  list("All" = m_all, "RetPen" = m_retpen, "No RetPen" = m_noretpen,
       "Imm" = m_imm_all, "Imm+RetPen" = m_imm_retpen, "Imm+NoRetPen" = m_imm_noretpen,
       "Nat" = m_nat_all, "Nat+RetPen" = m_nat_retpen, "Nat+NoRetPen" = m_nat_noretpen),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Trust in Canadian Government ~ Proximity to 28th (Waves 2-3 only)"
)
```

## Attachment to Quebec

```{r attachment-qc-retpen}
# All
m_all <- feols(attachment_qc ~ prox_28_circ | ID, data = df)

# Retirement pension recipients only
m_retpen <- feols(attachment_qc ~ prox_28_circ | ID,
                  data = df %>% filter(ben_retpen == 1))

# Non-retirement-pension recipients only
m_noretpen <- feols(attachment_qc ~ prox_28_circ | ID,
                    data = df %>% filter(ben_retpen == 0))

# Immigrants - All
m_imm_all <- feols(attachment_qc ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Retirement pension recipients
m_imm_retpen <- feols(attachment_qc ~ prox_28_circ | ID,
                      data = df %>% filter(immigrant == TRUE, ben_retpen == 1))

# Immigrants - Non-retirement-pension recipients
m_imm_noretpen <- feols(attachment_qc ~ prox_28_circ | ID,
                        data = df %>% filter(immigrant == TRUE, ben_retpen == 0))

# Non-immigrants - All
m_nat_all <- feols(attachment_qc ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Retirement pension recipients
m_nat_retpen <- feols(attachment_qc ~ prox_28_circ | ID,
                      data = df %>% filter(immigrant == FALSE, ben_retpen == 1))

# Non-immigrants - Non-retirement-pension recipients
m_nat_noretpen <- feols(attachment_qc ~ prox_28_circ | ID,
                        data = df %>% filter(immigrant == FALSE, ben_retpen == 0))

modelsummary(
  list("All" = m_all, "RetPen" = m_retpen, "No RetPen" = m_noretpen,
       "Imm" = m_imm_all, "Imm+RetPen" = m_imm_retpen, "Imm+NoRetPen" = m_imm_noretpen,
       "Nat" = m_nat_all, "Nat+RetPen" = m_nat_retpen, "Nat+NoRetPen" = m_nat_noretpen),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Attachment to Quebec ~ Proximity to 28th"
)
```

## Financial Satisfaction

```{r financial-satisf-retpen}
# All
m_all <- feols(financial_satisf ~ prox_28_circ | ID, data = df)

# Retirement pension recipients only
m_retpen <- feols(financial_satisf ~ prox_28_circ | ID,
                  data = df %>% filter(ben_retpen == 1))

# Non-retirement-pension recipients only
m_noretpen <- feols(financial_satisf ~ prox_28_circ | ID,
                    data = df %>% filter(ben_retpen == 0))

# Immigrants - All
m_imm_all <- feols(financial_satisf ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Retirement pension recipients
m_imm_retpen <- feols(financial_satisf ~ prox_28_circ | ID,
                      data = df %>% filter(immigrant == TRUE, ben_retpen == 1))

# Immigrants - Non-retirement-pension recipients
m_imm_noretpen <- feols(financial_satisf ~ prox_28_circ | ID,
                        data = df %>% filter(immigrant == TRUE, ben_retpen == 0))

# Non-immigrants - All
m_nat_all <- feols(financial_satisf ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Retirement pension recipients
m_nat_retpen <- feols(financial_satisf ~ prox_28_circ | ID,
                      data = df %>% filter(immigrant == FALSE, ben_retpen == 1))

# Non-immigrants - Non-retirement-pension recipients
m_nat_noretpen <- feols(financial_satisf ~ prox_28_circ | ID,
                        data = df %>% filter(immigrant == FALSE, ben_retpen == 0))

modelsummary(
  list("All" = m_all, "RetPen" = m_retpen, "No RetPen" = m_noretpen,
       "Imm" = m_imm_all, "Imm+RetPen" = m_imm_retpen, "Imm+NoRetPen" = m_imm_noretpen,
       "Nat" = m_nat_all, "Nat+RetPen" = m_nat_retpen, "Nat+NoRetPen" = m_nat_noretpen),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Financial Satisfaction ~ Proximity to 28th"
)
```

# Housing Benefit Analysis (Proximity to 28th)

## Trust in Quebec Government

```{r trust-qc-housing}
# All
m_all <- feols(trust_qc ~ prox_28_circ | ID, data = df)

# Housing benefit recipients only
m_hous <- feols(trust_qc ~ prox_28_circ | ID,
                data = df %>% filter(ben_housingbnft == 1))

# Non-housing-benefit recipients only
m_nohous <- feols(trust_qc ~ prox_28_circ | ID,
                  data = df %>% filter(ben_housingbnft == 0))

# Immigrants - All
m_imm_all <- feols(trust_qc ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Housing benefit recipients
m_imm_hous <- feols(trust_qc ~ prox_28_circ | ID,
                    data = df %>% filter(immigrant == TRUE, ben_housingbnft == 1))

# Immigrants - Non-housing-benefit recipients
m_imm_nohous <- feols(trust_qc ~ prox_28_circ | ID,
                      data = df %>% filter(immigrant == TRUE, ben_housingbnft == 0))

# Non-immigrants - All
m_nat_all <- feols(trust_qc ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Housing benefit recipients
m_nat_hous <- feols(trust_qc ~ prox_28_circ | ID,
                    data = df %>% filter(immigrant == FALSE, ben_housingbnft == 1))

# Non-immigrants - Non-housing-benefit recipients
m_nat_nohous <- feols(trust_qc ~ prox_28_circ | ID,
                      data = df %>% filter(immigrant == FALSE, ben_housingbnft == 0))

modelsummary(
  list("All" = m_all, "Hous" = m_hous, "No Hous" = m_nohous,
       "Imm" = m_imm_all, "Imm+Hous" = m_imm_hous, "Imm+NoHous" = m_imm_nohous,
       "Nat" = m_nat_all, "Nat+Hous" = m_nat_hous, "Nat+NoHous" = m_nat_nohous),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Trust in Quebec Government ~ Proximity to 28th (Housing Benefit)"
)
```

## Trust in Canadian Government

```{r trust-can-housing}
# All
m_all <- feols(trust_can ~ prox_28_circ | ID, data = df)

# Housing benefit recipients only
m_hous <- feols(trust_can ~ prox_28_circ | ID,
                data = df %>% filter(ben_housingbnft == 1))

# Non-housing-benefit recipients only
m_nohous <- feols(trust_can ~ prox_28_circ | ID,
                  data = df %>% filter(ben_housingbnft == 0))

# Immigrants - All
m_imm_all <- feols(trust_can ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Housing benefit recipients
m_imm_hous <- feols(trust_can ~ prox_28_circ | ID,
                    data = df %>% filter(immigrant == TRUE, ben_housingbnft == 1))

# Immigrants - Non-housing-benefit recipients
m_imm_nohous <- feols(trust_can ~ prox_28_circ | ID,
                      data = df %>% filter(immigrant == TRUE, ben_housingbnft == 0))

# Non-immigrants - All
m_nat_all <- feols(trust_can ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Housing benefit recipients
m_nat_hous <- feols(trust_can ~ prox_28_circ | ID,
                    data = df %>% filter(immigrant == FALSE, ben_housingbnft == 1))

# Non-immigrants - Non-housing-benefit recipients
m_nat_nohous <- feols(trust_can ~ prox_28_circ | ID,
                      data = df %>% filter(immigrant == FALSE, ben_housingbnft == 0))

modelsummary(
  list("All" = m_all, "Hous" = m_hous, "No Hous" = m_nohous,
       "Imm" = m_imm_all, "Imm+Hous" = m_imm_hous, "Imm+NoHous" = m_imm_nohous,
       "Nat" = m_nat_all, "Nat+Hous" = m_nat_hous, "Nat+NoHous" = m_nat_nohous),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Trust in Canadian Government ~ Proximity to 28th (Housing Benefit, Waves 2-3 only)"
)
```

## Attachment to Quebec

```{r attachment-qc-housing}
# All
m_all <- feols(attachment_qc ~ prox_28_circ | ID, data = df)

# Housing benefit recipients only
m_hous <- feols(attachment_qc ~ prox_28_circ | ID,
                data = df %>% filter(ben_housingbnft == 1))

# Non-housing-benefit recipients only
m_nohous <- feols(attachment_qc ~ prox_28_circ | ID,
                  data = df %>% filter(ben_housingbnft == 0))

# Immigrants - All
m_imm_all <- feols(attachment_qc ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Housing benefit recipients
m_imm_hous <- feols(attachment_qc ~ prox_28_circ | ID,
                    data = df %>% filter(immigrant == TRUE, ben_housingbnft == 1))

# Immigrants - Non-housing-benefit recipients
m_imm_nohous <- feols(attachment_qc ~ prox_28_circ | ID,
                      data = df %>% filter(immigrant == TRUE, ben_housingbnft == 0))

# Non-immigrants - All
m_nat_all <- feols(attachment_qc ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Housing benefit recipients
m_nat_hous <- feols(attachment_qc ~ prox_28_circ | ID,
                    data = df %>% filter(immigrant == FALSE, ben_housingbnft == 1))

# Non-immigrants - Non-housing-benefit recipients
m_nat_nohous <- feols(attachment_qc ~ prox_28_circ | ID,
                      data = df %>% filter(immigrant == FALSE, ben_housingbnft == 0))

modelsummary(
  list("All" = m_all, "Hous" = m_hous, "No Hous" = m_nohous,
       "Imm" = m_imm_all, "Imm+Hous" = m_imm_hous, "Imm+NoHous" = m_imm_nohous,
       "Nat" = m_nat_all, "Nat+Hous" = m_nat_hous, "Nat+NoHous" = m_nat_nohous),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Attachment to Quebec ~ Proximity to 28th (Housing Benefit)"
)
```

## Financial Satisfaction

```{r financial-satisf-housing}
# All
m_all <- feols(financial_satisf ~ prox_28_circ | ID, data = df)

# Housing benefit recipients only
m_hous <- feols(financial_satisf ~ prox_28_circ | ID,
                data = df %>% filter(ben_housingbnft == 1))

# Non-housing-benefit recipients only
m_nohous <- feols(financial_satisf ~ prox_28_circ | ID,
                  data = df %>% filter(ben_housingbnft == 0))

# Immigrants - All
m_imm_all <- feols(financial_satisf ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Housing benefit recipients
m_imm_hous <- feols(financial_satisf ~ prox_28_circ | ID,
                    data = df %>% filter(immigrant == TRUE, ben_housingbnft == 1))

# Immigrants - Non-housing-benefit recipients
m_imm_nohous <- feols(financial_satisf ~ prox_28_circ | ID,
                      data = df %>% filter(immigrant == TRUE, ben_housingbnft == 0))

# Non-immigrants - All
m_nat_all <- feols(financial_satisf ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Housing benefit recipients
m_nat_hous <- feols(financial_satisf ~ prox_28_circ | ID,
                    data = df %>% filter(immigrant == FALSE, ben_housingbnft == 1))

# Non-immigrants - Non-housing-benefit recipients
m_nat_nohous <- feols(financial_satisf ~ prox_28_circ | ID,
                      data = df %>% filter(immigrant == FALSE, ben_housingbnft == 0))

modelsummary(
  list("All" = m_all, "Hous" = m_hous, "No Hous" = m_nohous,
       "Imm" = m_imm_all, "Imm+Hous" = m_imm_hous, "Imm+NoHous" = m_imm_nohous,
       "Nat" = m_nat_all, "Nat+Hous" = m_nat_hous, "Nat+NoHous" = m_nat_nohous),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Financial Satisfaction ~ Proximity to 28th (Housing Benefit)"
)
```

# Social Assistance Analysis (Proximity to 1st)

## Trust in Quebec Government

```{r trust-qc-socasst}
# All
m_all <- feols(trust_qc ~ prox_first_circ | ID, data = df)

# Social assistance recipients only
m_soc <- feols(trust_qc ~ prox_first_circ | ID,
               data = df %>% filter(ben_socasst == 1))

# Non-social-assistance recipients only
m_nosoc <- feols(trust_qc ~ prox_first_circ | ID,
                 data = df %>% filter(ben_socasst == 0))

# Immigrants - All
m_imm_all <- feols(trust_qc ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Social assistance recipients
m_imm_soc <- feols(trust_qc ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == TRUE, ben_socasst == 1))

# Immigrants - Non-social-assistance recipients
m_imm_nosoc <- feols(trust_qc ~ prox_first_circ | ID,
                     data = df %>% filter(immigrant == TRUE, ben_socasst == 0))

# Non-immigrants - All
m_nat_all <- feols(trust_qc ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Social assistance recipients
m_nat_soc <- feols(trust_qc ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == FALSE, ben_socasst == 1))

# Non-immigrants - Non-social-assistance recipients
m_nat_nosoc <- feols(trust_qc ~ prox_first_circ | ID,
                     data = df %>% filter(immigrant == FALSE, ben_socasst == 0))

modelsummary(
  list("All" = m_all, "SocAsst" = m_soc, "No SocAsst" = m_nosoc,
       "Imm" = m_imm_all, "Imm+Soc" = m_imm_soc, "Imm+NoSoc" = m_imm_nosoc,
       "Nat" = m_nat_all, "Nat+Soc" = m_nat_soc, "Nat+NoSoc" = m_nat_nosoc),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Trust in Quebec Government ~ Proximity to 1st (Social Assistance)"
)
```

## Trust in Canadian Government

```{r trust-can-socasst}
# All
m_all <- feols(trust_can ~ prox_first_circ | ID, data = df)

# Social assistance recipients only
m_soc <- feols(trust_can ~ prox_first_circ | ID,
               data = df %>% filter(ben_socasst == 1))

# Non-social-assistance recipients only
m_nosoc <- feols(trust_can ~ prox_first_circ | ID,
                 data = df %>% filter(ben_socasst == 0))

# Immigrants - All
m_imm_all <- feols(trust_can ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Social assistance recipients
m_imm_soc <- feols(trust_can ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == TRUE, ben_socasst == 1))

# Immigrants - Non-social-assistance recipients
m_imm_nosoc <- feols(trust_can ~ prox_first_circ | ID,
                     data = df %>% filter(immigrant == TRUE, ben_socasst == 0))

# Non-immigrants - All
m_nat_all <- feols(trust_can ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Social assistance recipients
m_nat_soc <- feols(trust_can ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == FALSE, ben_socasst == 1))

# Non-immigrants - Non-social-assistance recipients
m_nat_nosoc <- feols(trust_can ~ prox_first_circ | ID,
                     data = df %>% filter(immigrant == FALSE, ben_socasst == 0))

modelsummary(
  list("All" = m_all, "SocAsst" = m_soc, "No SocAsst" = m_nosoc,
       "Imm" = m_imm_all, "Imm+Soc" = m_imm_soc, "Imm+NoSoc" = m_imm_nosoc,
       "Nat" = m_nat_all, "Nat+Soc" = m_nat_soc, "Nat+NoSoc" = m_nat_nosoc),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Trust in Canadian Government ~ Proximity to 1st (Social Assistance, Waves 2-3 only)"
)
```

## Attachment to Quebec

```{r attachment-qc-socasst}
# All
m_all <- feols(attachment_qc ~ prox_first_circ | ID, data = df)

# Social assistance recipients only
m_soc <- feols(attachment_qc ~ prox_first_circ | ID,
               data = df %>% filter(ben_socasst == 1))

# Non-social-assistance recipients only
m_nosoc <- feols(attachment_qc ~ prox_first_circ | ID,
                 data = df %>% filter(ben_socasst == 0))

# Immigrants - All
m_imm_all <- feols(attachment_qc ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Social assistance recipients
m_imm_soc <- feols(attachment_qc ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == TRUE, ben_socasst == 1))

# Immigrants - Non-social-assistance recipients
m_imm_nosoc <- feols(attachment_qc ~ prox_first_circ | ID,
                     data = df %>% filter(immigrant == TRUE, ben_socasst == 0))

# Non-immigrants - All
m_nat_all <- feols(attachment_qc ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Social assistance recipients
m_nat_soc <- feols(attachment_qc ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == FALSE, ben_socasst == 1))

# Non-immigrants - Non-social-assistance recipients
m_nat_nosoc <- feols(attachment_qc ~ prox_first_circ | ID,
                     data = df %>% filter(immigrant == FALSE, ben_socasst == 0))

modelsummary(
  list("All" = m_all, "SocAsst" = m_soc, "No SocAsst" = m_nosoc,
       "Imm" = m_imm_all, "Imm+Soc" = m_imm_soc, "Imm+NoSoc" = m_imm_nosoc,
       "Nat" = m_nat_all, "Nat+Soc" = m_nat_soc, "Nat+NoSoc" = m_nat_nosoc),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Attachment to Quebec ~ Proximity to 1st (Social Assistance)"
)
```

## Financial Satisfaction

```{r financial-satisf-socasst}
# All
m_all <- feols(financial_satisf ~ prox_first_circ | ID, data = df)

# Social assistance recipients only
m_soc <- feols(financial_satisf ~ prox_first_circ | ID,
               data = df %>% filter(ben_socasst == 1))

# Non-social-assistance recipients only
m_nosoc <- feols(financial_satisf ~ prox_first_circ | ID,
                 data = df %>% filter(ben_socasst == 0))

# Immigrants - All
m_imm_all <- feols(financial_satisf ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Social assistance recipients
m_imm_soc <- feols(financial_satisf ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == TRUE, ben_socasst == 1))

# Immigrants - Non-social-assistance recipients
m_imm_nosoc <- feols(financial_satisf ~ prox_first_circ | ID,
                     data = df %>% filter(immigrant == TRUE, ben_socasst == 0))

# Non-immigrants - All
m_nat_all <- feols(financial_satisf ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Social assistance recipients
m_nat_soc <- feols(financial_satisf ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == FALSE, ben_socasst == 1))

# Non-immigrants - Non-social-assistance recipients
m_nat_nosoc <- feols(financial_satisf ~ prox_first_circ | ID,
                     data = df %>% filter(immigrant == FALSE, ben_socasst == 0))

modelsummary(
  list("All" = m_all, "SocAsst" = m_soc, "No SocAsst" = m_nosoc,
       "Imm" = m_imm_all, "Imm+Soc" = m_imm_soc, "Imm+NoSoc" = m_imm_nosoc,
       "Nat" = m_nat_all, "Nat+Soc" = m_nat_soc, "Nat+NoSoc" = m_nat_nosoc),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Financial Satisfaction ~ Proximity to 1st (Social Assistance)"
)
```

# Basic Income Analysis (Proximity to 1st)

## Trust in Quebec Government

```{r trust-qc-basinc}
# All
m_all <- feols(trust_qc ~ prox_first_circ | ID, data = df)

# Basic income recipients only
m_bas <- feols(trust_qc ~ prox_first_circ | ID,
               data = df %>% filter(ben_basinc == 1))

# Non-basic-income recipients only
m_nobas <- feols(trust_qc ~ prox_first_circ | ID,
                 data = df %>% filter(ben_basinc == 0))

# Immigrants - All
m_imm_all <- feols(trust_qc ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Basic income recipients
m_imm_bas <- feols(trust_qc ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == TRUE, ben_basinc == 1))

# Immigrants - Non-basic-income recipients
m_imm_nobas <- feols(trust_qc ~ prox_first_circ | ID,
                     data = df %>% filter(immigrant == TRUE, ben_basinc == 0))

# Non-immigrants - All
m_nat_all <- feols(trust_qc ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Basic income recipients
m_nat_bas <- feols(trust_qc ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == FALSE, ben_basinc == 1))

# Non-immigrants - Non-basic-income recipients
m_nat_nobas <- feols(trust_qc ~ prox_first_circ | ID,
                     data = df %>% filter(immigrant == FALSE, ben_basinc == 0))

modelsummary(
  list("All" = m_all, "BasInc" = m_bas, "No BasInc" = m_nobas,
       "Imm" = m_imm_all, "Imm+Bas" = m_imm_bas, "Imm+NoBas" = m_imm_nobas,
       "Nat" = m_nat_all, "Nat+Bas" = m_nat_bas, "Nat+NoBas" = m_nat_nobas),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Trust in Quebec Government ~ Proximity to 1st (Basic Income)"
)
```

## Trust in Canadian Government

```{r trust-can-basinc}
# All
m_all <- feols(trust_can ~ prox_first_circ | ID, data = df)

# Basic income recipients only
m_bas <- feols(trust_can ~ prox_first_circ | ID,
               data = df %>% filter(ben_basinc == 1))

# Non-basic-income recipients only
m_nobas <- feols(trust_can ~ prox_first_circ | ID,
                 data = df %>% filter(ben_basinc == 0))

# Immigrants - All
m_imm_all <- feols(trust_can ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Basic income recipients
m_imm_bas <- feols(trust_can ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == TRUE, ben_basinc == 1))

# Immigrants - Non-basic-income recipients
m_imm_nobas <- feols(trust_can ~ prox_first_circ | ID,
                     data = df %>% filter(immigrant == TRUE, ben_basinc == 0))

# Non-immigrants - All
m_nat_all <- feols(trust_can ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Basic income recipients
m_nat_bas <- feols(trust_can ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == FALSE, ben_basinc == 1))

# Non-immigrants - Non-basic-income recipients
m_nat_nobas <- feols(trust_can ~ prox_first_circ | ID,
                     data = df %>% filter(immigrant == FALSE, ben_basinc == 0))

modelsummary(
  list("All" = m_all, "BasInc" = m_bas, "No BasInc" = m_nobas,
       "Imm" = m_imm_all, "Imm+Bas" = m_imm_bas, "Imm+NoBas" = m_imm_nobas,
       "Nat" = m_nat_all, "Nat+Bas" = m_nat_bas, "Nat+NoBas" = m_nat_nobas),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Trust in Canadian Government ~ Proximity to 1st (Basic Income, Waves 2-3 only)"
)
```

## Attachment to Quebec

```{r attachment-qc-basinc}
# All
m_all <- feols(attachment_qc ~ prox_first_circ | ID, data = df)

# Basic income recipients only
m_bas <- feols(attachment_qc ~ prox_first_circ | ID,
               data = df %>% filter(ben_basinc == 1))

# Non-basic-income recipients only
m_nobas <- feols(attachment_qc ~ prox_first_circ | ID,
                 data = df %>% filter(ben_basinc == 0))

# Immigrants - All
m_imm_all <- feols(attachment_qc ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Basic income recipients
m_imm_bas <- feols(attachment_qc ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == TRUE, ben_basinc == 1))

# Immigrants - Non-basic-income recipients
m_imm_nobas <- feols(attachment_qc ~ prox_first_circ | ID,
                     data = df %>% filter(immigrant == TRUE, ben_basinc == 0))

# Non-immigrants - All
m_nat_all <- feols(attachment_qc ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Basic income recipients
m_nat_bas <- feols(attachment_qc ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == FALSE, ben_basinc == 1))

# Non-immigrants - Non-basic-income recipients
m_nat_nobas <- feols(attachment_qc ~ prox_first_circ | ID,
                     data = df %>% filter(immigrant == FALSE, ben_basinc == 0))

modelsummary(
  list("All" = m_all, "BasInc" = m_bas, "No BasInc" = m_nobas,
       "Imm" = m_imm_all, "Imm+Bas" = m_imm_bas, "Imm+NoBas" = m_imm_nobas,
       "Nat" = m_nat_all, "Nat+Bas" = m_nat_bas, "Nat+NoBas" = m_nat_nobas),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Attachment to Quebec ~ Proximity to 1st (Basic Income)"
)
```

## Financial Satisfaction

```{r financial-satisf-basinc}
# All
m_all <- feols(financial_satisf ~ prox_first_circ | ID, data = df)

# Basic income recipients only
m_bas <- feols(financial_satisf ~ prox_first_circ | ID,
               data = df %>% filter(ben_basinc == 1))

# Non-basic-income recipients only
m_nobas <- feols(financial_satisf ~ prox_first_circ | ID,
                 data = df %>% filter(ben_basinc == 0))

# Immigrants - All
m_imm_all <- feols(financial_satisf ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Basic income recipients
m_imm_bas <- feols(financial_satisf ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == TRUE, ben_basinc == 1))

# Immigrants - Non-basic-income recipients
m_imm_nobas <- feols(financial_satisf ~ prox_first_circ | ID,
                     data = df %>% filter(immigrant == TRUE, ben_basinc == 0))

# Non-immigrants - All
m_nat_all <- feols(financial_satisf ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Basic income recipients
m_nat_bas <- feols(financial_satisf ~ prox_first_circ | ID,
                   data = df %>% filter(immigrant == FALSE, ben_basinc == 1))

# Non-immigrants - Non-basic-income recipients
m_nat_nobas <- feols(financial_satisf ~ prox_first_circ | ID,
                     data = df %>% filter(immigrant == FALSE, ben_basinc == 0))

modelsummary(
  list("All" = m_all, "BasInc" = m_bas, "No BasInc" = m_nobas,
       "Imm" = m_imm_all, "Imm+Bas" = m_imm_bas, "Imm+NoBas" = m_imm_nobas,
       "Nat" = m_nat_all, "Nat+Bas" = m_nat_bas, "Nat+NoBas" = m_nat_nobas),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Financial Satisfaction ~ Proximity to 1st (Basic Income)"
)
```

# Disability Pension Analysis (Proximity to 28th)

## Trust in Quebec Government

```{r trust-qc-dispen}
# All
m_all <- feols(trust_qc ~ prox_28_circ | ID, data = df)

# Disability pension recipients only
m_dis <- feols(trust_qc ~ prox_28_circ | ID,
               data = df %>% filter(ben_dispen == 1))

# Non-disability-pension recipients only
m_nodis <- feols(trust_qc ~ prox_28_circ | ID,
                 data = df %>% filter(ben_dispen == 0))

# Immigrants - All
m_imm_all <- feols(trust_qc ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Disability pension recipients
m_imm_dis <- feols(trust_qc ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == TRUE, ben_dispen == 1))

# Immigrants - Non-disability-pension recipients
m_imm_nodis <- feols(trust_qc ~ prox_28_circ | ID,
                     data = df %>% filter(immigrant == TRUE, ben_dispen == 0))

# Non-immigrants - All
m_nat_all <- feols(trust_qc ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Disability pension recipients
m_nat_dis <- feols(trust_qc ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == FALSE, ben_dispen == 1))

# Non-immigrants - Non-disability-pension recipients
m_nat_nodis <- feols(trust_qc ~ prox_28_circ | ID,
                     data = df %>% filter(immigrant == FALSE, ben_dispen == 0))

modelsummary(
  list("All" = m_all, "DisPen" = m_dis, "No DisPen" = m_nodis,
       "Imm" = m_imm_all, "Imm+Dis" = m_imm_dis, "Imm+NoDis" = m_imm_nodis,
       "Nat" = m_nat_all, "Nat+Dis" = m_nat_dis, "Nat+NoDis" = m_nat_nodis),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Trust in Quebec Government ~ Proximity to 28th (Disability Pension)"
)
```

## Trust in Canadian Government

```{r trust-can-dispen}
# All
m_all <- feols(trust_can ~ prox_28_circ | ID, data = df)

# Disability pension recipients only
m_dis <- feols(trust_can ~ prox_28_circ | ID,
               data = df %>% filter(ben_dispen == 1))

# Non-disability-pension recipients only
m_nodis <- feols(trust_can ~ prox_28_circ | ID,
                 data = df %>% filter(ben_dispen == 0))

# Immigrants - All
m_imm_all <- feols(trust_can ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Disability pension recipients
m_imm_dis <- feols(trust_can ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == TRUE, ben_dispen == 1))

# Immigrants - Non-disability-pension recipients
m_imm_nodis <- feols(trust_can ~ prox_28_circ | ID,
                     data = df %>% filter(immigrant == TRUE, ben_dispen == 0))

# Non-immigrants - All
m_nat_all <- feols(trust_can ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Disability pension recipients
m_nat_dis <- feols(trust_can ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == FALSE, ben_dispen == 1))

# Non-immigrants - Non-disability-pension recipients
m_nat_nodis <- feols(trust_can ~ prox_28_circ | ID,
                     data = df %>% filter(immigrant == FALSE, ben_dispen == 0))

modelsummary(
  list("All" = m_all, "DisPen" = m_dis, "No DisPen" = m_nodis,
       "Imm" = m_imm_all, "Imm+Dis" = m_imm_dis, "Imm+NoDis" = m_imm_nodis,
       "Nat" = m_nat_all, "Nat+Dis" = m_nat_dis, "Nat+NoDis" = m_nat_nodis),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Trust in Canadian Government ~ Proximity to 28th (Disability Pension, Waves 2-3 only)"
)
```

## Attachment to Quebec

```{r attachment-qc-dispen}
# All
m_all <- feols(attachment_qc ~ prox_28_circ | ID, data = df)

# Disability pension recipients only
m_dis <- feols(attachment_qc ~ prox_28_circ | ID,
               data = df %>% filter(ben_dispen == 1))

# Non-disability-pension recipients only
m_nodis <- feols(attachment_qc ~ prox_28_circ | ID,
                 data = df %>% filter(ben_dispen == 0))

# Immigrants - All
m_imm_all <- feols(attachment_qc ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Disability pension recipients
m_imm_dis <- feols(attachment_qc ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == TRUE, ben_dispen == 1))

# Immigrants - Non-disability-pension recipients
m_imm_nodis <- feols(attachment_qc ~ prox_28_circ | ID,
                     data = df %>% filter(immigrant == TRUE, ben_dispen == 0))

# Non-immigrants - All
m_nat_all <- feols(attachment_qc ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Disability pension recipients
m_nat_dis <- feols(attachment_qc ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == FALSE, ben_dispen == 1))

# Non-immigrants - Non-disability-pension recipients
m_nat_nodis <- feols(attachment_qc ~ prox_28_circ | ID,
                     data = df %>% filter(immigrant == FALSE, ben_dispen == 0))

modelsummary(
  list("All" = m_all, "DisPen" = m_dis, "No DisPen" = m_nodis,
       "Imm" = m_imm_all, "Imm+Dis" = m_imm_dis, "Imm+NoDis" = m_imm_nodis,
       "Nat" = m_nat_all, "Nat+Dis" = m_nat_dis, "Nat+NoDis" = m_nat_nodis),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Attachment to Quebec ~ Proximity to 28th (Disability Pension)"
)
```

## Financial Satisfaction

```{r financial-satisf-dispen}
# All
m_all <- feols(financial_satisf ~ prox_28_circ | ID, data = df)

# Disability pension recipients only
m_dis <- feols(financial_satisf ~ prox_28_circ | ID,
               data = df %>% filter(ben_dispen == 1))

# Non-disability-pension recipients only
m_nodis <- feols(financial_satisf ~ prox_28_circ | ID,
                 data = df %>% filter(ben_dispen == 0))

# Immigrants - All
m_imm_all <- feols(financial_satisf ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == TRUE))

# Immigrants - Disability pension recipients
m_imm_dis <- feols(financial_satisf ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == TRUE, ben_dispen == 1))

# Immigrants - Non-disability-pension recipients
m_imm_nodis <- feols(financial_satisf ~ prox_28_circ | ID,
                     data = df %>% filter(immigrant == TRUE, ben_dispen == 0))

# Non-immigrants - All
m_nat_all <- feols(financial_satisf ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == FALSE))

# Non-immigrants - Disability pension recipients
m_nat_dis <- feols(financial_satisf ~ prox_28_circ | ID,
                   data = df %>% filter(immigrant == FALSE, ben_dispen == 1))

# Non-immigrants - Non-disability-pension recipients
m_nat_nodis <- feols(financial_satisf ~ prox_28_circ | ID,
                     data = df %>% filter(immigrant == FALSE, ben_dispen == 0))

modelsummary(
  list("All" = m_all, "DisPen" = m_dis, "No DisPen" = m_nodis,
       "Imm" = m_imm_all, "Imm+Dis" = m_imm_dis, "Imm+NoDis" = m_imm_nodis,
       "Nat" = m_nat_all, "Nat+Dis" = m_nat_dis, "Nat+NoDis" = m_nat_nodis),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Financial Satisfaction ~ Proximity to 28th (Disability Pension)"
)
```

# Directional Proximity Analysis (Days Since vs Days Until)

This section examines the effects of days since last payment and days until next payment separately, rather than using the circular (minimum) distance measure.

## Child Benefit (Payment Day: 20th)

### Days Since Last Payment

```{r ccb-since}
# Trust in QC - Days Since
m_tqc_all <- feols(trust_qc ~ prox_child_since | ID, data = df)
m_tqc_ccb <- feols(trust_qc ~ prox_child_since | ID, data = df %>% filter(ben_childbnft == 1))
m_tqc_noccb <- feols(trust_qc ~ prox_child_since | ID, data = df %>% filter(ben_childbnft == 0))

# Trust in Canada - Days Since
m_tcan_all <- feols(trust_can ~ prox_child_since | ID, data = df)
m_tcan_ccb <- feols(trust_can ~ prox_child_since | ID, data = df %>% filter(ben_childbnft == 1))
m_tcan_noccb <- feols(trust_can ~ prox_child_since | ID, data = df %>% filter(ben_childbnft == 0))

# Attachment to QC - Days Since
m_att_all <- feols(attachment_qc ~ prox_child_since | ID, data = df)
m_att_ccb <- feols(attachment_qc ~ prox_child_since | ID, data = df %>% filter(ben_childbnft == 1))
m_att_noccb <- feols(attachment_qc ~ prox_child_since | ID, data = df %>% filter(ben_childbnft == 0))

# Financial Satisfaction - Days Since
m_fin_all <- feols(financial_satisf ~ prox_child_since | ID, data = df)
m_fin_ccb <- feols(financial_satisf ~ prox_child_since | ID, data = df %>% filter(ben_childbnft == 1))
m_fin_noccb <- feols(financial_satisf ~ prox_child_since | ID, data = df %>% filter(ben_childbnft == 0))

modelsummary(
  list("TrustQC All" = m_tqc_all, "TrustQC CCB" = m_tqc_ccb, "TrustQC NoCCB" = m_tqc_noccb,
       "TrustCAN All" = m_tcan_all, "TrustCAN CCB" = m_tcan_ccb, "TrustCAN NoCCB" = m_tcan_noccb,
       "Attach All" = m_att_all, "Attach CCB" = m_att_ccb, "Attach NoCCB" = m_att_noccb,
       "FinSat All" = m_fin_all, "FinSat CCB" = m_fin_ccb, "FinSat NoCCB" = m_fin_noccb),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "Child Benefit: Days SINCE Last Payment (20th)"
)
```

### Days Until Next Payment

```{r ccb-until}
# Trust in QC - Days Until
m_tqc_all <- feols(trust_qc ~ prox_child_until | ID, data = df)
m_tqc_ccb <- feols(trust_qc ~ prox_child_until | ID, data = df %>% filter(ben_childbnft == 1))
m_tqc_noccb <- feols(trust_qc ~ prox_child_until | ID, data = df %>% filter(ben_childbnft == 0))

# Trust in Canada - Days Until
m_tcan_all <- feols(trust_can ~ prox_child_until | ID, data = df)
m_tcan_ccb <- feols(trust_can ~ prox_child_until | ID, data = df %>% filter(ben_childbnft == 1))
m_tcan_noccb <- feols(trust_can ~ prox_child_until | ID, data = df %>% filter(ben_childbnft == 0))

# Attachment to QC - Days Until
m_att_all <- feols(attachment_qc ~ prox_child_until | ID, data = df)
m_att_ccb <- feols(attachment_qc ~ prox_child_until | ID, data = df %>% filter(ben_childbnft == 1))
m_att_noccb <- feols(attachment_qc ~ prox_child_until | ID, data = df %>% filter(ben_childbnft == 0))

# Financial Satisfaction - Days Until
m_fin_all <- feols(financial_satisf ~ prox_child_until | ID, data = df)
m_fin_ccb <- feols(financial_satisf ~ prox_child_until | ID, data = df %>% filter(ben_childbnft == 1))
m_fin_noccb <- feols(financial_satisf ~ prox_child_until | ID, data = df %>% filter(ben_childbnft == 0))

modelsummary(
  list("TrustQC All" = m_tqc_all, "TrustQC CCB" = m_tqc_ccb, "TrustQC NoCCB" = m_tqc_noccb,
       "TrustCAN All" = m_tcan_all, "TrustCAN CCB" = m_tcan_ccb, "TrustCAN NoCCB" = m_tcan_noccb,
       "Attach All" = m_att_all, "Attach CCB" = m_att_ccb, "Attach NoCCB" = m_att_noccb,
       "FinSat All" = m_fin_all, "FinSat CCB" = m_fin_ccb, "FinSat NoCCB" = m_fin_noccb),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "Child Benefit: Days UNTIL Next Payment (20th)"
)
```

## Retirement Pension (Payment Day: \~28th)

### Days Since Last Payment

```{r retpen-since}
# Trust in QC - Days Since
m_tqc_all <- feols(trust_qc ~ prox_28_since | ID, data = df)
m_tqc_ben <- feols(trust_qc ~ prox_28_since | ID, data = df %>% filter(ben_retpen == 1))
m_tqc_noben <- feols(trust_qc ~ prox_28_since | ID, data = df %>% filter(ben_retpen == 0))

# Trust in Canada - Days Since
m_tcan_all <- feols(trust_can ~ prox_28_since | ID, data = df)
m_tcan_ben <- feols(trust_can ~ prox_28_since | ID, data = df %>% filter(ben_retpen == 1))
m_tcan_noben <- feols(trust_can ~ prox_28_since | ID, data = df %>% filter(ben_retpen == 0))

# Attachment to QC - Days Since
m_att_all <- feols(attachment_qc ~ prox_28_since | ID, data = df)
m_att_ben <- feols(attachment_qc ~ prox_28_since | ID, data = df %>% filter(ben_retpen == 1))
m_att_noben <- feols(attachment_qc ~ prox_28_since | ID, data = df %>% filter(ben_retpen == 0))

# Financial Satisfaction - Days Since
m_fin_all <- feols(financial_satisf ~ prox_28_since | ID, data = df)
m_fin_ben <- feols(financial_satisf ~ prox_28_since | ID, data = df %>% filter(ben_retpen == 1))
m_fin_noben <- feols(financial_satisf ~ prox_28_since | ID, data = df %>% filter(ben_retpen == 0))

modelsummary(
  list("TrustQC All" = m_tqc_all, "TrustQC Ben" = m_tqc_ben, "TrustQC NoBen" = m_tqc_noben,
       "TrustCAN All" = m_tcan_all, "TrustCAN Ben" = m_tcan_ben, "TrustCAN NoBen" = m_tcan_noben,
       "Attach All" = m_att_all, "Attach Ben" = m_att_ben, "Attach NoBen" = m_att_noben,
       "FinSat All" = m_fin_all, "FinSat Ben" = m_fin_ben, "FinSat NoBen" = m_fin_noben),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "Retirement Pension: Days SINCE Last Payment (28th)"
)
```

### Days Until Next Payment

```{r retpen-until}
# Trust in QC - Days Until
m_tqc_all <- feols(trust_qc ~ prox_28_until | ID, data = df)
m_tqc_ben <- feols(trust_qc ~ prox_28_until | ID, data = df %>% filter(ben_retpen == 1))
m_tqc_noben <- feols(trust_qc ~ prox_28_until | ID, data = df %>% filter(ben_retpen == 0))

# Trust in Canada - Days Until
m_tcan_all <- feols(trust_can ~ prox_28_until | ID, data = df)
m_tcan_ben <- feols(trust_can ~ prox_28_until | ID, data = df %>% filter(ben_retpen == 1))
m_tcan_noben <- feols(trust_can ~ prox_28_until | ID, data = df %>% filter(ben_retpen == 0))

# Attachment to QC - Days Until
m_att_all <- feols(attachment_qc ~ prox_28_until | ID, data = df)
m_att_ben <- feols(attachment_qc ~ prox_28_until | ID, data = df %>% filter(ben_retpen == 1))
m_att_noben <- feols(attachment_qc ~ prox_28_until | ID, data = df %>% filter(ben_retpen == 0))

# Financial Satisfaction - Days Until
m_fin_all <- feols(financial_satisf ~ prox_28_until | ID, data = df)
m_fin_ben <- feols(financial_satisf ~ prox_28_until | ID, data = df %>% filter(ben_retpen == 1))
m_fin_noben <- feols(financial_satisf ~ prox_28_until | ID, data = df %>% filter(ben_retpen == 0))

modelsummary(
  list("TrustQC All" = m_tqc_all, "TrustQC Ben" = m_tqc_ben, "TrustQC NoBen" = m_tqc_noben,
       "TrustCAN All" = m_tcan_all, "TrustCAN Ben" = m_tcan_ben, "TrustCAN NoBen" = m_tcan_noben,
       "Attach All" = m_att_all, "Attach Ben" = m_att_ben, "Attach NoBen" = m_att_noben,
       "FinSat All" = m_fin_all, "FinSat Ben" = m_fin_ben, "FinSat NoBen" = m_fin_noben),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "Retirement Pension: Days UNTIL Next Payment (28th)"
)
```

## Housing Benefit (Payment Day: 28th)

### Days Since Last Payment

```{r housing-since}
# Trust in QC - Days Since
m_tqc_all <- feols(trust_qc ~ prox_28_since | ID, data = df)
m_tqc_ben <- feols(trust_qc ~ prox_28_since | ID, data = df %>% filter(ben_housingbnft == 1))
m_tqc_noben <- feols(trust_qc ~ prox_28_since | ID, data = df %>% filter(ben_housingbnft == 0))

# Trust in Canada - Days Since
m_tcan_all <- feols(trust_can ~ prox_28_since | ID, data = df)
m_tcan_ben <- feols(trust_can ~ prox_28_since | ID, data = df %>% filter(ben_housingbnft == 1))
m_tcan_noben <- feols(trust_can ~ prox_28_since | ID, data = df %>% filter(ben_housingbnft == 0))

# Attachment to QC - Days Since
m_att_all <- feols(attachment_qc ~ prox_28_since | ID, data = df)
m_att_ben <- feols(attachment_qc ~ prox_28_since | ID, data = df %>% filter(ben_housingbnft == 1))
m_att_noben <- feols(attachment_qc ~ prox_28_since | ID, data = df %>% filter(ben_housingbnft == 0))

# Financial Satisfaction - Days Since
m_fin_all <- feols(financial_satisf ~ prox_28_since | ID, data = df)
m_fin_ben <- feols(financial_satisf ~ prox_28_since | ID, data = df %>% filter(ben_housingbnft == 1))
m_fin_noben <- feols(financial_satisf ~ prox_28_since | ID, data = df %>% filter(ben_housingbnft == 0))

modelsummary(
  list("TrustQC All" = m_tqc_all, "TrustQC Ben" = m_tqc_ben, "TrustQC NoBen" = m_tqc_noben,
       "TrustCAN All" = m_tcan_all, "TrustCAN Ben" = m_tcan_ben, "TrustCAN NoBen" = m_tcan_noben,
       "Attach All" = m_att_all, "Attach Ben" = m_att_ben, "Attach NoBen" = m_att_noben,
       "FinSat All" = m_fin_all, "FinSat Ben" = m_fin_ben, "FinSat NoBen" = m_fin_noben),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "Housing Benefit: Days SINCE Last Payment (28th)"
)
```

### Days Until Next Payment

```{r housing-until}
# Trust in QC - Days Until
m_tqc_all <- feols(trust_qc ~ prox_28_until | ID, data = df)
m_tqc_ben <- feols(trust_qc ~ prox_28_until | ID, data = df %>% filter(ben_housingbnft == 1))
m_tqc_noben <- feols(trust_qc ~ prox_28_until | ID, data = df %>% filter(ben_housingbnft == 0))

# Trust in Canada - Days Until
m_tcan_all <- feols(trust_can ~ prox_28_until | ID, data = df)
m_tcan_ben <- feols(trust_can ~ prox_28_until | ID, data = df %>% filter(ben_housingbnft == 1))
m_tcan_noben <- feols(trust_can ~ prox_28_until | ID, data = df %>% filter(ben_housingbnft == 0))

# Attachment to QC - Days Until
m_att_all <- feols(attachment_qc ~ prox_28_until | ID, data = df)
m_att_ben <- feols(attachment_qc ~ prox_28_until | ID, data = df %>% filter(ben_housingbnft == 1))
m_att_noben <- feols(attachment_qc ~ prox_28_until | ID, data = df %>% filter(ben_housingbnft == 0))

# Financial Satisfaction - Days Until
m_fin_all <- feols(financial_satisf ~ prox_28_until | ID, data = df)
m_fin_ben <- feols(financial_satisf ~ prox_28_until | ID, data = df %>% filter(ben_housingbnft == 1))
m_fin_noben <- feols(financial_satisf ~ prox_28_until | ID, data = df %>% filter(ben_housingbnft == 0))

modelsummary(
  list("TrustQC All" = m_tqc_all, "TrustQC Ben" = m_tqc_ben, "TrustQC NoBen" = m_tqc_noben,
       "TrustCAN All" = m_tcan_all, "TrustCAN Ben" = m_tcan_ben, "TrustCAN NoBen" = m_tcan_noben,
       "Attach All" = m_att_all, "Attach Ben" = m_att_ben, "Attach NoBen" = m_att_noben,
       "FinSat All" = m_fin_all, "FinSat Ben" = m_fin_ben, "FinSat NoBen" = m_fin_noben),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "Housing Benefit: Days UNTIL Next Payment (28th)"
)
```

## Social Assistance (Payment Day: 1st)

### Days Since Last Payment

```{r socasst-since}
# Trust in QC - Days Since
m_tqc_all <- feols(trust_qc ~ prox_first_since | ID, data = df)
m_tqc_ben <- feols(trust_qc ~ prox_first_since | ID, data = df %>% filter(ben_socasst == 1))
m_tqc_noben <- feols(trust_qc ~ prox_first_since | ID, data = df %>% filter(ben_socasst == 0))

# Trust in Canada - Days Since
m_tcan_all <- feols(trust_can ~ prox_first_since | ID, data = df)
m_tcan_ben <- feols(trust_can ~ prox_first_since | ID, data = df %>% filter(ben_socasst == 1))
m_tcan_noben <- feols(trust_can ~ prox_first_since | ID, data = df %>% filter(ben_socasst == 0))

# Attachment to QC - Days Since
m_att_all <- feols(attachment_qc ~ prox_first_since | ID, data = df)
m_att_ben <- feols(attachment_qc ~ prox_first_since | ID, data = df %>% filter(ben_socasst == 1))
m_att_noben <- feols(attachment_qc ~ prox_first_since | ID, data = df %>% filter(ben_socasst == 0))

# Financial Satisfaction - Days Since
m_fin_all <- feols(financial_satisf ~ prox_first_since | ID, data = df)
m_fin_ben <- feols(financial_satisf ~ prox_first_since | ID, data = df %>% filter(ben_socasst == 1))
m_fin_noben <- feols(financial_satisf ~ prox_first_since | ID, data = df %>% filter(ben_socasst == 0))

modelsummary(
  list("TrustQC All" = m_tqc_all, "TrustQC Ben" = m_tqc_ben, "TrustQC NoBen" = m_tqc_noben,
       "TrustCAN All" = m_tcan_all, "TrustCAN Ben" = m_tcan_ben, "TrustCAN NoBen" = m_tcan_noben,
       "Attach All" = m_att_all, "Attach Ben" = m_att_ben, "Attach NoBen" = m_att_noben,
       "FinSat All" = m_fin_all, "FinSat Ben" = m_fin_ben, "FinSat NoBen" = m_fin_noben),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "Social Assistance: Days SINCE Last Payment (1st)"
)
```

### Days Until Next Payment

```{r socasst-until}
# Trust in QC - Days Until
m_tqc_all <- feols(trust_qc ~ prox_first_until | ID, data = df)
m_tqc_ben <- feols(trust_qc ~ prox_first_until | ID, data = df %>% filter(ben_socasst == 1))
m_tqc_noben <- feols(trust_qc ~ prox_first_until | ID, data = df %>% filter(ben_socasst == 0))

# Trust in Canada - Days Until
m_tcan_all <- feols(trust_can ~ prox_first_until | ID, data = df)
m_tcan_ben <- feols(trust_can ~ prox_first_until | ID, data = df %>% filter(ben_socasst == 1))
m_tcan_noben <- feols(trust_can ~ prox_first_until | ID, data = df %>% filter(ben_socasst == 0))

# Attachment to QC - Days Until
m_att_all <- feols(attachment_qc ~ prox_first_until | ID, data = df)
m_att_ben <- feols(attachment_qc ~ prox_first_until | ID, data = df %>% filter(ben_socasst == 1))
m_att_noben <- feols(attachment_qc ~ prox_first_until | ID, data = df %>% filter(ben_socasst == 0))

# Financial Satisfaction - Days Until
m_fin_all <- feols(financial_satisf ~ prox_first_until | ID, data = df)
m_fin_ben <- feols(financial_satisf ~ prox_first_until | ID, data = df %>% filter(ben_socasst == 1))
m_fin_noben <- feols(financial_satisf ~ prox_first_until | ID, data = df %>% filter(ben_socasst == 0))

modelsummary(
  list("TrustQC All" = m_tqc_all, "TrustQC Ben" = m_tqc_ben, "TrustQC NoBen" = m_tqc_noben,
       "TrustCAN All" = m_tcan_all, "TrustCAN Ben" = m_tcan_ben, "TrustCAN NoBen" = m_tcan_noben,
       "Attach All" = m_att_all, "Attach Ben" = m_att_ben, "Attach NoBen" = m_att_noben,
       "FinSat All" = m_fin_all, "FinSat Ben" = m_fin_ben, "FinSat NoBen" = m_fin_noben),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "Social Assistance: Days UNTIL Next Payment (1st)"
)
```

## Basic Income (Payment Day: 1st)

### Days Since Last Payment

```{r basinc-since}
# Trust in QC - Days Since
m_tqc_all <- feols(trust_qc ~ prox_first_since | ID, data = df)
m_tqc_ben <- feols(trust_qc ~ prox_first_since | ID, data = df %>% filter(ben_basinc == 1))
m_tqc_noben <- feols(trust_qc ~ prox_first_since | ID, data = df %>% filter(ben_basinc == 0))

# Trust in Canada - Days Since
m_tcan_all <- feols(trust_can ~ prox_first_since | ID, data = df)
m_tcan_ben <- feols(trust_can ~ prox_first_since | ID, data = df %>% filter(ben_basinc == 1))
m_tcan_noben <- feols(trust_can ~ prox_first_since | ID, data = df %>% filter(ben_basinc == 0))

# Attachment to QC - Days Since
m_att_all <- feols(attachment_qc ~ prox_first_since | ID, data = df)
m_att_ben <- feols(attachment_qc ~ prox_first_since | ID, data = df %>% filter(ben_basinc == 1))
m_att_noben <- feols(attachment_qc ~ prox_first_since | ID, data = df %>% filter(ben_basinc == 0))

# Financial Satisfaction - Days Since
m_fin_all <- feols(financial_satisf ~ prox_first_since | ID, data = df)
m_fin_ben <- feols(financial_satisf ~ prox_first_since | ID, data = df %>% filter(ben_basinc == 1))
m_fin_noben <- feols(financial_satisf ~ prox_first_since | ID, data = df %>% filter(ben_basinc == 0))

modelsummary(
  list("TrustQC All" = m_tqc_all, "TrustQC Ben" = m_tqc_ben, "TrustQC NoBen" = m_tqc_noben,
       "TrustCAN All" = m_tcan_all, "TrustCAN Ben" = m_tcan_ben, "TrustCAN NoBen" = m_tcan_noben,
       "Attach All" = m_att_all, "Attach Ben" = m_att_ben, "Attach NoBen" = m_att_noben,
       "FinSat All" = m_fin_all, "FinSat Ben" = m_fin_ben, "FinSat NoBen" = m_fin_noben),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "Basic Income: Days SINCE Last Payment (1st)"
)
```

### Days Until Next Payment

```{r basinc-until}
# Trust in QC - Days Until
m_tqc_all <- feols(trust_qc ~ prox_first_until | ID, data = df)
m_tqc_ben <- feols(trust_qc ~ prox_first_until | ID, data = df %>% filter(ben_basinc == 1))
m_tqc_noben <- feols(trust_qc ~ prox_first_until | ID, data = df %>% filter(ben_basinc == 0))

# Trust in Canada - Days Until
m_tcan_all <- feols(trust_can ~ prox_first_until | ID, data = df)
m_tcan_ben <- feols(trust_can ~ prox_first_until | ID, data = df %>% filter(ben_basinc == 1))
m_tcan_noben <- feols(trust_can ~ prox_first_until | ID, data = df %>% filter(ben_basinc == 0))

# Attachment to QC - Days Until
m_att_all <- feols(attachment_qc ~ prox_first_until | ID, data = df)
m_att_ben <- feols(attachment_qc ~ prox_first_until | ID, data = df %>% filter(ben_basinc == 1))
m_att_noben <- feols(attachment_qc ~ prox_first_until | ID, data = df %>% filter(ben_basinc == 0))

# Financial Satisfaction - Days Until
m_fin_all <- feols(financial_satisf ~ prox_first_until | ID, data = df)
m_fin_ben <- feols(financial_satisf ~ prox_first_until | ID, data = df %>% filter(ben_basinc == 1))
m_fin_noben <- feols(financial_satisf ~ prox_first_until | ID, data = df %>% filter(ben_basinc == 0))

modelsummary(
  list("TrustQC All" = m_tqc_all, "TrustQC Ben" = m_tqc_ben, "TrustQC NoBen" = m_tqc_noben,
       "TrustCAN All" = m_tcan_all, "TrustCAN Ben" = m_tcan_ben, "TrustCAN NoBen" = m_tcan_noben,
       "Attach All" = m_att_all, "Attach Ben" = m_att_ben, "Attach NoBen" = m_att_noben,
       "FinSat All" = m_fin_all, "FinSat Ben" = m_fin_ben, "FinSat NoBen" = m_fin_noben),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "Basic Income: Days UNTIL Next Payment (1st)"
)
```

## Disability Pension (Payment Day: \~28th)

### Days Since Last Payment

```{r dispen-since}
# Trust in QC - Days Since
m_tqc_all <- feols(trust_qc ~ prox_28_since | ID, data = df)
m_tqc_ben <- feols(trust_qc ~ prox_28_since | ID, data = df %>% filter(ben_dispen == 1))
m_tqc_noben <- feols(trust_qc ~ prox_28_since | ID, data = df %>% filter(ben_dispen == 0))

# Trust in Canada - Days Since
m_tcan_all <- feols(trust_can ~ prox_28_since | ID, data = df)
m_tcan_ben <- feols(trust_can ~ prox_28_since | ID, data = df %>% filter(ben_dispen == 1))
m_tcan_noben <- feols(trust_can ~ prox_28_since | ID, data = df %>% filter(ben_dispen == 0))

# Attachment to QC - Days Since
m_att_all <- feols(attachment_qc ~ prox_28_since | ID, data = df)
m_att_ben <- feols(attachment_qc ~ prox_28_since | ID, data = df %>% filter(ben_dispen == 1))
m_att_noben <- feols(attachment_qc ~ prox_28_since | ID, data = df %>% filter(ben_dispen == 0))

# Financial Satisfaction - Days Since
m_fin_all <- feols(financial_satisf ~ prox_28_since | ID, data = df)
m_fin_ben <- feols(financial_satisf ~ prox_28_since | ID, data = df %>% filter(ben_dispen == 1))
m_fin_noben <- feols(financial_satisf ~ prox_28_since | ID, data = df %>% filter(ben_dispen == 0))

modelsummary(
  list("TrustQC All" = m_tqc_all, "TrustQC Ben" = m_tqc_ben, "TrustQC NoBen" = m_tqc_noben,
       "TrustCAN All" = m_tcan_all, "TrustCAN Ben" = m_tcan_ben, "TrustCAN NoBen" = m_tcan_noben,
       "Attach All" = m_att_all, "Attach Ben" = m_att_ben, "Attach NoBen" = m_att_noben,
       "FinSat All" = m_fin_all, "FinSat Ben" = m_fin_ben, "FinSat NoBen" = m_fin_noben),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "Disability Pension: Days SINCE Last Payment (28th)"
)
```

### Days Until Next Payment

```{r dispen-until}
# Trust in QC - Days Until
m_tqc_all <- feols(trust_qc ~ prox_28_until | ID, data = df)
m_tqc_ben <- feols(trust_qc ~ prox_28_until | ID, data = df %>% filter(ben_dispen == 1))
m_tqc_noben <- feols(trust_qc ~ prox_28_until | ID, data = df %>% filter(ben_dispen == 0))

# Trust in Canada - Days Until
m_tcan_all <- feols(trust_can ~ prox_28_until | ID, data = df)
m_tcan_ben <- feols(trust_can ~ prox_28_until | ID, data = df %>% filter(ben_dispen == 1))
m_tcan_noben <- feols(trust_can ~ prox_28_until | ID, data = df %>% filter(ben_dispen == 0))

# Attachment to QC - Days Until
m_att_all <- feols(attachment_qc ~ prox_28_until | ID, data = df)
m_att_ben <- feols(attachment_qc ~ prox_28_until | ID, data = df %>% filter(ben_dispen == 1))
m_att_noben <- feols(attachment_qc ~ prox_28_until | ID, data = df %>% filter(ben_dispen == 0))

# Financial Satisfaction - Days Until
m_fin_all <- feols(financial_satisf ~ prox_28_until | ID, data = df)
m_fin_ben <- feols(financial_satisf ~ prox_28_until | ID, data = df %>% filter(ben_dispen == 1))
m_fin_noben <- feols(financial_satisf ~ prox_28_until | ID, data = df %>% filter(ben_dispen == 0))

modelsummary(
  list("TrustQC All" = m_tqc_all, "TrustQC Ben" = m_tqc_ben, "TrustQC NoBen" = m_tqc_noben,
       "TrustCAN All" = m_tcan_all, "TrustCAN Ben" = m_tcan_ben, "TrustCAN NoBen" = m_tcan_noben,
       "Attach All" = m_att_all, "Attach Ben" = m_att_ben, "Attach NoBen" = m_att_noben,
       "FinSat All" = m_fin_all, "FinSat Ben" = m_fin_ben, "FinSat NoBen" = m_fin_noben),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "Disability Pension: Days UNTIL Next Payment (28th)"
)
```

# Pooled Beneficiary Analysis (Personalized Proximity)

This analysis pools all beneficiaries together using a personalized proximity measure. For each beneficiary, we calculate proximity to their specific benefit payment day(s). If they receive multiple benefits with different payment dates, we use whichever payment is closest (minimum circular distance).

Payment day groups: - 1st: Social Assistance, Basic Income - 20th: Child Benefit - 28th: Housing Benefit, Retirement Pension, Disability Pension

```{r personalized-proximity}
# Calculate proximity to each payment day (vectorized)
calc_prox_vec <- function(survey_days, payment_day, days_in_month = 30) {
  since <- ifelse(survey_days >= payment_day,
                  survey_days - payment_day,
                  (days_in_month - payment_day) + survey_days)
  until <- ifelse(survey_days >= payment_day,
                  (days_in_month - survey_days) + payment_day,
                  payment_day - survey_days)
  circ <- pmin(since, until)
  data.frame(since = since, until = until, circ = circ)
}

prox_1 <- calc_prox_vec(df$day_of_month, 1)
prox_20 <- calc_prox_vec(df$day_of_month, 20)
prox_28 <- calc_prox_vec(df$day_of_month, 28)

df$prox_1_since <- prox_1$since
df$prox_1_until <- prox_1$until
df$prox_1_circ <- prox_1$circ

df$prox_20_since <- prox_20$since
df$prox_20_until <- prox_20$until
df$prox_20_circ <- prox_20$circ

df$prox_28_since <- prox_28$since
df$prox_28_until <- prox_28$until
df$prox_28_circ <- prox_28$circ

# Payment day groups
df <- df %>%
  mutate(
    has_pay_1 = (ben_socasst == 1 | ben_basinc == 1),
    has_pay_20 = (ben_childbnft == 1),
    has_pay_28 = (ben_housingbnft == 1 | ben_retpen == 1 | ben_dispen == 1),
    is_any_ben = (has_pay_1 | has_pay_20 | has_pay_28)
  )

# Find closest payment day for each beneficiary
df <- df %>%
  mutate(
    circ_1_adj = ifelse(has_pay_1, prox_1_circ, 999),
    circ_20_adj = ifelse(has_pay_20, prox_20_circ, 999),
    circ_28_adj = ifelse(has_pay_28, prox_28_circ, 999),
    min_circ = pmin(circ_1_adj, circ_20_adj, circ_28_adj),

    closest_pay_day = case_when(
      !is_any_ben ~ NA_real_,
      min_circ == circ_1_adj ~ 1,
      min_circ == circ_20_adj ~ 20,
      min_circ == circ_28_adj ~ 28,
      TRUE ~ NA_real_
    ),

    personal_prox_circ = case_when(
      !is_any_ben ~ NA_real_,
      closest_pay_day == 1 ~ prox_1_circ,
      closest_pay_day == 20 ~ prox_20_circ,
      closest_pay_day == 28 ~ prox_28_circ
    ),
    personal_prox_since = case_when(
      !is_any_ben ~ NA_real_,
      closest_pay_day == 1 ~ prox_1_since,
      closest_pay_day == 20 ~ prox_20_since,
      closest_pay_day == 28 ~ prox_28_since
    ),
    personal_prox_until = case_when(
      !is_any_ben ~ NA_real_,
      closest_pay_day == 1 ~ prox_1_until,
      closest_pay_day == 20 ~ prox_20_until,
      closest_pay_day == 28 ~ prox_28_until
    )
  )

# Verify
cat("Beneficiary counts:\n")
cat("Any beneficiary:", sum(df$is_any_ben, na.rm = TRUE), "\n")
cat("Closest payment day distribution:\n")
print(table(df$closest_pay_day, useNA = "ifany"))
```

## All Beneficiaries

```{r pooled-all}
ben_df <- df %>% filter(is_any_ben == TRUE)

# Circular proximity
m_circ_tqc <- feols(trust_qc ~ personal_prox_circ | ID, data = ben_df)
m_circ_tcan <- feols(trust_can ~ personal_prox_circ | ID, data = ben_df)
m_circ_att <- feols(attachment_qc ~ personal_prox_circ | ID, data = ben_df)
m_circ_fin <- feols(financial_satisf ~ personal_prox_circ | ID, data = ben_df)

# Days since
m_since_tqc <- feols(trust_qc ~ personal_prox_since | ID, data = ben_df)
m_since_tcan <- feols(trust_can ~ personal_prox_since | ID, data = ben_df)
m_since_att <- feols(attachment_qc ~ personal_prox_since | ID, data = ben_df)
m_since_fin <- feols(financial_satisf ~ personal_prox_since | ID, data = ben_df)

# Days until
m_until_tqc <- feols(trust_qc ~ personal_prox_until | ID, data = ben_df)
m_until_tcan <- feols(trust_can ~ personal_prox_until | ID, data = ben_df)
m_until_att <- feols(attachment_qc ~ personal_prox_until | ID, data = ben_df)
m_until_fin <- feols(financial_satisf ~ personal_prox_until | ID, data = ben_df)

modelsummary(
  list("TrustQC Circ" = m_circ_tqc, "TrustQC Since" = m_since_tqc, "TrustQC Until" = m_until_tqc,
       "TrustCAN Circ" = m_circ_tcan, "TrustCAN Since" = m_since_tcan, "TrustCAN Until" = m_until_tcan,
       "Attach Circ" = m_circ_att, "Attach Since" = m_since_att, "Attach Until" = m_until_att,
       "FinSat Circ" = m_circ_fin, "FinSat Since" = m_since_fin, "FinSat Until" = m_until_fin),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "Pooled Beneficiaries: Personalized Proximity (All)"
)
```

## Immigrant Beneficiaries

```{r pooled-immigrants}
imm_ben <- ben_df %>% filter(immigrant == TRUE)

# Circular proximity
m_circ_tqc <- feols(trust_qc ~ personal_prox_circ | ID, data = imm_ben)
m_circ_tcan <- feols(trust_can ~ personal_prox_circ | ID, data = imm_ben)
m_circ_att <- feols(attachment_qc ~ personal_prox_circ | ID, data = imm_ben)
m_circ_fin <- feols(financial_satisf ~ personal_prox_circ | ID, data = imm_ben)

# Days since
m_since_tqc <- feols(trust_qc ~ personal_prox_since | ID, data = imm_ben)
m_since_tcan <- feols(trust_can ~ personal_prox_since | ID, data = imm_ben)
m_since_att <- feols(attachment_qc ~ personal_prox_since | ID, data = imm_ben)
m_since_fin <- feols(financial_satisf ~ personal_prox_since | ID, data = imm_ben)

# Days until
m_until_tqc <- feols(trust_qc ~ personal_prox_until | ID, data = imm_ben)
m_until_tcan <- feols(trust_can ~ personal_prox_until | ID, data = imm_ben)
m_until_att <- feols(attachment_qc ~ personal_prox_until | ID, data = imm_ben)
m_until_fin <- feols(financial_satisf ~ personal_prox_until | ID, data = imm_ben)

modelsummary(
  list("TrustQC Circ" = m_circ_tqc, "TrustQC Since" = m_since_tqc, "TrustQC Until" = m_until_tqc,
       "TrustCAN Circ" = m_circ_tcan, "TrustCAN Since" = m_since_tcan, "TrustCAN Until" = m_until_tcan,
       "Attach Circ" = m_circ_att, "Attach Since" = m_since_att, "Attach Until" = m_until_att,
       "FinSat Circ" = m_circ_fin, "FinSat Since" = m_since_fin, "FinSat Until" = m_until_fin),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "Pooled Beneficiaries: Personalized Proximity (Immigrants)"
)
```

## Non-Immigrant Beneficiaries

```{r pooled-natives}
nat_ben <- ben_df %>% filter(immigrant == FALSE)

# Circular proximity
m_circ_tqc <- feols(trust_qc ~ personal_prox_circ | ID, data = nat_ben)
m_circ_tcan <- feols(trust_can ~ personal_prox_circ | ID, data = nat_ben)
m_circ_att <- feols(attachment_qc ~ personal_prox_circ | ID, data = nat_ben)
m_circ_fin <- feols(financial_satisf ~ personal_prox_circ | ID, data = nat_ben)

# Days since
m_since_tqc <- feols(trust_qc ~ personal_prox_since | ID, data = nat_ben)
m_since_tcan <- feols(trust_can ~ personal_prox_since | ID, data = nat_ben)
m_since_att <- feols(attachment_qc ~ personal_prox_since | ID, data = nat_ben)
m_since_fin <- feols(financial_satisf ~ personal_prox_since | ID, data = nat_ben)

# Days until
m_until_tqc <- feols(trust_qc ~ personal_prox_until | ID, data = nat_ben)
m_until_tcan <- feols(trust_can ~ personal_prox_until | ID, data = nat_ben)
m_until_att <- feols(attachment_qc ~ personal_prox_until | ID, data = nat_ben)
m_until_fin <- feols(financial_satisf ~ personal_prox_until | ID, data = nat_ben)

modelsummary(
  list("TrustQC Circ" = m_circ_tqc, "TrustQC Since" = m_since_tqc, "TrustQC Until" = m_until_tqc,
       "TrustCAN Circ" = m_circ_tcan, "TrustCAN Since" = m_since_tcan, "TrustCAN Until" = m_until_tcan,
       "Attach Circ" = m_circ_att, "Attach Since" = m_since_att, "Attach Until" = m_until_att,
       "FinSat Circ" = m_circ_fin, "FinSat Since" = m_since_fin, "FinSat Until" = m_until_fin),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "Pooled Beneficiaries: Personalized Proximity (Non-Immigrants)"
)
```

# Parallel Trends Charts (DiD Assumption Check)

This section creates parallel trends charts comparing beneficiaries vs non-beneficiaries around each payment date. For DiD identification, we need to see: 1. Parallel trends in the pre-period (similar slopes before treatment) 2. A potential discontinuity at the payment date

```{r parallel-trends-setup}
# Function to calculate relative day (distance from payment day)
# Wraps around month boundaries so day 28 is +8 from the 20th, not -8
calc_relative_day <- function(day_of_month, payment_day) {
  rel <- day_of_month - payment_day
  rel <- ifelse(rel > 15, rel - 30, rel)
  rel <- ifelse(rel < -15, rel + 30, rel)
  return(rel)
}

# Outcomes to plot
outcomes <- c("trust_qc", "trust_can", "attachment_qc", "financial_satisf")
outcome_labels <- c("Trust in QC Gov", "Trust in CAN Gov",
                    "Attachment to QC", "Financial Satisfaction")
```

## Payment Day 1 (Social Assistance / Basic Income)

```{r parallel-trends-day1, fig.width=10, fig.height=8}
# Social Assistance and Basic Income pay on the 1st
df_day1 <- df %>%
  mutate(
    relative_day = calc_relative_day(day_of_month, 1),
    is_ben = as.numeric(ben_socasst == 1 | ben_basinc == 1)
  ) %>%
  filter(abs(relative_day) <= 10) %>%
  # Exclude anyone with ANY fixed benefit from non-beneficiary group
  filter(is_ben == 1 | ben_any_fixed == 0)

# Aggregate means by relative day and beneficiary status
agg_day1 <- df_day1 %>%
  group_by(relative_day, is_ben) %>%
  summarise(
    n = n(),
    trust_qc = mean(trust_qc, na.rm = TRUE),
    trust_can = mean(trust_can, na.rm = TRUE),
    attachment_qc = mean(attachment_qc, na.rm = TRUE),
    financial_satisf = mean(financial_satisf, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(group = ifelse(is_ben == 1, "Beneficiaries", "Non-Beneficiaries"))

# Sample sizes
cat("Day 1 (Social Assistance/Basic Income) sample sizes:\n")
cat("Beneficiaries:", sum(df_day1$is_ben == 1), "\n")
cat("Non-beneficiaries:", sum(df_day1$is_ben == 0), "\n")

# Create plots
plots_day1 <- map2(outcomes, outcome_labels, function(outcome, label) {
  ggplot(agg_day1, aes(x = relative_day, y = .data[[outcome]],
                       color = group, linetype = group)) +
    geom_line(linewidth = 1) +
    geom_point(size = 2) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.8) +
    scale_x_continuous(breaks = seq(-10, 10, 2)) +
    labs(
      title = paste0(label, " - Day 1 (Social Asst/Basic Income)"),
      x = "Days Relative to Payment (0 = Payment Day)",
      y = label,
      color = "Group",
      linetype = "Group"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")
})

# Combine plots
cowplot::plot_grid(plotlist = plots_day1, ncol = 2)
```

## Payment Day 20 (Child Benefit)

```{r parallel-trends-day20, fig.width=10, fig.height=8}
# Child Benefit pays on the 20th
df_day20 <- df %>%
  mutate(
    relative_day = calc_relative_day(day_of_month, 20),
    is_ben = as.numeric(ben_childbnft == 1)
  ) %>%
  filter(abs(relative_day) <= 10) %>%
  # Exclude anyone with ANY fixed benefit from non-beneficiary group
  filter(is_ben == 1 | ben_any_fixed == 0)

# Aggregate means by relative day and beneficiary status
agg_day20 <- df_day20 %>%
  group_by(relative_day, is_ben) %>%
  summarise(
    n = n(),
    trust_qc = mean(trust_qc, na.rm = TRUE),
    trust_can = mean(trust_can, na.rm = TRUE),
    attachment_qc = mean(attachment_qc, na.rm = TRUE),
    financial_satisf = mean(financial_satisf, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(group = ifelse(is_ben == 1, "Beneficiaries", "Non-Beneficiaries"))

# Sample sizes
cat("Day 20 (Child Benefit) sample sizes:\n")
cat("Beneficiaries:", sum(df_day20$is_ben == 1), "\n")
cat("Non-beneficiaries:", sum(df_day20$is_ben == 0), "\n")

# Create plots
plots_day20 <- map2(outcomes, outcome_labels, function(outcome, label) {
  ggplot(agg_day20, aes(x = relative_day, y = .data[[outcome]],
                        color = group, linetype = group)) +
    geom_line(linewidth = 1) +
    geom_point(size = 2) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.8) +
    scale_x_continuous(breaks = seq(-10, 10, 2)) +
    labs(
      title = paste0(label, " - Day 20 (Child Benefit)"),
      x = "Days Relative to Payment (0 = Payment Day)",
      y = label,
      color = "Group",
      linetype = "Group"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")
})

# Combine plots
cowplot::plot_grid(plotlist = plots_day20, ncol = 2)
```

## Payment Day 28 (Housing Benefit / Pensions)

```{r parallel-trends-day28, fig.width=10, fig.height=8}
# Housing Benefit and Pensions pay around the 28th
df_day28 <- df %>%
  mutate(
    relative_day = calc_relative_day(day_of_month, 28),
    is_ben = as.numeric(ben_housingbnft == 1 | ben_retpen == 1 | ben_dispen == 1)
  ) %>%
  filter(abs(relative_day) <= 10) %>%
  # Exclude anyone with ANY fixed benefit from non-beneficiary group
  filter(is_ben == 1 | ben_any_fixed == 0)

# Aggregate means by relative day and beneficiary status
agg_day28 <- df_day28 %>%
  group_by(relative_day, is_ben) %>%
  summarise(
    n = n(),
    trust_qc = mean(trust_qc, na.rm = TRUE),
    trust_can = mean(trust_can, na.rm = TRUE),
    attachment_qc = mean(attachment_qc, na.rm = TRUE),
    financial_satisf = mean(financial_satisf, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(group = ifelse(is_ben == 1, "Beneficiaries", "Non-Beneficiaries"))

# Sample sizes
cat("Day 28 (Housing/Pensions) sample sizes:\n")
cat("Beneficiaries:", sum(df_day28$is_ben == 1), "\n")
cat("Non-beneficiaries:", sum(df_day28$is_ben == 0), "\n")

# Create plots
plots_day28 <- map2(outcomes, outcome_labels, function(outcome, label) {
  ggplot(agg_day28, aes(x = relative_day, y = .data[[outcome]],
                        color = group, linetype = group)) +
    geom_line(linewidth = 1) +
    geom_point(size = 2) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.8) +
    scale_x_continuous(breaks = seq(-10, 10, 2)) +
    labs(
      title = paste0(label, " - Day 28 (Housing/Pensions)"),
      x = "Days Relative to Payment (0 = Payment Day)",
      y = label,
      color = "Group",
      linetype = "Group"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")
})

# Combine plots
cowplot::plot_grid(plotlist = plots_day28, ncol = 2)
```

# Difference-in-Differences: Child Benefit (Day 20)

This section estimates DiD models for the Child Benefit payment date (20th). - **Treated**: Receives Child Benefit (`ben_childbnft == 1`) - **Post**: Surveyed after the 20th of the month (`day_of_month > 20`) - **Fixed effects**: Individual ID + Wave - **Clustered SEs**: Individual ID

```{r did-day20-setup}
# NOTE: mprog_* variables are character (text labels when selected, NA otherwise)
# Need to check for !is.na() not == 1

# Create beneficiary variable with panel propagation
df <- df %>%
  group_by(ID) %>%
  mutate(
    ever_child = any(!is.na(mprog_childbnft)),
    selected_none_wave = !is.na(mprog_none)
  ) %>%
  ungroup() %>%
  mutate(
    ben_childbnft = case_when(
      selected_none_wave ~ 0,
      ever_child ~ 1,
      TRUE ~ 0
    )
  )

# Create DiD variables
df <- df %>%
  mutate(
    # Post = surveyed after the 20th
    post_20 = as.numeric(day_of_month > 20),
    # Treated = receives child benefit
    treated_child = as.numeric(ben_childbnft == 1),
    # Interaction
    treat_post_child = treated_child * post_20
  )

# Check distribution
cat("Post (after 20th) distribution:\n")
table(df$post_20, useNA = "ifany")
cat("\nTreated (Child Benefit) distribution:\n")
table(df$treated_child, useNA = "ifany")
cat("\n2x2 Table:\n")
table(Treated = df$treated_child, Post = df$post_20)
```

## Full Sample DiD

```{r did-day20-full}
# Full sample DiD models
# Specification: outcome ~ treated * post | ID + wave, cluster = ~ID

m_full_tqc <- feols(trust_qc ~ treated_child * post_20 | ID + wave,
                    data = df, cluster = ~ID)
m_full_tcan <- feols(trust_can ~ treated_child * post_20 | ID + wave,
                     data = df, cluster = ~ID)
m_full_att <- feols(attachment_qc ~ treated_child * post_20 | ID + wave,
                    data = df, cluster = ~ID)
m_full_fin <- feols(financial_satisf ~ treated_child * post_20 | ID + wave,
                    data = df, cluster = ~ID)

modelsummary(
  list("Trust QC" = m_full_tqc, "Trust CAN" = m_full_tcan,
       "Attachment QC" = m_full_att, "Financial Sat" = m_full_fin),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "DiD: Child Benefit (Day 20) - Full Sample"
)
```

## Temporal Subsets

### ±10 Days Window

```{r did-day20-10days}
# Subset to ±10 days from the 20th
df_10d <- df %>%
  filter(day_of_month >= 10 & day_of_month <= 30)

cat("±10 days window (days 10-30): n =", nrow(df_10d), "\n")

m_10d_tqc <- feols(trust_qc ~ treated_child * post_20 | ID + wave,
                   data = df_10d, cluster = ~ID)
m_10d_tcan <- feols(trust_can ~ treated_child * post_20 | ID + wave,
                    data = df_10d, cluster = ~ID)
m_10d_att <- feols(attachment_qc ~ treated_child * post_20 | ID + wave,
                   data = df_10d, cluster = ~ID)
m_10d_fin <- feols(financial_satisf ~ treated_child * post_20 | ID + wave,
                   data = df_10d, cluster = ~ID)

modelsummary(
  list("Trust QC" = m_10d_tqc, "Trust CAN" = m_10d_tcan,
       "Attachment QC" = m_10d_att, "Financial Sat" = m_10d_fin),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "DiD: Child Benefit (Day 20) - ±10 Days Window"
)
```

### ±5 Days Window

```{r did-day20-5days}
# Subset to ±5 days from the 20th
df_5d <- df %>%
  filter(day_of_month >= 15 & day_of_month <= 25)

cat("±5 days window (days 15-25): n =", nrow(df_5d), "\n")

m_5d_tqc <- feols(trust_qc ~ treated_child * post_20 | ID + wave,
                  data = df_5d, cluster = ~ID)
m_5d_tcan <- feols(trust_can ~ treated_child * post_20 | ID + wave,
                   data = df_5d, cluster = ~ID)
m_5d_att <- feols(attachment_qc ~ treated_child * post_20 | ID + wave,
                  data = df_5d, cluster = ~ID)
m_5d_fin <- feols(financial_satisf ~ treated_child * post_20 | ID + wave,
                  data = df_5d, cluster = ~ID)

modelsummary(
  list("Trust QC" = m_5d_tqc, "Trust CAN" = m_5d_tcan,
       "Attachment QC" = m_5d_att, "Financial Sat" = m_5d_fin),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "DiD: Child Benefit (Day 20) - ±5 Days Window"
)
```

### ±3 Days Window

```{r did-day20-3days}
# Subset to ±3 days from the 20th
df_3d <- df %>%
  filter(day_of_month >= 17 & day_of_month <= 23)

cat("±3 days window (days 17-23): n =", nrow(df_3d), "\n")

m_3d_tqc <- feols(trust_qc ~ treated_child * post_20 | ID + wave,
                  data = df_3d, cluster = ~ID)
m_3d_tcan <- feols(trust_can ~ treated_child * post_20 | ID + wave,
                   data = df_3d, cluster = ~ID)
m_3d_att <- feols(attachment_qc ~ treated_child * post_20 | ID + wave,
                  data = df_3d, cluster = ~ID)
m_3d_fin <- feols(financial_satisf ~ treated_child * post_20 | ID + wave,
                  data = df_3d, cluster = ~ID)

modelsummary(
  list("Trust QC" = m_3d_tqc, "Trust CAN" = m_3d_tcan,
       "Attachment QC" = m_3d_att, "Financial Sat" = m_3d_fin),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "DiD: Child Benefit (Day 20) - ±3 Days Window"
)
```

## Individual FE Only (No Wave FE)

Same DiD models but with individual fixed effects only (no wave fixed effects).

### Full Sample (Individual FE)

```{r did-day20-full-id-only}
m_full_tqc_id <- feols(trust_qc ~ treated_child * post_20 | ID,
                       data = df, cluster = ~ID)
m_full_tcan_id <- feols(trust_can ~ treated_child * post_20 | ID,
                        data = df, cluster = ~ID)
m_full_att_id <- feols(attachment_qc ~ treated_child * post_20 | ID,
                       data = df, cluster = ~ID)
m_full_fin_id <- feols(financial_satisf ~ treated_child * post_20 | ID,
                       data = df, cluster = ~ID)

modelsummary(
  list("Trust QC" = m_full_tqc_id, "Trust CAN" = m_full_tcan_id,
       "Attachment QC" = m_full_att_id, "Financial Sat" = m_full_fin_id),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "DiD: Child Benefit (Day 20) - Full Sample (Individual FE Only)"
)
```

### ±10 Days Window (Individual FE)

```{r did-day20-10days-id-only}
m_10d_tqc_id <- feols(trust_qc ~ treated_child * post_20 | ID,
                      data = df_10d, cluster = ~ID)
m_10d_tcan_id <- feols(trust_can ~ treated_child * post_20 | ID,
                       data = df_10d, cluster = ~ID)
m_10d_att_id <- feols(attachment_qc ~ treated_child * post_20 | ID,
                      data = df_10d, cluster = ~ID)
m_10d_fin_id <- feols(financial_satisf ~ treated_child * post_20 | ID,
                      data = df_10d, cluster = ~ID)

modelsummary(
  list("Trust QC" = m_10d_tqc_id, "Trust CAN" = m_10d_tcan_id,
       "Attachment QC" = m_10d_att_id, "Financial Sat" = m_10d_fin_id),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "DiD: Child Benefit (Day 20) - ±10 Days (Individual FE Only)"
)
```

### ±5 Days Window (Individual FE)

```{r did-day20-5days-id-only}
m_5d_tqc_id <- feols(trust_qc ~ treated_child * post_20 | ID,
                     data = df_5d, cluster = ~ID)
m_5d_tcan_id <- feols(trust_can ~ treated_child * post_20 | ID,
                      data = df_5d, cluster = ~ID)
m_5d_att_id <- feols(attachment_qc ~ treated_child * post_20 | ID,
                     data = df_5d, cluster = ~ID)
m_5d_fin_id <- feols(financial_satisf ~ treated_child * post_20 | ID,
                     data = df_5d, cluster = ~ID)

modelsummary(
  list("Trust QC" = m_5d_tqc_id, "Trust CAN" = m_5d_tcan_id,
       "Attachment QC" = m_5d_att_id, "Financial Sat" = m_5d_fin_id),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "DiD: Child Benefit (Day 20) - ±5 Days (Individual FE Only)"
)
```

### ±3 Days Window (Individual FE)

```{r did-day20-3days-id-only}
m_3d_tqc_id <- feols(trust_qc ~ treated_child * post_20 | ID,
                     data = df_3d, cluster = ~ID)
m_3d_tcan_id <- feols(trust_can ~ treated_child * post_20 | ID,
                      data = df_3d, cluster = ~ID)
m_3d_att_id <- feols(attachment_qc ~ treated_child * post_20 | ID,
                     data = df_3d, cluster = ~ID)
m_3d_fin_id <- feols(financial_satisf ~ treated_child * post_20 | ID,
                     data = df_3d, cluster = ~ID)

modelsummary(
  list("Trust QC" = m_3d_tqc_id, "Trust CAN" = m_3d_tcan_id,
       "Attachment QC" = m_3d_att_id, "Financial Sat" = m_3d_fin_id),
  stars = TRUE,
  gof_map = c("nobs", "r.squared.within"),
  title = "DiD: Child Benefit (Day 20) - ±3 Days (Individual FE Only)"
)
```

# Save Prepared Data

```{r save}
# Select key variables for analysis
df_analysis <- df %>%
  select(
    # Identifiers
    ID, wave, immigrant,
    # Outcomes (cleaned)
    trust_qc, trust_can, attachment_qc, financial_satisf,
    # Original outcomes (for reference)
    trust_qcgov, trust_cangov, attach_qc, current_financialsatisf,
    # Survey timing
    startdate, enddate, recordeddate,
    survey_date, day_of_month, month, year,
    # Proximity variables
    starts_with("prox_"),
    # Beneficiary variables
    starts_with("ben_"),
    selected_none,
    # Original benefit variables
    starts_with("mprog_"),
    # Demographics
    birthyear, gender, income, hhincome, education_cat
  )

cat("Analysis dataset:", nrow(df_analysis), "rows,", ncol(df_analysis), "columns\n")

# Quick check
cat("\nOutcome variable summary in analysis dataset:\n")
df_analysis %>%
  summarise(
    n = n(),
    trust_qc_mean = mean(trust_qc, na.rm = TRUE),
    trust_can_mean = mean(trust_can, na.rm = TRUE),
    attachment_qc_mean = mean(attachment_qc, na.rm = TRUE),
    financial_satisf_mean = mean(financial_satisf, na.rm = TRUE)
  ) %>%
  kable(digits = 2)
```
