---
title: "Housing Benefit Analysis"
subtitle: "Payment Timing and Government Attitudes"
format:
  html:
    toc: true
    number-sections: true
    code-fold: true
  pdf:
    toc: true
    number-sections: true
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Setup

```{r packages}
rm(list = ls())

pacman::p_load(

  tidyverse,
  lubridate,
  fixest,
  modelsummary,
  knitr
)
```

```{r load-data}
df <- readRDS("df_full_panel_both_samples.rds")
cat("Loaded:", nrow(df), "observations,", ncol(df), "variables\n")
```

# Data Preparation

## Outcome Variables

All outcomes are 0-10 scales where higher = more of the construct.

```{r outcomes}
df <- df %>%
  mutate(
    trust_qc = as.numeric(trust_qcgov),
    trust_can = as.numeric(trust_cangov),
    attachment_qc = as.numeric(attach_qc),
    attachment_can = as.numeric(attach_can),
    financial_satisf = as.numeric(current_financialsatisf),
    imp_qcvalues = as.numeric(imp_qcvalues)
  )

# Summary
outcomes_summary <- df %>%
  summarise(
    across(
      c(trust_qc, trust_can, attachment_qc, attachment_can, financial_satisf, imp_qcvalues),
      list(n = ~sum(!is.na(.)), mean = ~mean(., na.rm = TRUE), sd = ~sd(., na.rm = TRUE)),
      .names = "{.col}_{.fn}"
    )
  ) %>%
  pivot_longer(everything(), names_to = c("variable", "stat"), names_sep = "_(?=[^_]+$)") %>%
  pivot_wider(names_from = stat, values_from = value)

kable(outcomes_summary, digits = 2, caption = "Outcome Variables Summary")
```

## Survey Timing

```{r timing}
df <- df %>%
  mutate(
    survey_datetime = as.POSIXct(startdate),
    survey_date = as.Date(survey_datetime),
    day_of_month = day(survey_datetime),
    month = month(survey_datetime),
    year = year(survey_datetime)
  )

cat("Day of month distribution:\n")
print(table(df$day_of_month))
```

## Proximity to Day 28 (Housing Benefit Payment)

```{r proximity}
# Function to calculate distance to a fixed payment day
calc_payment_proximity <- function(survey_day, payment_day, days_in_month = 30) {
  if (survey_day >= payment_day) {
    days_since <- survey_day - payment_day
    days_until <- (days_in_month - survey_day) + payment_day
  } else {
    days_since <- (days_in_month - payment_day) + survey_day
    days_until <- payment_day - survey_day
  }
  circular <- min(days_since, days_until)
  return(list(days_since = days_since, days_until = days_until, circular = circular))
}

# Vectorized version
calc_proximity_vec <- function(survey_days, payment_day, days_in_month = 30) {
  n <- length(survey_days)
  days_since <- numeric(n)
  days_until <- numeric(n)

  for (i in seq_len(n)) {
    if (is.na(survey_days[i])) {
      days_since[i] <- NA
      days_until[i] <- NA
    } else {
      result <- calc_payment_proximity(survey_days[i], payment_day, days_in_month)
      days_since[i] <- result$days_since
      days_until[i] <- result$days_until
    }
  }
  circular <- pmin(days_since, days_until)
  return(data.frame(days_since = days_since, days_until = days_until, circular = circular))
}

# Calculate proximity to 28th
prox_28 <- calc_proximity_vec(df$day_of_month, payment_day = 28)
df$prox_28_since <- prox_28$days_since
df$prox_28_until <- prox_28$days_until
df$prox_28_circ <- prox_28$circular

cat("Proximity to 28th (Housing Benefit):\n")
cat("Days since:", summary(df$prox_28_since), "\n")
cat("Days until:", summary(df$prox_28_until), "\n")
cat("Circular:", summary(df$prox_28_circ), "\n")
```

## Housing Benefit Status

Panel propagation logic: if someone reports receiving a benefit in ANY wave, code them as beneficiary in ALL waves, UNLESS they select "None of these programs" in that specific wave.

```{r beneficiary}
# Raw indicator
df$raw_mprog_housingbnft <- ifelse(!is.na(df$mprog_housingbnft), 1, 0)

# "None of these programs" indicator
df$selected_none <- ifelse(!is.na(df$mprog_none), 1, 0)

# Get IDs who ever reported housing benefit
ever_housing <- df %>%
  filter(raw_mprog_housingbnft == 1) %>%
  pull(ID) %>%
  unique()

# Create beneficiary variable with propagation
df <- df %>%
  mutate(
    ben_housingbnft = case_when(
      selected_none == 1 ~ 0,
      ID %in% ever_housing ~ 1,
      TRUE ~ 0
    )
  )

cat("Housing Benefit Status:\n")
print(table(df$ben_housingbnft, useNA = "ifany"))
cat("\nBy immigrant status:\n")
print(table(Housing = df$ben_housingbnft, Immigrant = df$immigrant))
```

# Panel Fixed Effects Models (Circular Distance)

These models use `prox_28_circ` — circular distance to payment date (0-15, min of days since/until).

## Trust in Quebec Government

```{r fe-trust-qc}
# All observations
m_all <- feols(trust_qc ~ prox_28_circ | ID, data = df)

# Beneficiaries only
m_ben <- feols(trust_qc ~ prox_28_circ | ID,
               data = df %>% filter(ben_housingbnft == 1))

# Non-beneficiaries (placebo)
m_noben <- feols(trust_qc ~ prox_28_circ | ID,
                 data = df %>% filter(ben_housingbnft == 0))

# Immigrant beneficiaries
m_imm_ben <- feols(trust_qc ~ prox_28_circ | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == TRUE))

# Immigrant non-beneficiaries
m_imm_noben <- feols(trust_qc ~ prox_28_circ | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == TRUE))

# Non-immigrant beneficiaries
m_nat_ben <- feols(trust_qc ~ prox_28_circ | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == FALSE))

# Non-immigrant non-beneficiaries
m_nat_noben <- feols(trust_qc ~ prox_28_circ | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == FALSE))

modelsummary(
  list("All" = m_all,
       "Beneficiaries" = m_ben,
       "Non-Ben (Placebo)" = m_noben,
       "Imm + Ben" = m_imm_ben,
       "Imm + Non-Ben" = m_imm_noben,
       "Native + Ben" = m_nat_ben,
       "Native + Non-Ben" = m_nat_noben),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_rename = c("prox_28_circ" = "Circular Distance (Days)"),
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Trust in QC Government ~ Circular Distance to Payment (Day 28)"
)
```

## Trust in Canadian Government

```{r fe-trust-can}
m_all <- feols(trust_can ~ prox_28_circ | ID, data = df)
m_ben <- feols(trust_can ~ prox_28_circ | ID,
               data = df %>% filter(ben_housingbnft == 1))
m_noben <- feols(trust_can ~ prox_28_circ | ID,
                 data = df %>% filter(ben_housingbnft == 0))
m_imm_ben <- feols(trust_can ~ prox_28_circ | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == TRUE))
m_imm_noben <- feols(trust_can ~ prox_28_circ | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == TRUE))
m_nat_ben <- feols(trust_can ~ prox_28_circ | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == FALSE))
m_nat_noben <- feols(trust_can ~ prox_28_circ | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == FALSE))

modelsummary(
  list("All" = m_all,
       "Beneficiaries" = m_ben,
       "Non-Ben (Placebo)" = m_noben,
       "Imm + Ben" = m_imm_ben,
       "Imm + Non-Ben" = m_imm_noben,
       "Native + Ben" = m_nat_ben,
       "Native + Non-Ben" = m_nat_noben),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_rename = c("prox_28_circ" = "Circular Distance (Days)"),
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Trust in Canadian Government ~ Circular Distance to Payment (Day 28)"
)
```

## Attachment to Quebec

```{r fe-attach-qc}
m_all <- feols(attachment_qc ~ prox_28_circ | ID, data = df)
m_ben <- feols(attachment_qc ~ prox_28_circ | ID,
               data = df %>% filter(ben_housingbnft == 1))
m_noben <- feols(attachment_qc ~ prox_28_circ | ID,
                 data = df %>% filter(ben_housingbnft == 0))
m_imm_ben <- feols(attachment_qc ~ prox_28_circ | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == TRUE))
m_imm_noben <- feols(attachment_qc ~ prox_28_circ | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == TRUE))
m_nat_ben <- feols(attachment_qc ~ prox_28_circ | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == FALSE))
m_nat_noben <- feols(attachment_qc ~ prox_28_circ | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == FALSE))

modelsummary(
  list("All" = m_all,
       "Beneficiaries" = m_ben,
       "Non-Ben (Placebo)" = m_noben,
       "Imm + Ben" = m_imm_ben,
       "Imm + Non-Ben" = m_imm_noben,
       "Native + Ben" = m_nat_ben,
       "Native + Non-Ben" = m_nat_noben),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_rename = c("prox_28_circ" = "Circular Distance (Days)"),
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Attachment to QC ~ Circular Distance to Payment (Day 28)"
)
```

## Financial Satisfaction

```{r fe-financial}
m_all <- feols(financial_satisf ~ prox_28_circ | ID, data = df)
m_ben <- feols(financial_satisf ~ prox_28_circ | ID,
               data = df %>% filter(ben_housingbnft == 1))
m_noben <- feols(financial_satisf ~ prox_28_circ | ID,
                 data = df %>% filter(ben_housingbnft == 0))
m_imm_ben <- feols(financial_satisf ~ prox_28_circ | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == TRUE))
m_imm_noben <- feols(financial_satisf ~ prox_28_circ | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == TRUE))
m_nat_ben <- feols(financial_satisf ~ prox_28_circ | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == FALSE))
m_nat_noben <- feols(financial_satisf ~ prox_28_circ | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == FALSE))

modelsummary(
  list("All" = m_all,
       "Beneficiaries" = m_ben,
       "Non-Ben (Placebo)" = m_noben,
       "Imm + Ben" = m_imm_ben,
       "Imm + Non-Ben" = m_imm_noben,
       "Native + Ben" = m_nat_ben,
       "Native + Non-Ben" = m_nat_noben),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_rename = c("prox_28_circ" = "Circular Distance (Days)"),
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Financial Satisfaction ~ Circular Distance to Payment (Day 28)"
)
```

## Importance of Quebec Values

```{r fe-qcvalues}
m_all <- feols(imp_qcvalues ~ prox_28_circ | ID, data = df)
m_ben <- feols(imp_qcvalues ~ prox_28_circ | ID,
               data = df %>% filter(ben_housingbnft == 1))
m_noben <- feols(imp_qcvalues ~ prox_28_circ | ID,
                 data = df %>% filter(ben_housingbnft == 0))
m_imm_ben <- feols(imp_qcvalues ~ prox_28_circ | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == TRUE))
m_imm_noben <- feols(imp_qcvalues ~ prox_28_circ | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == TRUE))
m_nat_ben <- feols(imp_qcvalues ~ prox_28_circ | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == FALSE))
m_nat_noben <- feols(imp_qcvalues ~ prox_28_circ | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == FALSE))

modelsummary(
  list("All" = m_all,
       "Beneficiaries" = m_ben,
       "Non-Ben (Placebo)" = m_noben,
       "Imm + Ben" = m_imm_ben,
       "Imm + Non-Ben" = m_imm_noben,
       "Native + Ben" = m_nat_ben,
       "Native + Non-Ben" = m_nat_noben),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_rename = c("prox_28_circ" = "Circular Distance (Days)"),
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Importance of Quebec Values ~ Circular Distance to Payment (Day 28)"
)
```

## Attachment to Canada

```{r fe-attach-can}
m_all <- feols(attachment_can ~ prox_28_circ | ID, data = df)
m_ben <- feols(attachment_can ~ prox_28_circ | ID,
               data = df %>% filter(ben_housingbnft == 1))
m_noben <- feols(attachment_can ~ prox_28_circ | ID,
                 data = df %>% filter(ben_housingbnft == 0))
m_imm_ben <- feols(attachment_can ~ prox_28_circ | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == TRUE))
m_imm_noben <- feols(attachment_can ~ prox_28_circ | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == TRUE))
m_nat_ben <- feols(attachment_can ~ prox_28_circ | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == FALSE))
m_nat_noben <- feols(attachment_can ~ prox_28_circ | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == FALSE))

modelsummary(
  list("All" = m_all,
       "Beneficiaries" = m_ben,
       "Non-Ben (Placebo)" = m_noben,
       "Imm + Ben" = m_imm_ben,
       "Imm + Non-Ben" = m_imm_noben,
       "Native + Ben" = m_nat_ben,
       "Native + Non-Ben" = m_nat_noben),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_rename = c("prox_28_circ" = "Circular Distance (Days)"),
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Attachment to Canada ~ Circular Distance to Payment (Day 28)"
)
```

# Panel Fixed Effects Models (Days Since Payment)

These models use `prox_28_since` — directional measure of days elapsed since last payment (0-29).

## Trust in Quebec Government

```{r fe-since-trust-qc}
m_all <- feols(trust_qc ~ prox_28_since | ID, data = df)
m_ben <- feols(trust_qc ~ prox_28_since | ID,
               data = df %>% filter(ben_housingbnft == 1))
m_noben <- feols(trust_qc ~ prox_28_since | ID,
                 data = df %>% filter(ben_housingbnft == 0))
m_imm_ben <- feols(trust_qc ~ prox_28_since | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == TRUE))
m_imm_noben <- feols(trust_qc ~ prox_28_since | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == TRUE))
m_nat_ben <- feols(trust_qc ~ prox_28_since | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == FALSE))
m_nat_noben <- feols(trust_qc ~ prox_28_since | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == FALSE))

modelsummary(
  list("All" = m_all,
       "Beneficiaries" = m_ben,
       "Non-Ben (Placebo)" = m_noben,
       "Imm + Ben" = m_imm_ben,
       "Imm + Non-Ben" = m_imm_noben,
       "Native + Ben" = m_nat_ben,
       "Native + Non-Ben" = m_nat_noben),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_rename = c("prox_28_since" = "Days Since Payment"),
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Trust in QC Government ~ Days Since Payment (Day 28)"
)
```

## Trust in Canadian Government

```{r fe-since-trust-can}
m_all <- feols(trust_can ~ prox_28_since | ID, data = df)
m_ben <- feols(trust_can ~ prox_28_since | ID,
               data = df %>% filter(ben_housingbnft == 1))
m_noben <- feols(trust_can ~ prox_28_since | ID,
                 data = df %>% filter(ben_housingbnft == 0))
m_imm_ben <- feols(trust_can ~ prox_28_since | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == TRUE))
m_imm_noben <- feols(trust_can ~ prox_28_since | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == TRUE))
m_nat_ben <- feols(trust_can ~ prox_28_since | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == FALSE))
m_nat_noben <- feols(trust_can ~ prox_28_since | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == FALSE))

modelsummary(
  list("All" = m_all,
       "Beneficiaries" = m_ben,
       "Non-Ben (Placebo)" = m_noben,
       "Imm + Ben" = m_imm_ben,
       "Imm + Non-Ben" = m_imm_noben,
       "Native + Ben" = m_nat_ben,
       "Native + Non-Ben" = m_nat_noben),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_rename = c("prox_28_since" = "Days Since Payment"),
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Trust in Canadian Government ~ Days Since Payment (Day 28)"
)
```

## Attachment to Quebec

```{r fe-since-attach-qc}
m_all <- feols(attachment_qc ~ prox_28_since | ID, data = df)
m_ben <- feols(attachment_qc ~ prox_28_since | ID,
               data = df %>% filter(ben_housingbnft == 1))
m_noben <- feols(attachment_qc ~ prox_28_since | ID,
                 data = df %>% filter(ben_housingbnft == 0))
m_imm_ben <- feols(attachment_qc ~ prox_28_since | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == TRUE))
m_imm_noben <- feols(attachment_qc ~ prox_28_since | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == TRUE))
m_nat_ben <- feols(attachment_qc ~ prox_28_since | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == FALSE))
m_nat_noben <- feols(attachment_qc ~ prox_28_since | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == FALSE))

modelsummary(
  list("All" = m_all,
       "Beneficiaries" = m_ben,
       "Non-Ben (Placebo)" = m_noben,
       "Imm + Ben" = m_imm_ben,
       "Imm + Non-Ben" = m_imm_noben,
       "Native + Ben" = m_nat_ben,
       "Native + Non-Ben" = m_nat_noben),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_rename = c("prox_28_since" = "Days Since Payment"),
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Attachment to QC ~ Days Since Payment (Day 28)"
)
```

## Financial Satisfaction

```{r fe-since-financial}
m_all <- feols(financial_satisf ~ prox_28_since | ID, data = df)
m_ben <- feols(financial_satisf ~ prox_28_since | ID,
               data = df %>% filter(ben_housingbnft == 1))
m_noben <- feols(financial_satisf ~ prox_28_since | ID,
                 data = df %>% filter(ben_housingbnft == 0))
m_imm_ben <- feols(financial_satisf ~ prox_28_since | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == TRUE))
m_imm_noben <- feols(financial_satisf ~ prox_28_since | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == TRUE))
m_nat_ben <- feols(financial_satisf ~ prox_28_since | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == FALSE))
m_nat_noben <- feols(financial_satisf ~ prox_28_since | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == FALSE))

modelsummary(
  list("All" = m_all,
       "Beneficiaries" = m_ben,
       "Non-Ben (Placebo)" = m_noben,
       "Imm + Ben" = m_imm_ben,
       "Imm + Non-Ben" = m_imm_noben,
       "Native + Ben" = m_nat_ben,
       "Native + Non-Ben" = m_nat_noben),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_rename = c("prox_28_since" = "Days Since Payment"),
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Financial Satisfaction ~ Days Since Payment (Day 28)"
)
```

## Importance of Quebec Values

```{r fe-since-qcvalues}
m_all <- feols(imp_qcvalues ~ prox_28_since | ID, data = df)
m_ben <- feols(imp_qcvalues ~ prox_28_since | ID,
               data = df %>% filter(ben_housingbnft == 1))
m_noben <- feols(imp_qcvalues ~ prox_28_since | ID,
                 data = df %>% filter(ben_housingbnft == 0))
m_imm_ben <- feols(imp_qcvalues ~ prox_28_since | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == TRUE))
m_imm_noben <- feols(imp_qcvalues ~ prox_28_since | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == TRUE))
m_nat_ben <- feols(imp_qcvalues ~ prox_28_since | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == FALSE))
m_nat_noben <- feols(imp_qcvalues ~ prox_28_since | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == FALSE))

modelsummary(
  list("All" = m_all,
       "Beneficiaries" = m_ben,
       "Non-Ben (Placebo)" = m_noben,
       "Imm + Ben" = m_imm_ben,
       "Imm + Non-Ben" = m_imm_noben,
       "Native + Ben" = m_nat_ben,
       "Native + Non-Ben" = m_nat_noben),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_rename = c("prox_28_since" = "Days Since Payment"),
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Importance of Quebec Values ~ Days Since Payment (Day 28)"
)
```

## Attachment to Canada

```{r fe-since-attach-can}
m_all <- feols(attachment_can ~ prox_28_since | ID, data = df)
m_ben <- feols(attachment_can ~ prox_28_since | ID,
               data = df %>% filter(ben_housingbnft == 1))
m_noben <- feols(attachment_can ~ prox_28_since | ID,
                 data = df %>% filter(ben_housingbnft == 0))
m_imm_ben <- feols(attachment_can ~ prox_28_since | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == TRUE))
m_imm_noben <- feols(attachment_can ~ prox_28_since | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == TRUE))
m_nat_ben <- feols(attachment_can ~ prox_28_since | ID,
                   data = df %>% filter(ben_housingbnft == 1 & immigrant == FALSE))
m_nat_noben <- feols(attachment_can ~ prox_28_since | ID,
                     data = df %>% filter(ben_housingbnft == 0 & immigrant == FALSE))

modelsummary(
  list("All" = m_all,
       "Beneficiaries" = m_ben,
       "Non-Ben (Placebo)" = m_noben,
       "Imm + Ben" = m_imm_ben,
       "Imm + Non-Ben" = m_imm_noben,
       "Native + Ben" = m_nat_ben,
       "Native + Non-Ben" = m_nat_noben),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_rename = c("prox_28_since" = "Days Since Payment"),
  gof_map = c("nobs", "r.squared.within", "FE: ID"),
  title = "Attachment to Canada ~ Days Since Payment (Day 28)"
)
```

# Summary

```{r summary-stats}
cat("=== SAMPLE SIZES ===\n")
cat("Total observations:", nrow(df), "\n")
cat("Housing benefit recipients:", sum(df$ben_housingbnft == 1), "\n")
cat("Non-recipients:", sum(df$ben_housingbnft == 0), "\n")
cat("\nBy immigrant status:\n")
cat("Immigrant beneficiaries:", sum(df$ben_housingbnft == 1 & df$immigrant == TRUE, na.rm = TRUE), "\n")
cat("Immigrant non-beneficiaries:", sum(df$ben_housingbnft == 0 & df$immigrant == TRUE, na.rm = TRUE), "\n")
cat("Native beneficiaries:", sum(df$ben_housingbnft == 1 & df$immigrant == FALSE, na.rm = TRUE), "\n")
cat("Native non-beneficiaries:", sum(df$ben_housingbnft == 0 & df$immigrant == FALSE, na.rm = TRUE), "\n")
```
