---
title: "Buying Love? How Government Benefits Shape Immigrant Political Attachment"
author: "Alex Ross^[Postdoctoral Researcher, Université Laval. alexander-frederick.ross.1@ulaval.ca]"
date: last-modified
date-format: "D MMMM, YYYY"
format:
  pdf:
    documentclass: article
    fig-cap-location: bottom
    tbl-cap-location: top
    toc: false
    number-sections: true
    fontsize: 12pt
    mainfont: "Times New Roman"
    include-in-header:
      text: |
        \usepackage{setspace}
        \doublespacing
crossref:
  fig-title: "Figure"
  tbl-title: "Table"
  fig-prefix: "Figure"
  tbl-prefix: "Table"
bibliography: references.bib
abstract: |
  Do government benefits shape recipients' political attitudes? I leverage quasi-random variation in survey timing relative to fixed monthly benefit payment dates among immigrants in Quebec to test whether proximity to payday affects attachment to government. Using a panel design with individual fixed effects, I find that proximity to benefit payments significantly increases immigrants' attachment to Quebec, financial satisfaction, and the importance they place on Quebec values and friendships. These effects pass multiple placebo tests: proximity to payment dates beneficiaries do *not* receive shows null effects, and full-time workers without benefits show no response to paycheck timing. Critically, payment proximity does not affect attitudes toward immigrants' origin countries, consistent with credit attribution to the benefit-providing government rather than general mood effects. Non-immigrant beneficiaries show weaker effects, suggesting that immigrants' more malleable political orientations are particularly responsive to material government support. These findings illuminate how welfare state policies may facilitate immigrant political integration.
---

\newpage

```{r setup}
#| include: false

rm(list = ls())

knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  error = FALSE,
  message = FALSE
)

pacman::p_load(
  tidyverse,
  lubridate,
  fixest,
  modelsummary,
  tinytable,
  ggthemes,
  marginaleffects
)

options(modelsummary_factory_default = "tinytable")
```

```{r load-data}
#| include: false

df <- readRDS("df_full_panel_both_samples.rds")

# Filter to respondents with >= 80% survey completion
df <- df %>%
  mutate(progress = as.numeric(progress)) %>%
  filter(progress >= 80)
```

```{r data-prep}
#| include: false

# Survey timing
df <- df %>%
  mutate(
    survey_datetime = as.POSIXct(startdate),
    survey_date = as.Date(survey_datetime),
    day_of_month = day(survey_datetime)
  )

# Outcome variables (0-10 scales)
df <- df %>%
  mutate(
    trust_qc = as.numeric(trust_qcgov),
    trust_can = as.numeric(trust_cangov),
    attachment_qc = as.numeric(attach_qc),
    attachment_can = as.numeric(attach_can),
    attachment_city = as.numeric(attach_city),
    financial_satisf = as.numeric(current_financialsatisf),
    life_satisf = as.numeric(current_lifesatisf),
    imp_qcvalues = as.numeric(imp_qcvalues),
    imp_qcfriends = as.numeric(imp_quebecerfriends),
    origin_trust_gov = as.numeric(origin_trustgovernment),
    origin_attachment = as.numeric(attach_origincountry),
    imp_valuesorigin = as.numeric(imp_valuesorigin),
    # Additional trust DVs
    qc_trust_people = as.numeric(qctrustpeople),
    trust_police = as.numeric(trust_police),
    trust_politicians = as.numeric(trust_politicians),
    # Origin trust DVs (placebos)
    origin_trust_people = as.numeric(origin_trustpeople),
    origin_trust_police = as.numeric(origin_trustpolice),
    origin_trust_politicians = as.numeric(origin_trustpoliticians)
  )

# Beneficiary status with panel propagation
df <- df %>%
  mutate(
    raw_childbnft = ifelse(!is.na(mprog_childbnft), 1, 0),
    raw_socasst = ifelse(!is.na(mprog_socasst), 1, 0),
    raw_basinc = ifelse(!is.na(mprog_basinc), 1, 0),
    raw_cfincsupp = ifelse(!is.na(mprog_cfincsupp), 1, 0),
    raw_housingbnft = ifelse(!is.na(mprog_housingbnft), 1, 0),
    raw_retpen = ifelse(!is.na(mprog_retpen), 1, 0),
    raw_dispen = ifelse(!is.na(mprog_dispen), 1, 0),
    raw_empinsur = ifelse(!is.na(mprog_empinsur), 1, 0),
    raw_subhousing = ifelse(!is.na(mprog_subhousing), 1, 0),
    raw_dentalbnft = ifelse(!is.na(mprog_dentalbnft), 1, 0),
    raw_studentfin = ifelse(!is.na(mprog_studentfin), 1, 0),
    raw_parentlv = ifelse(!is.na(mprog_parentlv), 1, 0),
    raw_other = ifelse(!is.na(mprog_other), 1, 0),
    selected_none = ifelse(!is.na(mprog_none), 1, 0),
    works_fulltime = ifelse(!is.na(occup_fulltime), 1, 0)
  )

# Calculate years in Quebec from wave 1 data
# yearqc has much better coverage than yearcan (638 vs 190 immigrant beneficiaries)
df <- df %>%
  mutate(yearqc_num = as.numeric(yearqc)) %>%
  group_by(ID) %>%
  mutate(
    # Get the wave 1 yearqc value and calculate years in Quebec as of 2023
    years_in_qc = 2023 - first(yearqc_num[wave == 1], default = NA_real_)
  ) %>%
  ungroup()

# Create household income as numeric scale (1-8)
# Using hhincome instead of personal income due to much better coverage
# (75% vs 18% for immigrants)
df <- df %>%
  mutate(
    hhincome_scale = case_when(
      hhincome == "No income" ~ 1,
      hhincome == "Between $1 and $29,999" ~ 2,
      hhincome == "Between $30,000 and $59,999" ~ 3,
      hhincome == "Between $60,000 and $89,999" ~ 4,
      hhincome == "Between $90,000 and $109,999" ~ 5,
      hhincome == "Between $110,000 and $149,999" ~ 6,
      hhincome == "Between $150,000 and $199,999" ~ 7,
      hhincome == "More than $200,000" ~ 8,
      TRUE ~ NA_real_
    )
  ) %>%
  # Fill missing income from any available wave for that person
  group_by(ID) %>%
  mutate(
    income_filled = if_else(
      is.na(hhincome_scale),
      first(na.omit(hhincome_scale)),
      hhincome_scale
    )
  ) %>%
  ungroup()

# Create French competency as numeric (0-10 scale)
# Fill missing values from any available wave for that person
df <- df %>%
  mutate(french_comp_num = as.numeric(french_competency)) %>%
  group_by(ID) %>%
  mutate(
    french_comp_filled = if_else(
      is.na(french_comp_num),
      first(na.omit(french_comp_num)),
      french_comp_num
    )
  ) %>%
  ungroup()

# Education as numeric (1-7 scale)
# Fill missing values from any available wave
df <- df %>%
  group_by(ID) %>%
  mutate(
    education_num_filled = if_else(
      is.na(education_num),
      first(na.omit(education_num)),
      education_num
    )
  ) %>%
  ungroup()

# Political and policy knowledge scores (already numeric, no filling needed)
# polknow_score: 0-4 (correct politician identifications)
# policyknow_score: 0-6 (correct policy answers)

ever_child <- df %>% filter(raw_childbnft == 1) %>% pull(ID) %>% unique()
ever_first <- df %>% filter(raw_socasst == 1 | raw_basinc == 1 | raw_cfincsupp == 1) %>% pull(ID) %>% unique()
ever_28 <- df %>% filter(raw_housingbnft == 1 | raw_retpen == 1 | raw_dispen == 1) %>% pull(ID) %>% unique()

ever_any_benefit <- df %>%
  filter(raw_childbnft == 1 | raw_socasst == 1 | raw_basinc == 1 | raw_cfincsupp == 1 |
         raw_housingbnft == 1 | raw_retpen == 1 | raw_dispen == 1 | raw_empinsur == 1 |
         raw_subhousing == 1 | raw_dentalbnft == 1 | raw_studentfin == 1 |
         raw_parentlv == 1 | raw_other == 1) %>%
  pull(ID) %>% unique()

df <- df %>%
  mutate(
    ben_20 = case_when(selected_none == 1 ~ 0, ID %in% ever_child ~ 1, TRUE ~ 0),
    ben_1 = case_when(selected_none == 1 ~ 0, ID %in% ever_first ~ 1, TRUE ~ 0),
    ben_28 = case_when(selected_none == 1 ~ 0, ID %in% ever_28 ~ 1, TRUE ~ 0),
    ben_any_fixed = ifelse(ben_20 == 1 | ben_1 == 1 | ben_28 == 1, 1, 0),
    ben_any_program = ifelse(ID %in% ever_any_benefit, 1, 0)
  )
```

```{r proximity}
#| include: false

days_since_vec <- function(survey_days, payment_day, days_in_month = 30) {
  sapply(survey_days, function(d) {
    if (is.na(d)) return(NA)
    if (d >= payment_day) d - payment_day else (days_in_month - payment_day) + d
  })
}

days_since_to_proximity <- function(days_since) {
  30 - days_since
}

df$days_since_1 <- days_since_vec(df$day_of_month, 1)
df$days_since_20 <- days_since_vec(df$day_of_month, 20)
df$days_since_28 <- days_since_vec(df$day_of_month, 28)

df$prox_1 <- days_since_to_proximity(df$days_since_1)
df$prox_20 <- days_since_to_proximity(df$days_since_20)
df$prox_28 <- days_since_to_proximity(df$days_since_28)

df <- df %>%
  mutate(
    prox_actual = case_when(
      ben_any_fixed == 0 ~ NA_real_,
      ben_1 == 1 & ben_20 == 0 & ben_28 == 0 ~ prox_1,
      ben_1 == 0 & ben_20 == 1 & ben_28 == 0 ~ prox_20,
      ben_1 == 0 & ben_20 == 0 & ben_28 == 1 ~ prox_28,
      ben_1 == 1 & ben_20 == 1 & ben_28 == 0 ~ pmax(prox_1, prox_20),
      ben_1 == 1 & ben_20 == 0 & ben_28 == 1 ~ pmax(prox_1, prox_28),
      ben_1 == 0 & ben_20 == 1 & ben_28 == 1 ~ pmax(prox_20, prox_28),
      ben_1 == 1 & ben_20 == 1 & ben_28 == 1 ~ pmax(prox_1, prox_20, prox_28),
      TRUE ~ NA_real_
    )
  )
```

```{r wrong-date}
#| include: false

df <- df %>%
  mutate(
    wrong_1_min_dist = case_when(
      ben_1 == 1 ~ NA_real_,
      ben_20 == 1 & ben_28 == 1 ~ pmin(11, 3),
      ben_20 == 1 & ben_28 == 0 ~ 11,
      ben_20 == 0 & ben_28 == 1 ~ 3,
      TRUE ~ NA_real_
    ),
    wrong_20_min_dist = case_when(
      ben_20 == 1 ~ NA_real_,
      ben_1 == 1 & ben_28 == 1 ~ pmin(11, 8),
      ben_1 == 1 & ben_28 == 0 ~ 11,
      ben_1 == 0 & ben_28 == 1 ~ 8,
      TRUE ~ NA_real_
    ),
    wrong_28_min_dist = case_when(
      ben_28 == 1 ~ NA_real_,
      ben_1 == 1 & ben_20 == 1 ~ pmin(3, 8),
      ben_1 == 1 & ben_20 == 0 ~ 3,
      ben_1 == 0 & ben_20 == 1 ~ 8,
      TRUE ~ NA_real_
    )
  )

df <- df %>%
  rowwise() %>%
  mutate(
    best_wrong_date = {
      dists <- c(wrong_1_min_dist, wrong_20_min_dist, wrong_28_min_dist)
      dates <- c(1, 20, 28)
      if (all(is.na(dists))) NA_real_ else dates[which.max(dists)]
    }
  ) %>%
  ungroup()

df <- df %>%
  mutate(
    prox_wrong = case_when(
      is.na(best_wrong_date) ~ NA_real_,
      best_wrong_date == 1 ~ prox_1,
      best_wrong_date == 20 ~ prox_20,
      best_wrong_date == 28 ~ prox_28
    )
  )
```

```{r samples}
#| include: false

df_ben <- df %>% filter(ben_any_fixed == 1, !is.na(best_wrong_date))
df_imm <- df_ben %>% filter(immigrant == TRUE)
df_nat <- df_ben %>% filter(immigrant == FALSE)

df_ft_noben <- df %>%
  filter(works_fulltime == 1, ben_any_program == 0) %>%
  mutate(
    days_since_31 = days_since_vec(day_of_month, 31),
    prox_31 = days_since_to_proximity(days_since_31)
  )
df_ft_noben_imm <- df_ft_noben %>% filter(immigrant == TRUE)

n_imm <- nrow(df_imm)
n_imm_id <- n_distinct(df_imm$ID)
n_nat <- nrow(df_nat)
n_nat_id <- n_distinct(df_nat$ID)
n_paycheck <- nrow(df_ft_noben_imm)
n_paycheck_id <- n_distinct(df_ft_noben_imm$ID)

# Exclusive CCB recipients (for methods section reference)
n_ccb_imm <- df %>%
  filter(immigrant == TRUE, ben_20 == 1, ben_1 == 0, ben_28 == 0) %>%
  pull(ID) %>% n_distinct()
```

# Introduction

One of the most contentious topics in popular discourse about immigration is the receipt—real or imagined—of welfare benefits by immigrants. Claims about immigrant welfare use feature prominently in the rhetoric of those who seek to restrict immigration, framing benefit receipt as taking from a more "deserving" native-born population. This framing reflects what scholars term "welfare chauvinism": the view that social benefits should be reserved primarily for natives rather than newcomers [@ennserjedenastik2018; @careja2022]. Such rhetoric has found expression across Western democracies. In the United States, the Trump administration's expansion of the "public charge" rule penalized immigrants for using Medicaid, food assistance, or housing benefits, explicitly framing welfare receipt as grounds for denying residency [@trump_publiccharge2019; @mpi_publiccharge2024]. In France, Marine Le Pen's *Rassemblement National* has long advocated *préférence nationale*—reserving social benefits, housing, and employment for French citizens—a policy that influenced the restrictive 2023 immigration law [@lepen_preference2022]. In the United Kingdom, UKIP's claims that immigrants engage in "health tourism" costing billions annually shaped public debate despite evidence that actual costs amount to less than 0.1 percent of NHS expenditure [@farage_healthtourism2015; @king_healthtourism2015].

Research consistently shows that attitudes toward immigration shape support for the welfare state, with those holding anti-immigrant views less willing to fund redistributive programs [@garand2017; @burgoon2021]. Yet while a large literature examines how *native* attitudes toward immigrants intersect with welfare preferences, remarkably little work investigates the reverse: how receiving welfare benefits affects the political attitudes of *immigrants themselves*. This gap persists despite evidence that immigrants' political orientations are not fixed but evolve substantially after arrival [@dinesen2012; @just2017; @superti2022], and despite arguments from settlement policy advocates that access to public benefits facilitates economic and social integration [@oecd_integration2023]. The existing work that does address immigrant benefit receipt suffers from several challenges: the difficulty of surveying recently arrived immigrants, the endogeneity of benefit receipt to the very attitudes researchers wish to study, and the limitations of cross-sectional data for capturing individuals during a period of rapid change.

This paper addresses that gap—and the stakes extend beyond academic debates about credit attribution. Political belonging is itself a core dimension of immigrant integration, sitting alongside economic participation, social connections, and civic engagement in leading frameworks for understanding how newcomers become members of their new societies [@agerstrang2008; @fouka2023]. If welfare benefits shape political attachment, they may constitute an underappreciated mechanism of integration—one operating through the everyday experience of receiving government support rather than through formal citizenship classes or settlement programs. This possibility carries normative implications: welfare chauvinism rests on an implicit assumption that extending benefits to immigrants yields few returns for host societies. But if benefit receipt builds precisely the political belonging that receiving societies desire from immigrants, then restricting access may be counterproductive. Understanding whether benefits affect immigrant attachment thus speaks not only to political behavior scholarship but to foundational questions about how democracies should approach immigrant incorporation.

How do citizens come to trust, feel attached to, and participate in their political community? A substantial literature in political behavior examines how welfare state policies shape these fundamental orientations. Policy feedback research demonstrates that encounters with government programs influence citizens' political engagement and participation [@campbell2012; @kumlin2014], their understanding of what government does for them [@mettler2011], and their broader sense of political efficacy and trust [@soss1999]. The mechanisms are both material and interpretive: policies provide resources that facilitate political action while simultaneously sending signals about citizens' standing in the polity [@pierson1993]. Yet establishing causal effects has proven difficult. Citizens who receive government benefits differ systematically from those who do not, and benefit receipt is endogenous to the very political attitudes researchers seek to explain.

Two additional limitations constrain the literature. First, most research focuses on "submerged" policies like tax expenditures, where benefits are invisible and citizens often fail to recognize government's role [@mettler2011]. Direct cash transfers—the most visible form of government support—remain understudied despite their theoretical importance for credit attribution. Second, nearly all policy feedback research examines established citizens in consolidated democracies, whose political orientations crystallized long ago. We know far less about how government benefits affect immigrants, a population whose attachments to their new country are actively forming and potentially far more responsive to material signals from the state. With nearly one in five residents of developed democracies now foreign-born, understanding how welfare state contact shapes immigrant political integration has become a first-order question for democratic politics.

This paper investigates whether government benefit payments shape immigrants' political attitudes toward their host society. I exploit a natural experiment arising from the timing of survey responses relative to fixed monthly benefit payment dates. Because the exact day a respondent completes a survey is essentially random with respect to the benefit payment schedule, proximity to payday provides quasi-exogenous variation in recent material support from government. Using panel data with individual fixed effects, I test whether being closer to one's most recent benefit payment predicts warmer attitudes toward Quebec and Canada.

The theoretical logic is straightforward: if government benefits create feelings of gratitude or material security that generalize to political attitudes, we should observe more positive orientations immediately following payment. This "credit attribution" mechanism [@healy2017] suggests that tangible government support makes abstract notions of state beneficence concrete and salient. For immigrants in particular, regular benefit payments may serve as repeated signals that the host society provides for them, potentially accelerating political integration.

I find strong support for this hypothesis among immigrant benefit recipients in Quebec. Proximity to payday significantly increases attachment to Quebec, financial satisfaction, and the importance immigrants place on Quebec values and having Quebecer friends. These effects survive multiple demanding placebo tests. First, proximity to payment dates that beneficiaries do *not* receive shows null effects—confirming that the actual payment date specifically matters. Second, full-time workers who receive no government benefits show no response to end-of-month timing, ruling out generic "time of month" confounds. Third, payment proximity does not affect immigrants' attitudes toward their origin countries, consistent with credit being attributed specifically to the benefit-providing government rather than general mood improvement.

Importantly, non-immigrant beneficiaries show substantially weaker effects. This pattern suggests that immigrants' political orientations, still in formation, are particularly responsive to material signals from government. The findings illuminate how welfare state policies may serve as mechanisms of immigrant political integration—not through explicit civic education, but through repeated, tangible demonstrations of state support. More broadly, the results challenge the implicit premise of welfare chauvinism: that extending benefits to immigrants serves only the immigrants themselves. If benefit receipt builds political belonging, then access to the welfare state may be precisely the kind of policy that helps produce the integrated, attached citizens that receiving societies seek.

# Data and Methods

## Context: Immigration and Integration in Quebec

Quebec occupies a distinctive position within Canadian immigration policy. While the federal government sets overall immigration targets and administers most entry categories, Quebec maintains substantial autonomy over immigrant selection and integration through the Canada-Quebec Accord. The province selects a majority of its economic immigrants and operates its own settlement and integration programs [@bouchard2011].

Quebec's approach to immigrant integration differs from the Canadian federal model of multiculturalism. The province embraces "interculturalism," which emphasizes French as the common public language, encourages intercultural exchange, and promotes a shared civic identity while respecting cultural pluralism in private life. This framework places particular importance on immigrants developing attachment to Quebec society and adopting its core values—making measures of Quebec attachment theoretically important indicators of integration success.

Quebec also operates an extensive welfare state that provides numerous benefits to residents regardless of immigration status. Many immigrants—particularly recent arrivals who may face labor market challenges during settlement—receive government transfers including the Canada Child Benefit, Quebec Social Assistance, housing benefits, and various pension and disability programs. These programs represent regular, tangible contact between immigrants and the state, potentially shaping perceptions of how the host society treats newcomers.

## Survey Data

I analyze data from a three-wave panel survey of Quebec residents conducted between 2023 and 2025 [@maheo2024]. This dataset offers unusual advantages for studying immigrant political attitudes. Recent immigrants constitute a notoriously hard-to-reach population for survey research: language barriers, residential instability, unfamiliarity with academic surveys, and wariness of government-affiliated contact all contribute to low response rates and unrepresentative samples in most studies. Longitudinal data on recent immigrants is rarer still—while scholars have long recognized the value of tracking integration trajectories over time, most research relies on cross-sectional snapshots that cannot disentangle individual change from cohort differences.

The present survey addresses these challenges through two design features. First, the immigrant sample was drawn from Quebec's official immigration registry maintained by the Ministère de l'Immigration, de la Francisation et de l'Intégration (MIFI), rather than convenience sampling or opt-in panels. MIFI selected 10,000 adult immigrants who had arrived in Quebec within the preceding five years, capturing the critical early integration period when attitudes toward the host society are actively forming. Registry-based sampling ensures that respondents are representative of the recent immigrant population rather than self-selected based on interest in surveys or civic engagement. Second, the panel design with individual fixed effects allows me to observe within-person attitude change—a substantial improvement over cross-sectional comparisons that conflate individual trajectories with compositional differences across cohorts.

Wave 1 was fielded in May-June 2023 and achieved a 26% response rate among contacted immigrants, with 1,831 respondents completing at least 80% of the survey. Wave 2 (May-July 2024) retained 74% of Wave 1 respondents—a strong retention rate for a hard-to-reach population that addresses concerns about panel attrition. Wave 3 was conducted in May-July 2025. The survey also includes a comparison sample of non-immigrants recruited through separate panels. Following standard practice, I restrict the analysis to respondents who completed at least 80% of survey questions.

The survey covers a range of topics relevant to immigrant integration, including attitudes toward Quebec and Canada, attachment to places of residence and origin, social networks, language use, and—critically for this study—detailed questions about government benefit receipt. Respondents indicated which, if any, of thirteen government transfer programs they currently receive.

My primary sample consists of `r n_imm_id` immigrant beneficiaries observed across `r n_imm` person-waves. For comparison, I analyze `r n_nat_id` non-immigrant beneficiaries (`r n_nat` person-waves) and `r n_paycheck_id` immigrant full-time workers who receive no government benefits (`r n_paycheck` person-waves).

## Identification Strategy

The key challenge in estimating how government benefits affect political attitudes is that benefit receipt is endogenous—people who receive benefits likely differ from non-recipients in ways that also shape their political orientations. Rather than comparing beneficiaries to non-beneficiaries, I exploit *timing* variation within beneficiaries to identify effects.

Several major benefit programs have fixed monthly disbursement dates [@canada_benefits_calendar2025; @retraite_quebec_dates2025]. I focus on three payment dates with substantial recipient populations:

-   **1st of the month**: Quebec Social Assistance and Social Solidarity programs provide monthly income support to individuals with limited resources, with benefits varying by household composition and work capacity [@quebec_social_assistance2025]. The federal Basic Income Program and Community Futures Income Support are also disbursed on the 1st.

-   **20th of the month**: The Canada Child Benefit (CCB) is a tax-free monthly payment to eligible families with children under 18 [@cra_ccb2025; @cra_ccb_dates2025]. As of 2025, maximum annual benefits are \$7,997 per child under 6 (\$666 monthly) and \$6,748 per child aged 6-17 (\$562 monthly), with benefits gradually reduced for families with adjusted net income above \$37,487.

-   **28th of the month**: Government pensions including the Canada Pension Plan (CPP), Quebec Pension Plan (QPP), and Old Age Security (OAS) are paid on this date, as are provincial housing benefits [@retraite_quebec_dates2025].

I conduct two complementary analyses. First, I pool all recipients of these fixed-date programs to maximize statistical power. For beneficiaries receiving multiple programs with different payment dates, I use proximity to whichever payment is most recent (i.e., the maximum proximity across their programs). Second, I analyze Canada Child Benefit recipients separately. The CCB is particularly well-suited for this analysis because it has the largest number of *exclusive* recipients—immigrants who receive CCB but no other fixed-date government benefit (`r n_ccb_imm` individuals). This allows for cleaner identification, as proximity to the 20th can only reflect CCB payments for these recipients.

Crucially, the specific day a respondent completes the survey—relative to their benefit payment schedule—is essentially random. Respondents did not choose their survey completion date based on when they would be paid; survey invitations arrived independently of benefit schedules.

I construct a "proximity to payday" measure for each beneficiary:

$$\text{Proximity} = 30 - \text{Days Since Payment}$$

This yields a scale from 1 (payment was 29 days ago) to 30 (payment day).

## Balance Checks

The identification strategy assumes that survey completion timing is as-if random with respect to benefit receipt and other respondent characteristics. I test this assumption in two ways. First, I examine whether day of month predicts benefit receipt among all immigrant respondents—if timing were systematically related to beneficiary status, this would threaten the design. Second, because respondents received a small payment for completing the survey, I test whether higher-income respondents systematically complete surveys on different days than lower-income respondents, which could introduce confounding if income-related financial pressures vary across the month.

```{r balance-checks}
#| include: false

# Subset to immigrants for balance checks
df_imm_all <- df %>% filter(immigrant == TRUE)

# Balance check 1: Does day of month predict beneficiary status?
balance_ben <- lm(ben_any_fixed ~ day_of_month, data = df_imm_all)
balance_ben_fstat <- summary(balance_ben)$fstatistic
balance_ben_p <- pf(balance_ben_fstat[1], balance_ben_fstat[2], balance_ben_fstat[3], lower.tail = FALSE)

# Balance check 2: Does income predict day of month (survey timing)?
# This tests whether higher-income people systematically complete surveys on different days
# Use income_filled (scale 1-8) as predictor
balance_inc <- lm(day_of_month ~ income_filled, data = df_imm_all)
balance_inc_fstat <- summary(balance_inc)$fstatistic
balance_inc_p <- pf(balance_inc_fstat[1], balance_inc_fstat[2], balance_inc_fstat[3], lower.tail = FALSE)

# Store results for inline reporting
ben_coef <- coef(balance_ben)["day_of_month"]
ben_se <- summary(balance_ben)$coefficients["day_of_month", "Std. Error"]
inc_coef <- coef(balance_inc)["income_filled"]
inc_se <- summary(balance_inc)$coefficients["income_filled", "Std. Error"]
```

@tbl-balance presents these balance checks. Day of month does not significantly predict beneficiary status ($\beta$ = `r sprintf("%.4f", ben_coef)`, SE = `r sprintf("%.4f", ben_se)`, $p$ = `r sprintf("%.3f", balance_ben_p)`), confirming that beneficiaries and non-beneficiaries are not systematically surveyed on different days. Similarly, income does not predict survey timing ($p$ = `r sprintf("%.3f", balance_inc_p)`), ruling out the concern that survey payment incentives induce differential timing by income level.

```{r tbl-balance}
#| label: tbl-balance
#| tbl-cap: "Balance Checks: Survey Timing and Respondent Characteristics (Immigrants)"

modelsummary(
  list(
    "Beneficiary Status" = balance_ben,
    "Day of Month" = balance_inc
  ),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_rename = c("day_of_month" = "Day of Month", "income_filled" = "Income (1-8 scale)"),
  coef_omit = "Intercept",
  gof_map = c("nobs", "r.squared"),
  output = "tinytable"
) |>
  theme_tt("striped") |>
  style_tt(j = 1, bold = TRUE) |>
  style_tt(fontsize = 0.9)
```

## Estimation

I estimate panel fixed effects models:

$$Y_{it} = \beta \cdot \text{Proximity}_{it} + \alpha_i + \varepsilon_{it}$$

where $Y_{it}$ is the outcome for individual $i$ at time $t$, and $\alpha_i$ are individual fixed effects that absorb all time-invariant characteristics. The coefficient $\beta$ captures the within-person effect of being one day closer to payday. Because individuals are observed across multiple survey waves—each fielded over a 6-8 week period—the same individual may be surveyed on different days of the month across waves, providing within-person variation in proximity.

All outcomes are measured on 0-10 scales where higher values indicate more of the construct (greater trust, stronger attachment, higher satisfaction).

## Placebo Tests

I implement three placebo tests to validate the identification strategy:

1.  **Wrong-date placebo**: For each beneficiary, I calculate proximity to a payment date they do *not* receive—specifically, the date most temporally distant from their actual payment date(s). For example, a beneficiary who receives only the Child Benefit (20th) has their wrong-date proximity calculated to the 1st, which is 11 days from the 20th. If effects are genuine, this placebo should be null—there is no reason proximity to an irrelevant payment date should matter.

2.  **Paycheck placebo**: I test whether full-time workers with no government benefits show similar patterns around the 31st (a common private-sector payday). If effects were merely "time of month" artifacts unrelated to government transfers, this should also be significant.

3.  **Origin country null**: I test whether proximity affects attitudes toward respondents' origin countries (attachment, values). The credit attribution mechanism predicts null effects here—Quebec/Canadian benefits should only affect attitudes toward Quebec/Canada, not generalized mood that spills over to all political attitudes.

# Results

## Main Effects and Placebo Tests

@fig-coef-plot presents the primary results for immigrant beneficiaries, displaying both the main treatment effects (proximity to actual payment date) and the wrong-date placebo test (proximity to a payment date the beneficiary does *not* receive). For each outcome, the top coefficient shows the effect of proximity to the respondent's actual benefit payment date, while the bottom coefficient shows the placebo test using proximity to an irrelevant payment date.

The pattern of results strongly supports the identification strategy. Proximity to payday significantly increases attachment to Quebec, financial satisfaction, and the importance immigrants place on Quebec values and having Quebecer friends. Crucially, these effects survive the wrong-date placebo: proximity to payment dates that beneficiaries do *not* receive shows null effects for most outcomes, confirming that the *actual* payment date specifically matters rather than generic time-of-month patterns.

The exception is trust in Quebec government, where both the main effect and the wrong-date placebo are significant—suggesting caution in interpreting the trust results. This pattern may reflect correlated timing across payment schedules or other confounds specific to trust measures.[^1]

[^1]: We use individual fixed effects only, not two-way (individual + wave) fixed effects. Adding wave fixed effects attenuates most results, likely because the more demanding specification removes legitimate variation: the identifying variation comes from within-person differences in survey timing across waves, and wave fixed effects partial this out.

```{r estimate-models}
#| include: false

# Main treatment effects
m1 <- feols(trust_qc ~ prox_actual | ID, data = df_imm)
m2 <- feols(trust_can ~ prox_actual | ID, data = df_imm)
m3 <- feols(attachment_qc ~ prox_actual | ID, data = df_imm)
m4 <- feols(attachment_can ~ prox_actual | ID, data = df_imm)
m5 <- feols(attachment_city ~ prox_actual | ID, data = df_imm)
m6 <- feols(financial_satisf ~ prox_actual | ID, data = df_imm)
m7 <- feols(life_satisf ~ prox_actual | ID, data = df_imm)
m8 <- feols(imp_qcvalues ~ prox_actual | ID, data = df_imm)
m9 <- feols(imp_qcfriends ~ prox_actual | ID, data = df_imm)

# Wrong-date placebo
p1 <- feols(trust_qc ~ prox_wrong | ID, data = df_imm)
p2 <- feols(trust_can ~ prox_wrong | ID, data = df_imm)
p3 <- feols(attachment_qc ~ prox_wrong | ID, data = df_imm)
p4 <- feols(attachment_can ~ prox_wrong | ID, data = df_imm)
p5 <- feols(attachment_city ~ prox_wrong | ID, data = df_imm)
p6 <- feols(financial_satisf ~ prox_wrong | ID, data = df_imm)
p7 <- feols(life_satisf ~ prox_wrong | ID, data = df_imm)
p8 <- feols(imp_qcvalues ~ prox_wrong | ID, data = df_imm)
p9 <- feols(imp_qcfriends ~ prox_wrong | ID, data = df_imm)
```

```{r fig-coef-plot}
#| label: fig-coef-plot
#| fig-cap: "Effect of Payment Proximity on Political Attitudes (Immigrant Beneficiaries)"
#| fig-height: 8
#| fig-width: 8

# Extract coefficients and create plotting data (fixest models)
extract_coef <- function(model, dv_name, model_type, coef_name) {
  coeftab <- coeftable(model)
  est <- coeftab[coef_name, "Estimate"]
  se <- coeftab[coef_name, "Std. Error"]
  pval <- coeftab[coef_name, "Pr(>|t|)"]
  stars <- case_when(
    pval < 0.01 ~ "***",
    pval < 0.05 ~ "**",
    pval < 0.1 ~ "*",
    TRUE ~ ""
  )
  tibble(
    outcome = dv_name,
    model = model_type,
    estimate = est,
    std.error = se,
    conf.low = est - 1.96 * se,
    conf.high = est + 1.96 * se,
    p.value = pval,
    stars = stars
  )
}

# Build coefficient dataset
coef_data <- bind_rows(
  extract_coef(m1, "Trust in QC Govt", "Benefit Payday", "prox_actual"),
  extract_coef(m2, "Trust in Canada Govt", "Benefit Payday", "prox_actual"),
  extract_coef(m3, "QC Attachment", "Benefit Payday", "prox_actual"),
  extract_coef(m4, "Canada Attachment", "Benefit Payday", "prox_actual"),
  extract_coef(m5, "City Attachment", "Benefit Payday", "prox_actual"),
  extract_coef(m6, "Financial Satisfaction", "Benefit Payday", "prox_actual"),
  extract_coef(m7, "Life Satisfaction", "Benefit Payday", "prox_actual"),
  extract_coef(m8, "QC Values Important", "Benefit Payday", "prox_actual"),
  extract_coef(m9, "QC Friends Important", "Benefit Payday", "prox_actual"),
  extract_coef(p1, "Trust in QC Govt", "Placebo Date", "prox_wrong"),
  extract_coef(p2, "Trust in Canada Govt", "Placebo Date", "prox_wrong"),
  extract_coef(p3, "QC Attachment", "Placebo Date", "prox_wrong"),
  extract_coef(p4, "Canada Attachment", "Placebo Date", "prox_wrong"),
  extract_coef(p5, "City Attachment", "Placebo Date", "prox_wrong"),
  extract_coef(p6, "Financial Satisfaction", "Placebo Date", "prox_wrong"),
  extract_coef(p7, "Life Satisfaction", "Placebo Date", "prox_wrong"),
  extract_coef(p8, "QC Values Important", "Placebo Date", "prox_wrong"),
  extract_coef(p9, "QC Friends Important", "Placebo Date", "prox_wrong")
)

# Set factor levels for ordering
coef_data <- coef_data %>%
  mutate(
    outcome = factor(outcome, levels = c(
      "Trust in QC Govt", "Trust in Canada Govt",
      "QC Attachment", "Canada Attachment", "City Attachment",
      "Financial Satisfaction", "Life Satisfaction",
      "QC Values Important", "QC Friends Important"
    )),
    model = factor(model, levels = c("Benefit Payday", "Placebo Date"))
  )

# Create coefficient plot
ggplot(coef_data, aes(x = estimate, y = model, color = model)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high), size = 0.5) +
  geom_text(aes(label = stars, x = conf.high), hjust = -0.2, vjust = 0.5,
            size = 5, show.legend = FALSE) +
  facet_wrap(~ outcome, ncol = 3, scales = "free_x") +
  scale_x_continuous(expand = expansion(mult = c(0.1, 0.2))) +
  scale_color_few(name = "Proximity to:") +
  coord_cartesian(clip = "off") +
  labs(
    x = "Coefficient Estimate (95% CI)",
    y = NULL
  ) +
  theme_tufte(base_size = 12) +
  theme(
    legend.position = "bottom",
    strip.text = element_text(face = "bold", size = 10),
    panel.spacing = unit(1.2, "lines"),
    axis.text.y = element_text(size = 10),
    axis.text.x = element_text(size = 9),
    axis.title.x = element_text(size = 11, margin = margin(t = 10)),
    plot.margin = margin(5, 15, 5, 5)
  )
```

@tbl-main provides detailed coefficient estimates for the main treatment effects.

```{r tbl-main}
#| label: tbl-main
#| tbl-cap: "Effect of Payment Proximity on Political Attitudes (Immigrant Beneficiaries)"

modelsummary(
  list(
    "QC" = m1, "CAN" = m2,
    "QC" = m3, "CAN" = m4, "City" = m5,
    "Financial" = m6, "Life" = m7,
    "Values" = m8, "Friends" = m9
  ),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = c("prox_actual" = "Proximity"),
  gof_map = c("nobs", "FE: ID"),
  output = "tinytable"
) |>
  group_tt(j = list("Trust in\ngovt. of:" = 2:3, "Attachment\nto:" = 4:6, "Satisfaction\nwith:" = 7:8, "Importance of QC" = 9:10)) |>
  theme_tt("striped") |>
  theme_tt("resize") |>
  style_tt(j = 1, bold = TRUE) |>
  style_tt(fontsize = 0.8)
```

## Paycheck Placebo

@tbl-placebo-paycheck tests whether the effects are merely generic "time of month" patterns unrelated to government benefits. I examine full-time workers who receive no government benefits, testing whether proximity to the 31st (a common private-sector payday) predicts their political attitudes. If the main results simply reflected mood cycles tied to any income receipt, this sample should show similar patterns.

The null results confirm that the effects are specific to government benefit receipt. Full-time workers without benefits show no relationship between end-of-month timing and political attitudes, ruling out generic income-timing confounds.

```{r tbl-placebo-paycheck}
#| label: tbl-placebo-paycheck
#| tbl-cap: "Paycheck Placebo: Full-Time Workers with No Government Benefits (Immigrants)"

c1 <- feols(trust_qc ~ prox_31 | ID, data = df_ft_noben_imm)
c2 <- feols(trust_can ~ prox_31 | ID, data = df_ft_noben_imm)
c3 <- feols(attachment_qc ~ prox_31 | ID, data = df_ft_noben_imm)
c4 <- feols(attachment_city ~ prox_31 | ID, data = df_ft_noben_imm)
c5 <- feols(life_satisf ~ prox_31 | ID, data = df_ft_noben_imm)
c6 <- feols(imp_qcvalues ~ prox_31 | ID, data = df_ft_noben_imm)
c7 <- feols(imp_qcfriends ~ prox_31 | ID, data = df_ft_noben_imm)

modelsummary(
  list(
    "QC" = c1, "CAN" = c2,
    "QC" = c3, "City" = c4,
    "Life" = c5, "Values" = c6, "Friends" = c7
  ),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = c("prox_31" = "Proximity (31st)"),
  gof_map = c("nobs", "FE: ID"),
  output = "tinytable"
) |>
  group_tt(j = list("Trust in\ngovt. of:" = 2:3, "Attachment\nto:" = 4:5, "Satisfaction\nwith:" = 6, "Importance of QC" = 7:8)) |>
  theme_tt("striped") |>
  theme_tt("resize") |>
  style_tt(j = 1, bold = TRUE) |>
  style_tt(fontsize = 0.8)
```

## Origin Country Attitudes

@tbl-origin tests the credit attribution mechanism. If benefit payments improve attitudes specifically toward the benefit-providing government—rather than simply improving mood generally—we should observe null effects on attitudes toward respondents' origin countries. The Quebec government provides the benefits; attitudes toward origin countries should be unaffected.

The results support credit attribution. Proximity to payday does not significantly affect attachment to origin country or the importance placed on origin country values. This pattern suggests that the main effects reflect targeted credit to Quebec/Canada rather than diffuse mood improvement.

```{r tbl-origin}
#| label: tbl-origin
#| tbl-cap: "Origin Country Outcomes: Test of Credit Attribution (Immigrant Beneficiaries)"

o1 <- feols(origin_attachment ~ prox_actual | ID, data = df_imm)
o2 <- feols(imp_valuesorigin ~ prox_actual | ID, data = df_imm)

modelsummary(
  list(
    "Attachment\nto:" = o1,
    "Values" = o2
  ),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = c("prox_actual" = "Proximity"),
  gof_map = c("nobs", "FE: ID"),
  output = "tinytable"
) |>
  group_tt(j = list("Origin Country" = 2:3)) |>
  theme_tt("striped") |>
  theme_tt("resize") |>
  style_tt(j = 1, bold = TRUE) |>
  style_tt(fontsize = 0.8)
```

## Non-Immigrant Comparison

@tbl-nonimm presents results for non-immigrant beneficiaries. If immigrants' more malleable political orientations make them particularly responsive to material government support, we should observe weaker effects among non-immigrants whose attachments are presumably more crystallized.

The results confirm this expectation. Non-immigrant beneficiaries show substantially weaker and generally non-significant effects of payment proximity on political attitudes. This pattern suggests that the political integration benefits of welfare state support may be concentrated among populations whose orientations are still forming.

```{r tbl-nonimm}
#| label: tbl-nonimm
#| tbl-cap: "Effect of Payment Proximity on Political Attitudes (Non-Immigrant Beneficiaries)"

n1 <- feols(trust_qc ~ prox_actual | ID, data = df_nat)
n2 <- feols(trust_can ~ prox_actual | ID, data = df_nat)
n3 <- feols(attachment_qc ~ prox_actual | ID, data = df_nat)
n4 <- feols(attachment_can ~ prox_actual | ID, data = df_nat)
n5 <- feols(attachment_city ~ prox_actual | ID, data = df_nat)
n6 <- feols(financial_satisf ~ prox_actual | ID, data = df_nat)
n7 <- feols(life_satisf ~ prox_actual | ID, data = df_nat)
n8 <- feols(imp_qcvalues ~ prox_actual | ID, data = df_nat)
n9 <- feols(imp_qcfriends ~ prox_actual | ID, data = df_nat)

modelsummary(
  list(
    "QC" = n1, "CAN" = n2,
    "QC" = n3, "CAN" = n4, "City" = n5,
    "Financial" = n6, "Life" = n7,
    "Values" = n8, "Friends" = n9
  ),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = c("prox_actual" = "Proximity"),
  gof_map = c("nobs", "FE: ID"),
  output = "tinytable"
) |>
  group_tt(j = list("Trust in\ngovt. of:" = 2:3, "Attachment\nto:" = 4:6, "Satisfaction\nwith:" = 7:8, "Importance of QC" = 9:10)) |>
  theme_tt("striped") |>
  theme_tt("resize") |>
  style_tt(j = 1, bold = TRUE) |>
  style_tt(fontsize = 0.8)
```

## Canada Child Benefit Recipients

```{r ccb-sample-prep}
#| include: false

# Exclusive CCB recipients - immigrants
df_ccb_imm <- df_imm %>%
  filter(ben_20 == 1, ben_1 == 0, ben_28 == 0)

# Exclusive CCB recipients - non-immigrants
df_ccb_nat <- df_nat %>%
  filter(ben_20 == 1, ben_1 == 0, ben_28 == 0)

# Parent placebo: immigrant parents without CCB
df <- df %>%
  mutate(has_minor_child = childminor %in% c("1", "2", "3", "4", "5", "6", "More than 6"))

df_parent_no_ccb <- df %>%
  filter(immigrant == TRUE, has_minor_child == TRUE, ben_20 == 0)

n_ccb_imm <- n_distinct(df_ccb_imm$ID)
n_ccb_nat <- n_distinct(df_ccb_nat$ID)
n_parent_no_ccb <- n_distinct(df_parent_no_ccb$ID)
```

The main analysis pools all beneficiaries receiving fixed-date payments. To isolate effects for a single program, I examine recipients of the Canada Child Benefit (CCB), paid on the 20th of each month. This sample includes only respondents who receive CCB but do *not* receive Social Assistance (1st) or Pensions/Housing benefits (28th), yielding `r n_ccb_imm` exclusive immigrant CCB recipients and `r n_ccb_nat` exclusive non-immigrant CCB recipients.

@tbl-ccb-imm presents treatment effects for immigrant CCB recipients. Proximity to the CCB payment date significantly increases trust in Quebec government, financial satisfaction, and the importance placed on Quebec values and friendships. Effects on attachment to Quebec are marginally significant. Notably, proximity does not significantly affect trust in Canada, attachment to Canada, or attachment to city—suggesting effects are concentrated on Quebec-specific orientations.

```{r tbl-ccb-imm}
#| label: tbl-ccb-imm
#| tbl-cap: "Effect of CCB Payment Proximity (Exclusive Immigrant CCB Recipients)"

ccb_i1 <- feols(trust_qc ~ prox_20 | ID, data = df_ccb_imm)
ccb_i2 <- feols(trust_can ~ prox_20 | ID, data = df_ccb_imm)
ccb_i3 <- feols(attachment_qc ~ prox_20 | ID, data = df_ccb_imm)
ccb_i4 <- feols(attachment_can ~ prox_20 | ID, data = df_ccb_imm)
ccb_i5 <- feols(attachment_city ~ prox_20 | ID, data = df_ccb_imm)
ccb_i6 <- feols(financial_satisf ~ prox_20 | ID, data = df_ccb_imm)
ccb_i7 <- feols(life_satisf ~ prox_20 | ID, data = df_ccb_imm)
ccb_i8 <- feols(imp_qcvalues ~ prox_20 | ID, data = df_ccb_imm)
ccb_i9 <- feols(imp_qcfriends ~ prox_20 | ID, data = df_ccb_imm)

modelsummary(
  list(
    "QC" = ccb_i1, "CAN" = ccb_i2,
    "QC" = ccb_i3, "CAN" = ccb_i4, "City" = ccb_i5,
    "Financial" = ccb_i6, "Life" = ccb_i7,
    "Values" = ccb_i8, "Friends" = ccb_i9
  ),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = c("prox_20" = "Proximity (20th)"),
  gof_map = c("nobs", "FE: ID"),
  output = "tinytable"
) |>
  group_tt(j = list("Trust in\ngovt. of:" = 2:3, "Attachment\nto:" = 4:6, "Satisfaction\nwith:" = 7:8, "Importance of QC" = 9:10)) |>
  theme_tt("striped") |>
  theme_tt("resize") |>
  style_tt(j = 1, bold = TRUE) |>
  style_tt(fontsize = 0.8)
```

@tbl-ccb-imm-placebo presents the wrong-date placebo for immigrant CCB recipients: proximity to the 1st of the month, a payment date they do not receive. All effects are null, confirming that the actual CCB payment date specifically matters.

```{r tbl-ccb-imm-placebo}
#| label: tbl-ccb-imm-placebo
#| tbl-cap: "Wrong-Date Placebo: Proximity to 1st (Exclusive Immigrant CCB Recipients)"

ccb_ip1 <- feols(trust_qc ~ prox_1 | ID, data = df_ccb_imm)
ccb_ip2 <- feols(trust_can ~ prox_1 | ID, data = df_ccb_imm)
ccb_ip3 <- feols(attachment_qc ~ prox_1 | ID, data = df_ccb_imm)
ccb_ip4 <- feols(attachment_can ~ prox_1 | ID, data = df_ccb_imm)
ccb_ip5 <- feols(attachment_city ~ prox_1 | ID, data = df_ccb_imm)
ccb_ip6 <- feols(financial_satisf ~ prox_1 | ID, data = df_ccb_imm)
ccb_ip7 <- feols(life_satisf ~ prox_1 | ID, data = df_ccb_imm)
ccb_ip8 <- feols(imp_qcvalues ~ prox_1 | ID, data = df_ccb_imm)
ccb_ip9 <- feols(imp_qcfriends ~ prox_1 | ID, data = df_ccb_imm)

modelsummary(
  list(
    "QC" = ccb_ip1, "CAN" = ccb_ip2,
    "QC" = ccb_ip3, "CAN" = ccb_ip4, "City" = ccb_ip5,
    "Financial" = ccb_ip6, "Life" = ccb_ip7,
    "Values" = ccb_ip8, "Friends" = ccb_ip9
  ),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = c("prox_1" = "Proximity (1st)"),
  gof_map = c("nobs", "FE: ID"),
  output = "tinytable"
) |>
  group_tt(j = list("Trust in\ngovt. of:" = 2:3, "Attachment\nto:" = 4:6, "Satisfaction\nwith:" = 7:8, "Importance of QC" = 9:10)) |>
  theme_tt("striped") |>
  theme_tt("resize") |>
  style_tt(j = 1, bold = TRUE) |>
  style_tt(fontsize = 0.8)
```

@tbl-ccb-nat presents treatment effects for non-immigrant CCB recipients. Consistent with the pattern in the pooled analysis, non-immigrants show weaker effects of CCB payment proximity on political attitudes.

```{r tbl-ccb-nat}
#| label: tbl-ccb-nat
#| tbl-cap: "Effect of CCB Payment Proximity (Exclusive Non-Immigrant CCB Recipients)"

ccb_n1 <- feols(trust_qc ~ prox_20 | ID, data = df_ccb_nat)
ccb_n2 <- feols(trust_can ~ prox_20 | ID, data = df_ccb_nat)
ccb_n3 <- feols(attachment_qc ~ prox_20 | ID, data = df_ccb_nat)
ccb_n4 <- feols(attachment_can ~ prox_20 | ID, data = df_ccb_nat)
ccb_n5 <- feols(attachment_city ~ prox_20 | ID, data = df_ccb_nat)
ccb_n6 <- feols(financial_satisf ~ prox_20 | ID, data = df_ccb_nat)
ccb_n7 <- feols(life_satisf ~ prox_20 | ID, data = df_ccb_nat)
ccb_n8 <- feols(imp_qcvalues ~ prox_20 | ID, data = df_ccb_nat)
ccb_n9 <- feols(imp_qcfriends ~ prox_20 | ID, data = df_ccb_nat)

modelsummary(
  list(
    "QC" = ccb_n1, "CAN" = ccb_n2,
    "QC" = ccb_n3, "CAN" = ccb_n4, "City" = ccb_n5,
    "Financial" = ccb_n6, "Life" = ccb_n7,
    "Values" = ccb_n8, "Friends" = ccb_n9
  ),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = c("prox_20" = "Proximity (20th)"),
  gof_map = c("nobs", "FE: ID"),
  output = "tinytable"
) |>
  group_tt(j = list("Trust in\ngovt. of:" = 2:3, "Attachment\nto:" = 4:6, "Satisfaction\nwith:" = 7:8, "Importance of QC" = 9:10)) |>
  theme_tt("striped") |>
  theme_tt("resize") |>
  style_tt(j = 1, bold = TRUE) |>
  style_tt(fontsize = 0.8)
```

@tbl-parent-placebo presents a parent placebo test: immigrant parents who do *not* receive CCB (`r n_parent_no_ccb` individuals). If effects were driven by generic parenting-related timing, this sample should also show significant effects. Most outcomes are null, though trust in Quebec government and attachment to Canada show significant effects—suggesting some caution in interpreting the trust results.

```{r tbl-parent-placebo}
#| label: tbl-parent-placebo
#| tbl-cap: "Parent Placebo: Immigrant Parents Without CCB (Proximity to 20th)"

pp_t1 <- feols(trust_qc ~ prox_20 | ID, data = df_parent_no_ccb)
pp_t2 <- feols(trust_can ~ prox_20 | ID, data = df_parent_no_ccb)
pp_t3 <- feols(attachment_qc ~ prox_20 | ID, data = df_parent_no_ccb)
pp_t4 <- feols(attachment_can ~ prox_20 | ID, data = df_parent_no_ccb)
pp_t5 <- feols(attachment_city ~ prox_20 | ID, data = df_parent_no_ccb)
pp_t6 <- feols(financial_satisf ~ prox_20 | ID, data = df_parent_no_ccb)
pp_t7 <- feols(life_satisf ~ prox_20 | ID, data = df_parent_no_ccb)
pp_t8 <- feols(imp_qcvalues ~ prox_20 | ID, data = df_parent_no_ccb)
pp_t9 <- feols(imp_qcfriends ~ prox_20 | ID, data = df_parent_no_ccb)

modelsummary(
  list(
    "QC" = pp_t1, "CAN" = pp_t2,
    "QC" = pp_t3, "CAN" = pp_t4, "City" = pp_t5,
    "Financial" = pp_t6, "Life" = pp_t7,
    "Values" = pp_t8, "Friends" = pp_t9
  ),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = c("prox_20" = "Proximity (20th)"),
  gof_map = c("nobs", "FE: ID"),
  output = "tinytable"
) |>
  group_tt(j = list("Trust in\ngovt. of:" = 2:3, "Attachment\nto:" = 4:6, "Satisfaction\nwith:" = 7:8, "Importance of QC" = 9:10)) |>
  theme_tt("striped") |>
  theme_tt("resize") |>
  style_tt(j = 1, bold = TRUE) |>
  style_tt(fontsize = 0.8)
```

## Heterogeneous Effects

Do payment proximity effects vary by immigrants' time in Canada or income level? To explore potential heterogeneity in treatment effects, I estimate models with interaction terms between proximity and baseline characteristics. Following Giesselmann and Schmidt-Catran (2020), interactions between time-varying treatments (proximity) and time-invariant or baseline moderators (years in Canada, income) are valid in fixed effects models—the interaction captures how the within-person effect of proximity differs across subgroups.

```{r interaction-prep}
#| include: false

# Update sample datasets with the interaction variables
df_imm <- df_ben %>% filter(immigrant == TRUE)
df_ccb_imm <- df_imm %>%
  filter(ben_20 == 1, ben_1 == 0, ben_28 == 0)

# Filter to observations with valid moderator values for interaction analysis
# Using years_in_qc (better coverage: 638 vs 190 individuals compared to years_in_qc)
df_imm_years <- df_imm %>%
  filter(!is.na(years_in_qc), years_in_qc >= 0)
df_imm_income <- df_imm %>%
  filter(!is.na(income_filled))

df_ccb_years <- df_ccb_imm %>%
  filter(!is.na(years_in_qc), years_in_qc >= 0)
df_ccb_income <- df_ccb_imm %>%
  filter(!is.na(income_filled))

# French competency samples
df_imm_french <- df_imm %>%
  filter(!is.na(french_comp_filled))
df_ccb_french <- df_ccb_imm %>%
  filter(!is.na(french_comp_filled))

# Education samples
df_imm_educ <- df_imm %>%
  filter(!is.na(education_num_filled))
df_ccb_educ <- df_ccb_imm %>%
  filter(!is.na(education_num_filled))

# Political knowledge samples
df_imm_polknow <- df_imm %>%
  filter(!is.na(polknow_score))
df_ccb_polknow <- df_ccb_imm %>%
  filter(!is.na(polknow_score))

# Policy knowledge samples
df_imm_policyknow <- df_imm %>%
  filter(!is.na(policyknow_score))
df_ccb_policyknow <- df_ccb_imm %>%
  filter(!is.na(policyknow_score))

# Get actual range of years for plotting
years_range <- range(df_imm_years$years_in_qc)
years_seq <- seq(years_range[1], years_range[2], by = 1)

# Define outcome groups
trust_vars <- c("trust_qc", "trust_can")
satisf_vars <- c("financial_satisf", "life_satisf")
attach_vars <- c("attachment_qc", "attachment_can", "attachment_city")
qc_attitude_vars <- c("imp_qcvalues", "imp_qcfriends")

# Labels for plots
dv_labels <- c(
  "trust_qc" = "Trust: QC Govt",
  "trust_can" = "Trust: Canada Govt",
  "financial_satisf" = "Financial Satisfaction",
  "life_satisf" = "Life Satisfaction",
  "attachment_qc" = "Attachment: Quebec",
  "attachment_can" = "Attachment: Canada",
  "attachment_city" = "Attachment: City",
  "imp_qcvalues" = "QC Values Important",
  "imp_qcfriends" = "QC Friends Important"
)
```

@fig-interaction-years presents how payment proximity effects vary by years in Quebec for all immigrant beneficiaries. Each panel shows the marginal effect of proximity to payday across the range of time spent in Quebec, with 95% confidence intervals. If newer immigrants show stronger effects, we would expect declining slopes; if effects are consistent across tenure, lines would be flat. Full interaction model coefficients are reported in @tbl-app-interaction-years and @tbl-app-interaction-income.

```{r fig-interaction-years}
#| label: fig-interaction-years
#| fig-cap: "Marginal Effect of Payment Proximity by Years in Quebec (All Immigrant Beneficiaries)"
#| fig-height: 10
#| fig-width: 10

# Estimate interaction models explicitly for each DV
mod_trust_qc <- feols(trust_qc ~ prox_actual * years_in_qc | ID, data = df_imm_years)
mod_trust_can <- feols(trust_can ~ prox_actual * years_in_qc | ID, data = df_imm_years)
mod_attach_qc <- feols(attachment_qc ~ prox_actual * years_in_qc | ID, data = df_imm_years)
mod_attach_can <- feols(attachment_can ~ prox_actual * years_in_qc | ID, data = df_imm_years)
mod_attach_city <- feols(attachment_city ~ prox_actual * years_in_qc | ID, data = df_imm_years)
mod_financial <- feols(financial_satisf ~ prox_actual * years_in_qc | ID, data = df_imm_years)
mod_life <- feols(life_satisf ~ prox_actual * years_in_qc | ID, data = df_imm_years)
mod_qcvalues <- feols(imp_qcvalues ~ prox_actual * years_in_qc | ID, data = df_imm_years)
mod_qcfriends <- feols(imp_qcfriends ~ prox_actual * years_in_qc | ID, data = df_imm_years)

# Extract marginal effect of proximity at each value of years_in_qc
slopes_trust_qc <- slopes(mod_trust_qc, variables = "prox_actual",
                          newdata = datagrid(years_in_qc = years_seq)) |>
  as_tibble() |> mutate(outcome = "Trust: QC Govt")

slopes_trust_can <- slopes(mod_trust_can, variables = "prox_actual",
                           newdata = datagrid(years_in_qc = years_seq)) |>
  as_tibble() |> mutate(outcome = "Trust: Canada Govt")

slopes_attach_qc <- slopes(mod_attach_qc, variables = "prox_actual",
                           newdata = datagrid(years_in_qc = years_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: Quebec")

slopes_attach_can <- slopes(mod_attach_can, variables = "prox_actual",
                            newdata = datagrid(years_in_qc = years_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: Canada")

slopes_attach_city <- slopes(mod_attach_city, variables = "prox_actual",
                             newdata = datagrid(years_in_qc = years_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: City")

slopes_financial <- slopes(mod_financial, variables = "prox_actual",
                           newdata = datagrid(years_in_qc = years_seq)) |>
  as_tibble() |> mutate(outcome = "Financial Satisfaction")

slopes_life <- slopes(mod_life, variables = "prox_actual",
                      newdata = datagrid(years_in_qc = years_seq)) |>
  as_tibble() |> mutate(outcome = "Life Satisfaction")

slopes_qcvalues <- slopes(mod_qcvalues, variables = "prox_actual",
                          newdata = datagrid(years_in_qc = years_seq)) |>
  as_tibble() |> mutate(outcome = "QC Values Important")

slopes_qcfriends <- slopes(mod_qcfriends, variables = "prox_actual",
                           newdata = datagrid(years_in_qc = years_seq)) |>
  as_tibble() |> mutate(outcome = "QC Friends Important")

# Combine all slopes
years_slopes <- bind_rows(
  slopes_trust_qc, slopes_trust_can,
  slopes_attach_qc, slopes_attach_can, slopes_attach_city,
  slopes_financial, slopes_life,
  slopes_qcvalues, slopes_qcfriends
)

# Plot: marginal effect of proximity across years in QC
ggplot(years_slopes, aes(x = years_in_qc, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, fill = "steelblue") +
  geom_line(color = "steelblue", linewidth = 1) +
  facet_wrap(~ outcome, ncol = 3, scales = "free_y") +
  labs(
    x = "Years in Quebec",
    y = "Marginal Effect of Payment Proximity"
  ) +
  theme_tufte(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.spacing = unit(1.2, "lines"),
    axis.title = element_text(size = 11)
  )
```

@fig-interaction-income examines heterogeneity by household income level. Lower-income beneficiaries may be more responsive to payment timing if financial constraints make payday more salient.

```{r fig-interaction-income}
#| label: fig-interaction-income
#| fig-cap: "Marginal Effect of Payment Proximity by Household Income (All Immigrant Beneficiaries)"
#| fig-height: 10
#| fig-width: 10

# Income scale values
income_seq <- 1:8

# Income labels for x-axis
income_labels <- c(
  "1" = "None",
  "2" = "<30k",
  "3" = "30-60k",
  "4" = "60-90k",
  "5" = "90-110k",
  "6" = "110-150k",
  "7" = "150-200k",
  "8" = ">200k"
)

# Estimate interaction models explicitly for each DV
mod_inc_trust_qc <- feols(trust_qc ~ prox_actual * income_filled | ID, data = df_imm_income)
mod_inc_trust_can <- feols(trust_can ~ prox_actual * income_filled | ID, data = df_imm_income)
mod_inc_attach_qc <- feols(attachment_qc ~ prox_actual * income_filled | ID, data = df_imm_income)
mod_inc_attach_can <- feols(attachment_can ~ prox_actual * income_filled | ID, data = df_imm_income)
mod_inc_attach_city <- feols(attachment_city ~ prox_actual * income_filled | ID, data = df_imm_income)
mod_inc_financial <- feols(financial_satisf ~ prox_actual * income_filled | ID, data = df_imm_income)
mod_inc_life <- feols(life_satisf ~ prox_actual * income_filled | ID, data = df_imm_income)
mod_inc_qcvalues <- feols(imp_qcvalues ~ prox_actual * income_filled | ID, data = df_imm_income)
mod_inc_qcfriends <- feols(imp_qcfriends ~ prox_actual * income_filled | ID, data = df_imm_income)

# Extract marginal effect of proximity at each income level
slopes_inc_trust_qc <- slopes(mod_inc_trust_qc, variables = "prox_actual",
                               newdata = datagrid(income_filled = income_seq)) |>
  as_tibble() |> mutate(outcome = "Trust: QC Govt")

slopes_inc_trust_can <- slopes(mod_inc_trust_can, variables = "prox_actual",
                                newdata = datagrid(income_filled = income_seq)) |>
  as_tibble() |> mutate(outcome = "Trust: Canada Govt")

slopes_inc_attach_qc <- slopes(mod_inc_attach_qc, variables = "prox_actual",
                                newdata = datagrid(income_filled = income_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: Quebec")

slopes_inc_attach_can <- slopes(mod_inc_attach_can, variables = "prox_actual",
                                 newdata = datagrid(income_filled = income_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: Canada")

slopes_inc_attach_city <- slopes(mod_inc_attach_city, variables = "prox_actual",
                                  newdata = datagrid(income_filled = income_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: City")

slopes_inc_financial <- slopes(mod_inc_financial, variables = "prox_actual",
                                newdata = datagrid(income_filled = income_seq)) |>
  as_tibble() |> mutate(outcome = "Financial Satisfaction")

slopes_inc_life <- slopes(mod_inc_life, variables = "prox_actual",
                           newdata = datagrid(income_filled = income_seq)) |>
  as_tibble() |> mutate(outcome = "Life Satisfaction")

slopes_inc_qcvalues <- slopes(mod_inc_qcvalues, variables = "prox_actual",
                               newdata = datagrid(income_filled = income_seq)) |>
  as_tibble() |> mutate(outcome = "QC Values Important")

slopes_inc_qcfriends <- slopes(mod_inc_qcfriends, variables = "prox_actual",
                                newdata = datagrid(income_filled = income_seq)) |>
  as_tibble() |> mutate(outcome = "QC Friends Important")

# Combine all slopes
income_slopes <- bind_rows(
  slopes_inc_trust_qc, slopes_inc_trust_can,
  slopes_inc_attach_qc, slopes_inc_attach_can, slopes_inc_attach_city,
  slopes_inc_financial, slopes_inc_life,
  slopes_inc_qcvalues, slopes_inc_qcfriends
)

# Plot: marginal effect of proximity across income levels
ggplot(income_slopes, aes(x = income_filled, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, fill = "darkgreen") +
  geom_line(color = "darkgreen", linewidth = 1) +
  facet_wrap(~ outcome, ncol = 3, scales = "free_y") +
  scale_x_continuous(breaks = 1:8, labels = income_labels) +
  labs(
    x = "Household Income",
    y = "Marginal Effect of Payment Proximity"
  ) +
  theme_tufte(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.spacing = unit(1.2, "lines"),
    axis.title = element_text(size = 11),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8)
  )
```

@fig-interaction-french examines heterogeneity by French language competency. If immigrants with lower French proficiency are more reliant on material signals from government—because linguistic barriers limit other channels of integration—we would expect stronger effects at lower levels of French competency.

```{r fig-interaction-french}
#| label: fig-interaction-french
#| fig-cap: "Marginal Effect of Payment Proximity by French Competency (All Immigrant Beneficiaries)"
#| fig-height: 10
#| fig-width: 10

# French competency scale values (0-10)
french_seq <- 0:10

# Estimate interaction models explicitly for each DV
mod_fr_trust_qc <- feols(trust_qc ~ prox_actual * french_comp_filled | ID, data = df_imm_french)
mod_fr_trust_can <- feols(trust_can ~ prox_actual * french_comp_filled | ID, data = df_imm_french)
mod_fr_attach_qc <- feols(attachment_qc ~ prox_actual * french_comp_filled | ID, data = df_imm_french)
mod_fr_attach_can <- feols(attachment_can ~ prox_actual * french_comp_filled | ID, data = df_imm_french)
mod_fr_attach_city <- feols(attachment_city ~ prox_actual * french_comp_filled | ID, data = df_imm_french)
mod_fr_financial <- feols(financial_satisf ~ prox_actual * french_comp_filled | ID, data = df_imm_french)
mod_fr_life <- feols(life_satisf ~ prox_actual * french_comp_filled | ID, data = df_imm_french)
mod_fr_qcvalues <- feols(imp_qcvalues ~ prox_actual * french_comp_filled | ID, data = df_imm_french)
mod_fr_qcfriends <- feols(imp_qcfriends ~ prox_actual * french_comp_filled | ID, data = df_imm_french)

# Extract marginal effect of proximity at each French competency level
slopes_fr_trust_qc <- slopes(mod_fr_trust_qc, variables = "prox_actual",
                              newdata = datagrid(french_comp_filled = french_seq)) |>
  as_tibble() |> mutate(outcome = "Trust: QC Govt")

slopes_fr_trust_can <- slopes(mod_fr_trust_can, variables = "prox_actual",
                               newdata = datagrid(french_comp_filled = french_seq)) |>
  as_tibble() |> mutate(outcome = "Trust: Canada Govt")

slopes_fr_attach_qc <- slopes(mod_fr_attach_qc, variables = "prox_actual",
                               newdata = datagrid(french_comp_filled = french_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: Quebec")

slopes_fr_attach_can <- slopes(mod_fr_attach_can, variables = "prox_actual",
                                newdata = datagrid(french_comp_filled = french_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: Canada")

slopes_fr_attach_city <- slopes(mod_fr_attach_city, variables = "prox_actual",
                                 newdata = datagrid(french_comp_filled = french_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: City")

slopes_fr_financial <- slopes(mod_fr_financial, variables = "prox_actual",
                               newdata = datagrid(french_comp_filled = french_seq)) |>
  as_tibble() |> mutate(outcome = "Financial Satisfaction")

slopes_fr_life <- slopes(mod_fr_life, variables = "prox_actual",
                          newdata = datagrid(french_comp_filled = french_seq)) |>
  as_tibble() |> mutate(outcome = "Life Satisfaction")

slopes_fr_qcvalues <- slopes(mod_fr_qcvalues, variables = "prox_actual",
                              newdata = datagrid(french_comp_filled = french_seq)) |>
  as_tibble() |> mutate(outcome = "QC Values Important")

slopes_fr_qcfriends <- slopes(mod_fr_qcfriends, variables = "prox_actual",
                               newdata = datagrid(french_comp_filled = french_seq)) |>
  as_tibble() |> mutate(outcome = "QC Friends Important")

# Combine all slopes
french_slopes <- bind_rows(
  slopes_fr_trust_qc, slopes_fr_trust_can,
  slopes_fr_attach_qc, slopes_fr_attach_can, slopes_fr_attach_city,
  slopes_fr_financial, slopes_fr_life,
  slopes_fr_qcvalues, slopes_fr_qcfriends
)

# Plot: marginal effect of proximity across French competency levels
ggplot(french_slopes, aes(x = french_comp_filled, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, fill = "darkorange") +
  geom_line(color = "darkorange", linewidth = 1) +
  facet_wrap(~ outcome, ncol = 3, scales = "free_y") +
  scale_x_continuous(breaks = seq(0, 10, 2)) +
  labs(
    x = "French Competency (0-10)",
    y = "Marginal Effect of Payment Proximity"
  ) +
  theme_tufte(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.spacing = unit(1.2, "lines"),
    axis.title = element_text(size = 11)
  )
```

@fig-interaction-educ examines heterogeneity by education level. Higher-educated immigrants may have more crystallized political orientations or alternative sources of information about government, potentially reducing responsiveness to material signals.

```{r fig-interaction-educ}
#| label: fig-interaction-educ
#| fig-cap: "Marginal Effect of Payment Proximity by Education Level (All Immigrant Beneficiaries)"
#| fig-height: 10
#| fig-width: 10

# Education scale values (1-7)
educ_seq <- 1:7
educ_labels <- c(
  "1" = "None",
  "2" = "<HS",
  "3" = "HS",
  "4" = "College",
  "5" = "BA",
  "6" = "MA",
  "7" = "PhD"
)

# Estimate interaction models
mod_ed_trust_qc <- feols(trust_qc ~ prox_actual * education_num_filled | ID, data = df_imm_educ)
mod_ed_trust_can <- feols(trust_can ~ prox_actual * education_num_filled | ID, data = df_imm_educ)
mod_ed_attach_qc <- feols(attachment_qc ~ prox_actual * education_num_filled | ID, data = df_imm_educ)
mod_ed_attach_can <- feols(attachment_can ~ prox_actual * education_num_filled | ID, data = df_imm_educ)
mod_ed_attach_city <- feols(attachment_city ~ prox_actual * education_num_filled | ID, data = df_imm_educ)
mod_ed_financial <- feols(financial_satisf ~ prox_actual * education_num_filled | ID, data = df_imm_educ)
mod_ed_life <- feols(life_satisf ~ prox_actual * education_num_filled | ID, data = df_imm_educ)
mod_ed_qcvalues <- feols(imp_qcvalues ~ prox_actual * education_num_filled | ID, data = df_imm_educ)
mod_ed_qcfriends <- feols(imp_qcfriends ~ prox_actual * education_num_filled | ID, data = df_imm_educ)

# Extract marginal effects
slopes_ed_trust_qc <- slopes(mod_ed_trust_qc, variables = "prox_actual",
                              newdata = datagrid(education_num_filled = educ_seq)) |>
  as_tibble() |> mutate(outcome = "Trust: QC Govt")
slopes_ed_trust_can <- slopes(mod_ed_trust_can, variables = "prox_actual",
                               newdata = datagrid(education_num_filled = educ_seq)) |>
  as_tibble() |> mutate(outcome = "Trust: Canada Govt")
slopes_ed_attach_qc <- slopes(mod_ed_attach_qc, variables = "prox_actual",
                               newdata = datagrid(education_num_filled = educ_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: Quebec")
slopes_ed_attach_can <- slopes(mod_ed_attach_can, variables = "prox_actual",
                                newdata = datagrid(education_num_filled = educ_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: Canada")
slopes_ed_attach_city <- slopes(mod_ed_attach_city, variables = "prox_actual",
                                 newdata = datagrid(education_num_filled = educ_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: City")
slopes_ed_financial <- slopes(mod_ed_financial, variables = "prox_actual",
                               newdata = datagrid(education_num_filled = educ_seq)) |>
  as_tibble() |> mutate(outcome = "Financial Satisfaction")
slopes_ed_life <- slopes(mod_ed_life, variables = "prox_actual",
                          newdata = datagrid(education_num_filled = educ_seq)) |>
  as_tibble() |> mutate(outcome = "Life Satisfaction")
slopes_ed_qcvalues <- slopes(mod_ed_qcvalues, variables = "prox_actual",
                              newdata = datagrid(education_num_filled = educ_seq)) |>
  as_tibble() |> mutate(outcome = "QC Values Important")
slopes_ed_qcfriends <- slopes(mod_ed_qcfriends, variables = "prox_actual",
                               newdata = datagrid(education_num_filled = educ_seq)) |>
  as_tibble() |> mutate(outcome = "QC Friends Important")

educ_slopes <- bind_rows(
  slopes_ed_trust_qc, slopes_ed_trust_can,
  slopes_ed_attach_qc, slopes_ed_attach_can, slopes_ed_attach_city,
  slopes_ed_financial, slopes_ed_life,
  slopes_ed_qcvalues, slopes_ed_qcfriends
)

ggplot(educ_slopes, aes(x = education_num_filled, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, fill = "purple4") +
  geom_line(color = "purple4", linewidth = 1) +
  facet_wrap(~ outcome, ncol = 3, scales = "free_y") +
  scale_x_continuous(breaks = 1:7, labels = educ_labels) +
  labs(
    x = "Education Level",
    y = "Marginal Effect of Payment Proximity"
  ) +
  theme_tufte(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.spacing = unit(1.2, "lines"),
    axis.title = element_text(size = 11),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8)
  )
```

@fig-interaction-polknow examines heterogeneity by political knowledge (ability to correctly identify politicians). Immigrants with lower political knowledge may be less attuned to government's role, potentially showing weaker credit attribution—or conversely, may be more responsive to concrete material signals.

```{r fig-interaction-polknow}
#| label: fig-interaction-polknow
#| fig-cap: "Marginal Effect of Payment Proximity by Political Knowledge (All Immigrant Beneficiaries)"
#| fig-height: 10
#| fig-width: 10

# Political knowledge scale (0-4)
polknow_seq <- 0:4

# Estimate interaction models
mod_pk_trust_qc <- feols(trust_qc ~ prox_actual * polknow_score | ID, data = df_imm_polknow)
mod_pk_trust_can <- feols(trust_can ~ prox_actual * polknow_score | ID, data = df_imm_polknow)
mod_pk_attach_qc <- feols(attachment_qc ~ prox_actual * polknow_score | ID, data = df_imm_polknow)
mod_pk_attach_can <- feols(attachment_can ~ prox_actual * polknow_score | ID, data = df_imm_polknow)
mod_pk_attach_city <- feols(attachment_city ~ prox_actual * polknow_score | ID, data = df_imm_polknow)
mod_pk_financial <- feols(financial_satisf ~ prox_actual * polknow_score | ID, data = df_imm_polknow)
mod_pk_life <- feols(life_satisf ~ prox_actual * polknow_score | ID, data = df_imm_polknow)
mod_pk_qcvalues <- feols(imp_qcvalues ~ prox_actual * polknow_score | ID, data = df_imm_polknow)
mod_pk_qcfriends <- feols(imp_qcfriends ~ prox_actual * polknow_score | ID, data = df_imm_polknow)

# Extract marginal effects
slopes_pk_trust_qc <- slopes(mod_pk_trust_qc, variables = "prox_actual",
                              newdata = datagrid(polknow_score = polknow_seq)) |>
  as_tibble() |> mutate(outcome = "Trust: QC Govt")
slopes_pk_trust_can <- slopes(mod_pk_trust_can, variables = "prox_actual",
                               newdata = datagrid(polknow_score = polknow_seq)) |>
  as_tibble() |> mutate(outcome = "Trust: Canada Govt")
slopes_pk_attach_qc <- slopes(mod_pk_attach_qc, variables = "prox_actual",
                               newdata = datagrid(polknow_score = polknow_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: Quebec")
slopes_pk_attach_can <- slopes(mod_pk_attach_can, variables = "prox_actual",
                                newdata = datagrid(polknow_score = polknow_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: Canada")
slopes_pk_attach_city <- slopes(mod_pk_attach_city, variables = "prox_actual",
                                 newdata = datagrid(polknow_score = polknow_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: City")
slopes_pk_financial <- slopes(mod_pk_financial, variables = "prox_actual",
                               newdata = datagrid(polknow_score = polknow_seq)) |>
  as_tibble() |> mutate(outcome = "Financial Satisfaction")
slopes_pk_life <- slopes(mod_pk_life, variables = "prox_actual",
                          newdata = datagrid(polknow_score = polknow_seq)) |>
  as_tibble() |> mutate(outcome = "Life Satisfaction")
slopes_pk_qcvalues <- slopes(mod_pk_qcvalues, variables = "prox_actual",
                              newdata = datagrid(polknow_score = polknow_seq)) |>
  as_tibble() |> mutate(outcome = "QC Values Important")
slopes_pk_qcfriends <- slopes(mod_pk_qcfriends, variables = "prox_actual",
                               newdata = datagrid(polknow_score = polknow_seq)) |>
  as_tibble() |> mutate(outcome = "QC Friends Important")

polknow_slopes <- bind_rows(
  slopes_pk_trust_qc, slopes_pk_trust_can,
  slopes_pk_attach_qc, slopes_pk_attach_can, slopes_pk_attach_city,
  slopes_pk_financial, slopes_pk_life,
  slopes_pk_qcvalues, slopes_pk_qcfriends
)

ggplot(polknow_slopes, aes(x = polknow_score, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, fill = "firebrick") +
  geom_line(color = "firebrick", linewidth = 1) +
  facet_wrap(~ outcome, ncol = 3, scales = "free_y") +
  scale_x_continuous(breaks = 0:4) +
  labs(
    x = "Political Knowledge Score (0-4)",
    y = "Marginal Effect of Payment Proximity"
  ) +
  theme_tufte(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.spacing = unit(1.2, "lines"),
    axis.title = element_text(size = 11)
  )
```

@fig-interaction-policyknow examines heterogeneity by policy knowledge (ability to correctly answer questions about government policies). This tests whether immigrants who better understand what government does show different responsiveness to benefit payments.

```{r fig-interaction-policyknow}
#| label: fig-interaction-policyknow
#| fig-cap: "Marginal Effect of Payment Proximity by Policy Knowledge (All Immigrant Beneficiaries)"
#| fig-height: 10
#| fig-width: 10

# Policy knowledge scale (0-6)
policyknow_seq <- 0:6

# Estimate interaction models
mod_pok_trust_qc <- feols(trust_qc ~ prox_actual * policyknow_score | ID, data = df_imm_policyknow)
mod_pok_trust_can <- feols(trust_can ~ prox_actual * policyknow_score | ID, data = df_imm_policyknow)
mod_pok_attach_qc <- feols(attachment_qc ~ prox_actual * policyknow_score | ID, data = df_imm_policyknow)
mod_pok_attach_can <- feols(attachment_can ~ prox_actual * policyknow_score | ID, data = df_imm_policyknow)
mod_pok_attach_city <- feols(attachment_city ~ prox_actual * policyknow_score | ID, data = df_imm_policyknow)
mod_pok_financial <- feols(financial_satisf ~ prox_actual * policyknow_score | ID, data = df_imm_policyknow)
mod_pok_life <- feols(life_satisf ~ prox_actual * policyknow_score | ID, data = df_imm_policyknow)
mod_pok_qcvalues <- feols(imp_qcvalues ~ prox_actual * policyknow_score | ID, data = df_imm_policyknow)
mod_pok_qcfriends <- feols(imp_qcfriends ~ prox_actual * policyknow_score | ID, data = df_imm_policyknow)

# Extract marginal effects
slopes_pok_trust_qc <- slopes(mod_pok_trust_qc, variables = "prox_actual",
                               newdata = datagrid(policyknow_score = policyknow_seq)) |>
  as_tibble() |> mutate(outcome = "Trust: QC Govt")
slopes_pok_trust_can <- slopes(mod_pok_trust_can, variables = "prox_actual",
                                newdata = datagrid(policyknow_score = policyknow_seq)) |>
  as_tibble() |> mutate(outcome = "Trust: Canada Govt")
slopes_pok_attach_qc <- slopes(mod_pok_attach_qc, variables = "prox_actual",
                                newdata = datagrid(policyknow_score = policyknow_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: Quebec")
slopes_pok_attach_can <- slopes(mod_pok_attach_can, variables = "prox_actual",
                                 newdata = datagrid(policyknow_score = policyknow_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: Canada")
slopes_pok_attach_city <- slopes(mod_pok_attach_city, variables = "prox_actual",
                                  newdata = datagrid(policyknow_score = policyknow_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: City")
slopes_pok_financial <- slopes(mod_pok_financial, variables = "prox_actual",
                                newdata = datagrid(policyknow_score = policyknow_seq)) |>
  as_tibble() |> mutate(outcome = "Financial Satisfaction")
slopes_pok_life <- slopes(mod_pok_life, variables = "prox_actual",
                           newdata = datagrid(policyknow_score = policyknow_seq)) |>
  as_tibble() |> mutate(outcome = "Life Satisfaction")
slopes_pok_qcvalues <- slopes(mod_pok_qcvalues, variables = "prox_actual",
                               newdata = datagrid(policyknow_score = policyknow_seq)) |>
  as_tibble() |> mutate(outcome = "QC Values Important")
slopes_pok_qcfriends <- slopes(mod_pok_qcfriends, variables = "prox_actual",
                                newdata = datagrid(policyknow_score = policyknow_seq)) |>
  as_tibble() |> mutate(outcome = "QC Friends Important")

policyknow_slopes <- bind_rows(
  slopes_pok_trust_qc, slopes_pok_trust_can,
  slopes_pok_attach_qc, slopes_pok_attach_can, slopes_pok_attach_city,
  slopes_pok_financial, slopes_pok_life,
  slopes_pok_qcvalues, slopes_pok_qcfriends
)

ggplot(policyknow_slopes, aes(x = policyknow_score, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, fill = "darkgoldenrod") +
  geom_line(color = "darkgoldenrod", linewidth = 1) +
  facet_wrap(~ outcome, ncol = 3, scales = "free_y") +
  scale_x_continuous(breaks = 0:6) +
  labs(
    x = "Policy Knowledge Score (0-6)",
    y = "Marginal Effect of Payment Proximity"
  ) +
  theme_tufte(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.spacing = unit(1.2, "lines"),
    axis.title = element_text(size = 11)
  )
```

@fig-interaction-years-ccb, @fig-interaction-income-ccb, and @fig-interaction-french-ccb replicate the heterogeneity analyses for exclusive CCB recipients, where identification is cleanest.

```{r fig-interaction-years-ccb}
#| label: fig-interaction-years-ccb
#| fig-cap: "Marginal Effect of CCB Payment Proximity by Years in Quebec (Exclusive CCB Recipients)"
#| fig-height: 12
#| fig-width: 12

# Get CCB-specific years range for plotting
years_range_ccb <- range(df_ccb_years$years_in_qc)
years_seq_ccb <- seq(years_range_ccb[1], years_range_ccb[2], by = 1)

# Estimate interaction models explicitly for each DV (CCB sample, using prox_20)
mod_ccb_trust_qc <- feols(trust_qc ~ prox_20 * years_in_qc | ID, data = df_ccb_years)
mod_ccb_trust_can <- feols(trust_can ~ prox_20 * years_in_qc | ID, data = df_ccb_years)
mod_ccb_attach_qc <- feols(attachment_qc ~ prox_20 * years_in_qc | ID, data = df_ccb_years)
mod_ccb_attach_can <- feols(attachment_can ~ prox_20 * years_in_qc | ID, data = df_ccb_years)
mod_ccb_attach_city <- feols(attachment_city ~ prox_20 * years_in_qc | ID, data = df_ccb_years)
mod_ccb_financial <- feols(financial_satisf ~ prox_20 * years_in_qc | ID, data = df_ccb_years)
mod_ccb_life <- feols(life_satisf ~ prox_20 * years_in_qc | ID, data = df_ccb_years)
mod_ccb_qcvalues <- feols(imp_qcvalues ~ prox_20 * years_in_qc | ID, data = df_ccb_years)
mod_ccb_qcfriends <- feols(imp_qcfriends ~ prox_20 * years_in_qc | ID, data = df_ccb_years)

# Extract marginal effect of prox_20 at each value of years_in_qc using slopes()
slopes_ccb_trust_qc <- slopes(mod_ccb_trust_qc, variables = "prox_20",
                               newdata = datagrid(years_in_qc = years_seq_ccb)) |>
  as_tibble() |> mutate(outcome = "Trust: QC Govt")

slopes_ccb_trust_can <- slopes(mod_ccb_trust_can, variables = "prox_20",
                                newdata = datagrid(years_in_qc = years_seq_ccb)) |>
  as_tibble() |> mutate(outcome = "Trust: Canada Govt")

slopes_ccb_attach_qc <- slopes(mod_ccb_attach_qc, variables = "prox_20",
                                newdata = datagrid(years_in_qc = years_seq_ccb)) |>
  as_tibble() |> mutate(outcome = "Attachment: Quebec")

slopes_ccb_attach_can <- slopes(mod_ccb_attach_can, variables = "prox_20",
                                 newdata = datagrid(years_in_qc = years_seq_ccb)) |>
  as_tibble() |> mutate(outcome = "Attachment: Canada")

slopes_ccb_attach_city <- slopes(mod_ccb_attach_city, variables = "prox_20",
                                  newdata = datagrid(years_in_qc = years_seq_ccb)) |>
  as_tibble() |> mutate(outcome = "Attachment: City")

slopes_ccb_financial <- slopes(mod_ccb_financial, variables = "prox_20",
                                newdata = datagrid(years_in_qc = years_seq_ccb)) |>
  as_tibble() |> mutate(outcome = "Financial Satisfaction")

slopes_ccb_life <- slopes(mod_ccb_life, variables = "prox_20",
                           newdata = datagrid(years_in_qc = years_seq_ccb)) |>
  as_tibble() |> mutate(outcome = "Life Satisfaction")

slopes_ccb_qcvalues <- slopes(mod_ccb_qcvalues, variables = "prox_20",
                               newdata = datagrid(years_in_qc = years_seq_ccb)) |>
  as_tibble() |> mutate(outcome = "QC Values Important")

slopes_ccb_qcfriends <- slopes(mod_ccb_qcfriends, variables = "prox_20",
                                newdata = datagrid(years_in_qc = years_seq_ccb)) |>
  as_tibble() |> mutate(outcome = "QC Friends Important")

# Combine all slopes
years_slopes_ccb <- bind_rows(
  slopes_ccb_trust_qc, slopes_ccb_trust_can,
  slopes_ccb_attach_qc, slopes_ccb_attach_can, slopes_ccb_attach_city,
  slopes_ccb_financial, slopes_ccb_life,
  slopes_ccb_qcvalues, slopes_ccb_qcfriends
)

# Plot
ggplot(years_slopes_ccb, aes(x = years_in_qc, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, fill = "steelblue") +
  geom_line(color = "steelblue", linewidth = 1) +
  facet_wrap(~ outcome, ncol = 3, scales = "free_y") +
  labs(
    x = "Years in Quebec",
    y = "Marginal Effect of CCB Payment Proximity"
  ) +
  theme_tufte(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.spacing = unit(1.2, "lines"),
    axis.title = element_text(size = 11)
  )
```

```{r fig-interaction-income-ccb}
#| label: fig-interaction-income-ccb
#| fig-cap: "Marginal Effect of CCB Payment Proximity by Household Income (Exclusive CCB Recipients)"
#| fig-height: 12
#| fig-width: 12

# Estimate interaction models explicitly for each DV (CCB sample, using prox_20)
mod_ccb_inc_trust_qc <- feols(trust_qc ~ prox_20 * income_filled | ID, data = df_ccb_income)
mod_ccb_inc_trust_can <- feols(trust_can ~ prox_20 * income_filled | ID, data = df_ccb_income)
mod_ccb_inc_attach_qc <- feols(attachment_qc ~ prox_20 * income_filled | ID, data = df_ccb_income)
mod_ccb_inc_attach_can <- feols(attachment_can ~ prox_20 * income_filled | ID, data = df_ccb_income)
mod_ccb_inc_attach_city <- feols(attachment_city ~ prox_20 * income_filled | ID, data = df_ccb_income)
mod_ccb_inc_financial <- feols(financial_satisf ~ prox_20 * income_filled | ID, data = df_ccb_income)
mod_ccb_inc_life <- feols(life_satisf ~ prox_20 * income_filled | ID, data = df_ccb_income)
mod_ccb_inc_qcvalues <- feols(imp_qcvalues ~ prox_20 * income_filled | ID, data = df_ccb_income)
mod_ccb_inc_qcfriends <- feols(imp_qcfriends ~ prox_20 * income_filled | ID, data = df_ccb_income)

# Extract marginal effect of prox_20 at each income level using slopes()
slopes_ccb_inc_trust_qc <- slopes(mod_ccb_inc_trust_qc, variables = "prox_20",
                                   newdata = datagrid(income_filled = income_seq)) |>
  as_tibble() |> mutate(outcome = "Trust: QC Govt")

slopes_ccb_inc_trust_can <- slopes(mod_ccb_inc_trust_can, variables = "prox_20",
                                    newdata = datagrid(income_filled = income_seq)) |>
  as_tibble() |> mutate(outcome = "Trust: Canada Govt")

slopes_ccb_inc_attach_qc <- slopes(mod_ccb_inc_attach_qc, variables = "prox_20",
                                    newdata = datagrid(income_filled = income_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: Quebec")

slopes_ccb_inc_attach_can <- slopes(mod_ccb_inc_attach_can, variables = "prox_20",
                                     newdata = datagrid(income_filled = income_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: Canada")

slopes_ccb_inc_attach_city <- slopes(mod_ccb_inc_attach_city, variables = "prox_20",
                                      newdata = datagrid(income_filled = income_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: City")

slopes_ccb_inc_financial <- slopes(mod_ccb_inc_financial, variables = "prox_20",
                                    newdata = datagrid(income_filled = income_seq)) |>
  as_tibble() |> mutate(outcome = "Financial Satisfaction")

slopes_ccb_inc_life <- slopes(mod_ccb_inc_life, variables = "prox_20",
                               newdata = datagrid(income_filled = income_seq)) |>
  as_tibble() |> mutate(outcome = "Life Satisfaction")

slopes_ccb_inc_qcvalues <- slopes(mod_ccb_inc_qcvalues, variables = "prox_20",
                                   newdata = datagrid(income_filled = income_seq)) |>
  as_tibble() |> mutate(outcome = "QC Values Important")

slopes_ccb_inc_qcfriends <- slopes(mod_ccb_inc_qcfriends, variables = "prox_20",
                                    newdata = datagrid(income_filled = income_seq)) |>
  as_tibble() |> mutate(outcome = "QC Friends Important")

# Combine all slopes
income_slopes_ccb <- bind_rows(
  slopes_ccb_inc_trust_qc, slopes_ccb_inc_trust_can,
  slopes_ccb_inc_attach_qc, slopes_ccb_inc_attach_can, slopes_ccb_inc_attach_city,
  slopes_ccb_inc_financial, slopes_ccb_inc_life,
  slopes_ccb_inc_qcvalues, slopes_ccb_inc_qcfriends
)

# Plot
ggplot(income_slopes_ccb, aes(x = income_filled, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, fill = "darkgreen") +
  geom_line(color = "darkgreen", linewidth = 1) +
  facet_wrap(~ outcome, ncol = 3, scales = "free_y") +
  scale_x_continuous(breaks = 1:8, labels = income_labels) +
  labs(
    x = "Household Income",
    y = "Marginal Effect of CCB Payment Proximity"
  ) +
  theme_tufte(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.spacing = unit(1.2, "lines"),
    axis.title = element_text(size = 11),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8)
  )
```

```{r fig-interaction-french-ccb}
#| label: fig-interaction-french-ccb
#| fig-cap: "Marginal Effect of CCB Payment Proximity by French Competency (Exclusive CCB Recipients)"
#| fig-height: 12
#| fig-width: 12

# Estimate interaction models explicitly for each DV (CCB sample, using prox_20)
mod_ccb_fr_trust_qc <- feols(trust_qc ~ prox_20 * french_comp_filled | ID, data = df_ccb_french)
mod_ccb_fr_trust_can <- feols(trust_can ~ prox_20 * french_comp_filled | ID, data = df_ccb_french)
mod_ccb_fr_attach_qc <- feols(attachment_qc ~ prox_20 * french_comp_filled | ID, data = df_ccb_french)
mod_ccb_fr_attach_can <- feols(attachment_can ~ prox_20 * french_comp_filled | ID, data = df_ccb_french)
mod_ccb_fr_attach_city <- feols(attachment_city ~ prox_20 * french_comp_filled | ID, data = df_ccb_french)
mod_ccb_fr_financial <- feols(financial_satisf ~ prox_20 * french_comp_filled | ID, data = df_ccb_french)
mod_ccb_fr_life <- feols(life_satisf ~ prox_20 * french_comp_filled | ID, data = df_ccb_french)
mod_ccb_fr_qcvalues <- feols(imp_qcvalues ~ prox_20 * french_comp_filled | ID, data = df_ccb_french)
mod_ccb_fr_qcfriends <- feols(imp_qcfriends ~ prox_20 * french_comp_filled | ID, data = df_ccb_french)

# Extract marginal effect of prox_20 at each French competency level
slopes_ccb_fr_trust_qc <- slopes(mod_ccb_fr_trust_qc, variables = "prox_20",
                                  newdata = datagrid(french_comp_filled = french_seq)) |>
  as_tibble() |> mutate(outcome = "Trust: QC Govt")

slopes_ccb_fr_trust_can <- slopes(mod_ccb_fr_trust_can, variables = "prox_20",
                                   newdata = datagrid(french_comp_filled = french_seq)) |>
  as_tibble() |> mutate(outcome = "Trust: Canada Govt")

slopes_ccb_fr_attach_qc <- slopes(mod_ccb_fr_attach_qc, variables = "prox_20",
                                   newdata = datagrid(french_comp_filled = french_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: Quebec")

slopes_ccb_fr_attach_can <- slopes(mod_ccb_fr_attach_can, variables = "prox_20",
                                    newdata = datagrid(french_comp_filled = french_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: Canada")

slopes_ccb_fr_attach_city <- slopes(mod_ccb_fr_attach_city, variables = "prox_20",
                                     newdata = datagrid(french_comp_filled = french_seq)) |>
  as_tibble() |> mutate(outcome = "Attachment: City")

slopes_ccb_fr_financial <- slopes(mod_ccb_fr_financial, variables = "prox_20",
                                   newdata = datagrid(french_comp_filled = french_seq)) |>
  as_tibble() |> mutate(outcome = "Financial Satisfaction")

slopes_ccb_fr_life <- slopes(mod_ccb_fr_life, variables = "prox_20",
                              newdata = datagrid(french_comp_filled = french_seq)) |>
  as_tibble() |> mutate(outcome = "Life Satisfaction")

slopes_ccb_fr_qcvalues <- slopes(mod_ccb_fr_qcvalues, variables = "prox_20",
                                  newdata = datagrid(french_comp_filled = french_seq)) |>
  as_tibble() |> mutate(outcome = "QC Values Important")

slopes_ccb_fr_qcfriends <- slopes(mod_ccb_fr_qcfriends, variables = "prox_20",
                                   newdata = datagrid(french_comp_filled = french_seq)) |>
  as_tibble() |> mutate(outcome = "QC Friends Important")

# Combine all slopes
french_slopes_ccb <- bind_rows(
  slopes_ccb_fr_trust_qc, slopes_ccb_fr_trust_can,
  slopes_ccb_fr_attach_qc, slopes_ccb_fr_attach_can, slopes_ccb_fr_attach_city,
  slopes_ccb_fr_financial, slopes_ccb_fr_life,
  slopes_ccb_fr_qcvalues, slopes_ccb_fr_qcfriends
)

# Plot
ggplot(french_slopes_ccb, aes(x = french_comp_filled, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, fill = "darkorange") +
  geom_line(color = "darkorange", linewidth = 1) +
  facet_wrap(~ outcome, ncol = 3, scales = "free_y") +
  scale_x_continuous(breaks = seq(0, 10, 2)) +
  labs(
    x = "French Competency (0-10)",
    y = "Marginal Effect of CCB Payment Proximity"
  ) +
  theme_tufte(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.spacing = unit(1.2, "lines"),
    axis.title = element_text(size = 11)
  )
```

# Discussion

This paper provides evidence that government benefit payments shape immigrants' political attitudes toward their host society. Using quasi-random variation in survey timing relative to fixed payment dates, I find that proximity to payday increases immigrants' attachment to Quebec, their financial satisfaction, and the importance they place on Quebec values and friendships. These effects are robust to multiple placebo tests and appear specific to immigrant populations.

The findings contribute to several literatures. First, they extend work on policy feedback effects [@campbell2012; @mettler2011] to immigrant populations, showing that welfare state policies may facilitate political integration through repeated material signals of state support. Second, they speak to debates about economic voting and credit attribution [@healy2017; @margalit2013], demonstrating that even relatively small, routine government transfers can shape political orientations when recipients connect benefits to government. Third, they contribute to research on immigrant political incorporation [@dinesen2012; @just2017], identifying a previously unexplored mechanism by which host societies may foster immigrant attachment.

The results also carry implications for contemporary debates about immigrant access to welfare. Welfare chauvinism rests on an implicit cost-benefit calculation: that benefits extended to immigrants yield returns only for the immigrants themselves, at the expense of native taxpayers. This framing ignores potential positive externalities. If benefit receipt builds political belonging, then welfare access may generate precisely the outcomes that receiving societies seek from immigrants—attachment to the host polity, adoption of its values, and investment in social relationships with natives. The broader implication is that integration policy need not rely solely on explicit programming like language classes or civic education; the everyday experience of receiving state support may itself constitute a powerful, if unrecognized, integration mechanism. Countries that restrict immigrant welfare access in the name of fiscal prudence may inadvertently undermine political incorporation.

Several limitations warrant discussion. The analysis cannot identify precisely *why* payment proximity affects attitudes—whether through gratitude, financial security reducing anxiety, or increased salience of government's role in daily life. The effects, while statistically significant, are modest in magnitude. And the Quebec context, with its robust welfare state and distinctive political dynamics around belonging, may not generalize to other settings.

Nevertheless, the results suggest that the welfare state may serve as a mechanism of immigrant political integration—not through explicit citizenship requirements or civic education, but through the quotidian experience of receiving government support. Each benefit payment represents a tangible demonstration that the host society provides for newcomers, potentially building the material foundations of political belonging.

Future research could productively explore several directions. First, examining which specific mechanisms drive the effect—gratitude, financial security, or government salience—would help clarify the theoretical channel. Second, testing whether similar patterns hold in contexts with less generous welfare states or different political cultures would establish generalizability. Third, investigating whether short-term attitude effects translate into longer-term behavioral outcomes, such as civic participation or naturalization, would establish the political significance of these findings. Finally, comparing the integration effects of different policy instruments—cash transfers versus in-kind benefits, universal versus targeted programs—could inform policy design.

\newpage

# References

::: {#refs}
:::

\newpage

# Appendix {.unnumbered}

## Wrong-Date Placebo: Immigrant Beneficiaries {.unnumbered}

@tbl-app-placebo-wrong presents the wrong-date placebo test for immigrant beneficiaries. For each beneficiary, proximity is calculated to a payment date they do *not* receive. Null effects indicate that the actual payment date specifically matters.

```{r tbl-app-placebo-wrong}
#| label: tbl-app-placebo-wrong
#| tbl-cap: "Wrong-Date Placebo Test (Immigrant Beneficiaries)"

modelsummary(
  list(
    "QC" = p1, "CAN" = p2,
    "QC" = p3, "CAN" = p4, "City" = p5,
    "Financial" = p6, "Life" = p7,
    "Values" = p8, "Friends" = p9
  ),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = c("prox_wrong" = "Proximity (Wrong Date)"),
  gof_map = c("nobs", "FE: ID"),
  output = "tinytable"
) |>
  group_tt(j = list("Trust in\ngovt. of:" = 2:3, "Attachment\nto:" = 4:6, "Satisfaction\nwith:" = 7:8, "Importance of QC" = 9:10)) |>
  theme_tt("striped") |>
  theme_tt("resize") |>
  style_tt(j = 1, bold = TRUE) |>
  style_tt(fontsize = 0.8)
```

## Wrong-Date Placebo: Non-Immigrant Beneficiaries {.unnumbered}

@tbl-app-nat-placebo presents the wrong-date placebo test for non-immigrant beneficiaries.

```{r tbl-app-nat-placebo}
#| label: tbl-app-nat-placebo
#| tbl-cap: "Wrong-Date Placebo Test (Non-Immigrant Beneficiaries)"

np1 <- feols(trust_qc ~ prox_wrong | ID, data = df_nat)
np2 <- feols(trust_can ~ prox_wrong | ID, data = df_nat)
np3 <- feols(attachment_qc ~ prox_wrong | ID, data = df_nat)
np4 <- feols(attachment_can ~ prox_wrong | ID, data = df_nat)
np5 <- feols(attachment_city ~ prox_wrong | ID, data = df_nat)
np6 <- feols(financial_satisf ~ prox_wrong | ID, data = df_nat)
np7 <- feols(life_satisf ~ prox_wrong | ID, data = df_nat)
np8 <- feols(imp_qcvalues ~ prox_wrong | ID, data = df_nat)
np9 <- feols(imp_qcfriends ~ prox_wrong | ID, data = df_nat)

modelsummary(
  list(
    "QC" = np1, "CAN" = np2,
    "QC" = np3, "CAN" = np4, "City" = np5,
    "Financial" = np6, "Life" = np7,
    "Values" = np8, "Friends" = np9
  ),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = c("prox_wrong" = "Proximity (Wrong Date)"),
  gof_map = c("nobs", "FE: ID"),
  output = "tinytable"
) |>
  group_tt(j = list("Trust in\ngovt. of:" = 2:3, "Attachment\nto:" = 4:6, "Satisfaction\nwith:" = 7:8, "Importance of QC" = 9:10)) |>
  theme_tt("striped") |>
  theme_tt("resize") |>
  style_tt(j = 1, bold = TRUE) |>
  style_tt(fontsize = 0.8)
```

## Interaction Models: Years in Quebec {.unnumbered}

@tbl-app-interaction-years presents the full interaction model coefficients for payment proximity × years in Quebec. A significant interaction term indicates that the effect of payment proximity varies by time spent in Quebec.

```{r tbl-app-interaction-years}
#| label: tbl-app-interaction-years
#| tbl-cap: "Interaction Effects: Payment Proximity × Years in Quebec (Immigrant Beneficiaries)"

# Estimate interaction models
int_y1 <- feols(trust_qc ~ prox_actual * years_in_qc | ID, data = df_imm_years)
int_y2 <- feols(trust_can ~ prox_actual * years_in_qc | ID, data = df_imm_years)
int_y3 <- feols(attachment_qc ~ prox_actual * years_in_qc | ID, data = df_imm_years)
int_y4 <- feols(attachment_can ~ prox_actual * years_in_qc | ID, data = df_imm_years)
int_y5 <- feols(attachment_city ~ prox_actual * years_in_qc | ID, data = df_imm_years)
int_y6 <- feols(financial_satisf ~ prox_actual * years_in_qc | ID, data = df_imm_years)
int_y7 <- feols(life_satisf ~ prox_actual * years_in_qc | ID, data = df_imm_years)
int_y8 <- feols(imp_qcvalues ~ prox_actual * years_in_qc | ID, data = df_imm_years)
int_y9 <- feols(imp_qcfriends ~ prox_actual * years_in_qc | ID, data = df_imm_years)

modelsummary(
  list(
    "QC" = int_y1, "CAN" = int_y2,
    "QC" = int_y3, "CAN" = int_y4, "City" = int_y5,
    "Financial" = int_y6, "Life" = int_y7,
    "Values" = int_y8, "Friends" = int_y9
  ),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = c(
    "prox_actual" = "Proximity",
    "prox_actual:years_in_qc" = "Proximity × Years in QC"
  ),
  gof_map = c("nobs", "FE: ID"),
  output = "tinytable"
) |>
  group_tt(j = list("Trust in\ngovt. of:" = 2:3, "Attachment\nto:" = 4:6, "Satisfaction\nwith:" = 7:8, "Importance of QC" = 9:10)) |>
  theme_tt("striped") |>
  theme_tt("resize") |>
  style_tt(j = 1, bold = TRUE) |>
  style_tt(fontsize = 0.8)
```

## Interaction Models: Household Income {.unnumbered}

@tbl-app-interaction-income presents the full interaction model coefficients for payment proximity × household income. Household income is coded on an 8-point scale from 1 (no income) to 8 (\>\$200,000). A significant interaction term indicates that the effect of payment proximity varies by income level.

```{r tbl-app-interaction-income}
#| label: tbl-app-interaction-income
#| tbl-cap: "Interaction Effects: Payment Proximity × Household Income (Immigrant Beneficiaries)"

# Estimate interaction models
int_i1 <- feols(trust_qc ~ prox_actual * income_filled | ID, data = df_imm_income)
int_i2 <- feols(trust_can ~ prox_actual * income_filled | ID, data = df_imm_income)
int_i3 <- feols(attachment_qc ~ prox_actual * income_filled | ID, data = df_imm_income)
int_i4 <- feols(attachment_can ~ prox_actual * income_filled | ID, data = df_imm_income)
int_i5 <- feols(attachment_city ~ prox_actual * income_filled | ID, data = df_imm_income)
int_i6 <- feols(financial_satisf ~ prox_actual * income_filled | ID, data = df_imm_income)
int_i7 <- feols(life_satisf ~ prox_actual * income_filled | ID, data = df_imm_income)
int_i8 <- feols(imp_qcvalues ~ prox_actual * income_filled | ID, data = df_imm_income)
int_i9 <- feols(imp_qcfriends ~ prox_actual * income_filled | ID, data = df_imm_income)

modelsummary(
  list(
    "QC" = int_i1, "CAN" = int_i2,
    "QC" = int_i3, "CAN" = int_i4, "City" = int_i5,
    "Financial" = int_i6, "Life" = int_i7,
    "Values" = int_i8, "Friends" = int_i9
  ),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = c(
    "prox_actual" = "Proximity",
    "prox_actual:income_filled" = "Proximity × HH Income"
  ),
  gof_map = c("nobs", "FE: ID"),
  output = "tinytable"
) |>
  group_tt(j = list("Trust in\ngovt. of:" = 2:3, "Attachment\nto:" = 4:6, "Satisfaction\nwith:" = 7:8, "Importance of QC" = 9:10)) |>
  theme_tt("striped") |>
  theme_tt("resize") |>
  style_tt(j = 1, bold = TRUE) |>
  style_tt(fontsize = 0.8)
```

## Interaction Models: French Competency {.unnumbered}

@tbl-app-interaction-french presents the full interaction model coefficients for payment proximity × French competency. French competency is self-reported on a 0-10 scale. A significant negative interaction term would indicate that payment proximity effects are stronger at lower levels of French competency.

```{r tbl-app-interaction-french}
#| label: tbl-app-interaction-french
#| tbl-cap: "Interaction Effects: Payment Proximity × French Competency (Immigrant Beneficiaries)"

# Estimate interaction models
int_f1 <- feols(trust_qc ~ prox_actual * french_comp_filled | ID, data = df_imm_french)
int_f2 <- feols(trust_can ~ prox_actual * french_comp_filled | ID, data = df_imm_french)
int_f3 <- feols(attachment_qc ~ prox_actual * french_comp_filled | ID, data = df_imm_french)
int_f4 <- feols(attachment_can ~ prox_actual * french_comp_filled | ID, data = df_imm_french)
int_f5 <- feols(attachment_city ~ prox_actual * french_comp_filled | ID, data = df_imm_french)
int_f6 <- feols(financial_satisf ~ prox_actual * french_comp_filled | ID, data = df_imm_french)
int_f7 <- feols(life_satisf ~ prox_actual * french_comp_filled | ID, data = df_imm_french)
int_f8 <- feols(imp_qcvalues ~ prox_actual * french_comp_filled | ID, data = df_imm_french)
int_f9 <- feols(imp_qcfriends ~ prox_actual * french_comp_filled | ID, data = df_imm_french)

modelsummary(
  list(
    "QC" = int_f1, "CAN" = int_f2,
    "QC" = int_f3, "CAN" = int_f4, "City" = int_f5,
    "Financial" = int_f6, "Life" = int_f7,
    "Values" = int_f8, "Friends" = int_f9
  ),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = c(
    "prox_actual" = "Proximity",
    "prox_actual:french_comp_filled" = "Proximity × French Competency"
  ),
  gof_map = c("nobs", "FE: ID"),
  output = "tinytable"
) |>
  group_tt(j = list("Trust in\ngovt. of:" = 2:3, "Attachment\nto:" = 4:6, "Satisfaction\nwith:" = 7:8, "Importance of QC" = 9:10)) |>
  theme_tt("striped") |>
  theme_tt("resize") |>
  style_tt(j = 1, bold = TRUE) |>
  style_tt(fontsize = 0.8)
```

## Interaction Models: Education {.unnumbered}

@tbl-app-interaction-educ presents the full interaction model coefficients for payment proximity × education level. Education is coded on a 1-7 scale (1 = no education, 7 = PhD/professional degree).

```{r tbl-app-interaction-educ}
#| label: tbl-app-interaction-educ
#| tbl-cap: "Interaction Effects: Payment Proximity × Education (Immigrant Beneficiaries)"

int_ed1 <- feols(trust_qc ~ prox_actual * education_num_filled | ID, data = df_imm_educ)
int_ed2 <- feols(trust_can ~ prox_actual * education_num_filled | ID, data = df_imm_educ)
int_ed3 <- feols(attachment_qc ~ prox_actual * education_num_filled | ID, data = df_imm_educ)
int_ed4 <- feols(attachment_can ~ prox_actual * education_num_filled | ID, data = df_imm_educ)
int_ed5 <- feols(attachment_city ~ prox_actual * education_num_filled | ID, data = df_imm_educ)
int_ed6 <- feols(financial_satisf ~ prox_actual * education_num_filled | ID, data = df_imm_educ)
int_ed7 <- feols(life_satisf ~ prox_actual * education_num_filled | ID, data = df_imm_educ)
int_ed8 <- feols(imp_qcvalues ~ prox_actual * education_num_filled | ID, data = df_imm_educ)
int_ed9 <- feols(imp_qcfriends ~ prox_actual * education_num_filled | ID, data = df_imm_educ)

modelsummary(
  list(
    "QC" = int_ed1, "CAN" = int_ed2,
    "QC" = int_ed3, "CAN" = int_ed4, "City" = int_ed5,
    "Financial" = int_ed6, "Life" = int_ed7,
    "Values" = int_ed8, "Friends" = int_ed9
  ),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = c(
    "prox_actual" = "Proximity",
    "prox_actual:education_num_filled" = "Proximity × Education"
  ),
  gof_map = c("nobs", "FE: ID"),
  output = "tinytable"
) |>
  group_tt(j = list("Trust in\ngovt. of:" = 2:3, "Attachment\nto:" = 4:6, "Satisfaction\nwith:" = 7:8, "Importance of QC" = 9:10)) |>
  theme_tt("striped") |>
  theme_tt("resize") |>
  style_tt(j = 1, bold = TRUE) |>
  style_tt(fontsize = 0.8)
```

## Interaction Models: Political Knowledge {.unnumbered}

@tbl-app-interaction-polknow presents the full interaction model coefficients for payment proximity × political knowledge score. Political knowledge is measured as the number of politicians correctly identified (0-4 scale).

```{r tbl-app-interaction-polknow}
#| label: tbl-app-interaction-polknow
#| tbl-cap: "Interaction Effects: Payment Proximity × Political Knowledge (Immigrant Beneficiaries)"

int_pk1 <- feols(trust_qc ~ prox_actual * polknow_score | ID, data = df_imm_polknow)
int_pk2 <- feols(trust_can ~ prox_actual * polknow_score | ID, data = df_imm_polknow)
int_pk3 <- feols(attachment_qc ~ prox_actual * polknow_score | ID, data = df_imm_polknow)
int_pk4 <- feols(attachment_can ~ prox_actual * polknow_score | ID, data = df_imm_polknow)
int_pk5 <- feols(attachment_city ~ prox_actual * polknow_score | ID, data = df_imm_polknow)
int_pk6 <- feols(financial_satisf ~ prox_actual * polknow_score | ID, data = df_imm_polknow)
int_pk7 <- feols(life_satisf ~ prox_actual * polknow_score | ID, data = df_imm_polknow)
int_pk8 <- feols(imp_qcvalues ~ prox_actual * polknow_score | ID, data = df_imm_polknow)
int_pk9 <- feols(imp_qcfriends ~ prox_actual * polknow_score | ID, data = df_imm_polknow)

modelsummary(
  list(
    "QC" = int_pk1, "CAN" = int_pk2,
    "QC" = int_pk3, "CAN" = int_pk4, "City" = int_pk5,
    "Financial" = int_pk6, "Life" = int_pk7,
    "Values" = int_pk8, "Friends" = int_pk9
  ),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = c(
    "prox_actual" = "Proximity",
    "prox_actual:polknow_score" = "Proximity × Pol. Knowledge"
  ),
  gof_map = c("nobs", "FE: ID"),
  output = "tinytable"
) |>
  group_tt(j = list("Trust in\ngovt. of:" = 2:3, "Attachment\nto:" = 4:6, "Satisfaction\nwith:" = 7:8, "Importance of QC" = 9:10)) |>
  theme_tt("striped") |>
  theme_tt("resize") |>
  style_tt(j = 1, bold = TRUE) |>
  style_tt(fontsize = 0.8)
```

## Interaction Models: Policy Knowledge {.unnumbered}

@tbl-app-interaction-policyknow presents the full interaction model coefficients for payment proximity × policy knowledge score. Policy knowledge is measured as the number of policy questions answered correctly (0-6 scale).

```{r tbl-app-interaction-policyknow}
#| label: tbl-app-interaction-policyknow
#| tbl-cap: "Interaction Effects: Payment Proximity × Policy Knowledge (Immigrant Beneficiaries)"

int_pok1 <- feols(trust_qc ~ prox_actual * policyknow_score | ID, data = df_imm_policyknow)
int_pok2 <- feols(trust_can ~ prox_actual * policyknow_score | ID, data = df_imm_policyknow)
int_pok3 <- feols(attachment_qc ~ prox_actual * policyknow_score | ID, data = df_imm_policyknow)
int_pok4 <- feols(attachment_can ~ prox_actual * policyknow_score | ID, data = df_imm_policyknow)
int_pok5 <- feols(attachment_city ~ prox_actual * policyknow_score | ID, data = df_imm_policyknow)
int_pok6 <- feols(financial_satisf ~ prox_actual * policyknow_score | ID, data = df_imm_policyknow)
int_pok7 <- feols(life_satisf ~ prox_actual * policyknow_score | ID, data = df_imm_policyknow)
int_pok8 <- feols(imp_qcvalues ~ prox_actual * policyknow_score | ID, data = df_imm_policyknow)
int_pok9 <- feols(imp_qcfriends ~ prox_actual * policyknow_score | ID, data = df_imm_policyknow)

modelsummary(
  list(
    "QC" = int_pok1, "CAN" = int_pok2,
    "QC" = int_pok3, "CAN" = int_pok4, "City" = int_pok5,
    "Financial" = int_pok6, "Life" = int_pok7,
    "Values" = int_pok8, "Friends" = int_pok9
  ),
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = c(
    "prox_actual" = "Proximity",
    "prox_actual:policyknow_score" = "Proximity × Policy Knowledge"
  ),
  gof_map = c("nobs", "FE: ID"),
  output = "tinytable"
) |>
  group_tt(j = list("Trust in\ngovt. of:" = 2:3, "Attachment\nto:" = 4:6, "Satisfaction\nwith:" = 7:8, "Importance of QC" = 9:10)) |>
  theme_tt("striped") |>
  theme_tt("resize") |>
  style_tt(j = 1, bold = TRUE) |>
  style_tt(fontsize = 0.8)
```
